\subsection{%
  Evidence of Mr. Taximov's receipt of lesser nationally or internationally recognized prizes or awards for excellence%
}
\label{subsec:Awards}

% =========================================================
% STATE MEDAL — "EREN ENBEGI UShIN" (2025)
% =========================================================
\subsubsection{Medal “Eren enbegi ushin”(\emph{For Distinguished Labour}). The Republic of Kazakhstan, 2025}
\label{subsubsec:ErenEnbegi2025}

On \textbf{21 October 2025}, Mr.~Taximov was awarded the state medal \textbf{“Eren enbegi ushin”} (\emph{For Distinguished Labour}) by \textbf{Presidential Decree}. Certificate and medal set were received, both personally issued to Mr. Taximov. \ExhibitRef{ErenEnbegi_Photo1}\ExhibitRef{ErenEnbegi_Photo2}

Under the Law \emph{“On State Awards of the Republic of Kazakhstan”}:

\begin{itemize}

  \item \textbf{State awards are conferred by the President} to citizens (and, where applicable, foreign nationals) in recognition of services to the Republic and labour feats. (Art.~1; \emph{awarded by the President, national scope})

  \item \textbf{State awards} are insignia of the highest distinctions, comprising orders, medals and honorary titles; names of state awards are established in the state language and their descriptions and certificate forms are \textbf{approved by the President}. (Arts.~2–3)

  \item The list of \textbf{medals of the Republic of Kazakhstan} expressly includes \textbf{“Eren enbegi ushin”}. (Art.~18)

  \item The \textbf{“Eren enbegi ushin” medal} is awarded to citizens \textbf{for labour achievements in the economic and social spheres, science, culture and public service}. (Art.~21)

\end{itemize}

\noindent\textit{Citations (authority text provided by petitioner).}
\ParagraphQuote{“Citizens of the Republic of Kazakhstan … shall be awarded state awards… State awards are awarded by the President of the Republic of Kazakhstan.”}{On State Awards of the Republic of Kazakhstan, Art.~1}
\ParagraphQuote{“State awards … include other orders, medals and honorary titles.”}{Art.~2}
\ParagraphQuote{“Names of state awards … are established in the state language… descriptions … certificates … are approved by the President.”}{Art.~3}
\ParagraphQuote{“Medals of the Republic of Kazakhstan are: … ‘Eren enbegi ushin’.”}{Art.~18}
\ParagraphQuote{“The ‘Eren enbegi ushin’ medal is awarded to citizens for labour achievements in economic and social spheres, science, culture and public service.”}{Art.~21}


This is a \textbf{national, presidential state award} written into law and listed among the \textbf{medals of the Republic of Kazakhstan}. It is \textbf{conferred by the President} and recognizes \textbf{excellence in labour achievements} across nationally important fields. The statutory framework (Arts.~1–3, 18, 21) and the certificate together demonstrate that the medal is a \textbf{lesser nationally recognized prize for excellence}.

\ExhibitList{%
  \ExhibitRef{ErenEnbegi_Photo1}% (booklet with decree text + medal)
  \ExhibitRef{ErenEnbegi_Photo2}% (booklet page with name + serial no. 23064 + medal)
}

\pagebreak


\subsubsection{“Bolashak” International Scholarship. President of the Republic of Kazakhstan, 2013–2014}

The JSC “Center for International Programs” (CIP) issued two letters confirming that Mr. Askar Taximov is a recipient of the Bolashak International Scholarship. One of the letters is addressed to University College London (UCL) and the other is for the British Embassy Office for visa processing. Each letter is signed by the President of CIP and shows the funded degree (Master) and major (Building and Urban Design in Development), with the funded period from 23 September 2013 to 22 September 2014.

The Bolashak International Scholarship of the President of the Republic of Kazakhstan was established by Presidential Decree on November 5, 1993, initiated by the First President of Kazakhstan, Nursultan Nazarbayev. The program aims to develop highly qualified personnel in priority economic sectors by funding advanced academic studies and internships abroad.

The scholarship operates according to Government resolutions that approve the Rules for selecting candidates for the Bolashak scholarship. By Presidential Decree No. 1569 dated May 4, 2005, the Government of the Republic of Kazakhstan was mandated to approve the Rules for selection of applicants for the award of the Bolashak International Scholarship. Additionally, Government Decree No. 301 dated April 4, 2005, established the Joint Stock Company “Center for International Programs” (CIP) to administer the program.



The Bolashak program's selection process is competitive, strict and merit-based. It consists of three separate rounds.



\textbf{Round 1. Comprehensive Testing}

The testing process evaluates the candidate's ability to analyze and comprehend information within a constrained time limit.

Candidates need to complete three online assessments with audio and video monitoring:

\begin{itemize}
  \item Verbal Reasoning 
  \item Numerical Reasoning 
  \item Personality Assessment
\end{itemize}

Only the candidates who met the minimum threshold score proceed to Round 2. No retesting is allowed.

\textbf{Round 2.Expert Commission Interview}

Expert Commission assesses each candidate's professional preparation and suitability for the scholarship by conducting anonymous personal interview.

The assessment focuses on the applicant's level of professional training, theoretical knowledge, and professional competencies in the chosen field of specialization. The Commision members provide recommendations for each applicant, taking into account the information provided in the applicant's motivation letter.


\textbf{Round 3. Republican Commission Decision}

The Republican Commission for Training Personnel Abroad operates as an advisory and consultative body to the President of the Republic of Kazakhstan. It was established under  the Presidential Decree No. 470 of October 12, 2000. The Commission is responsible for supervising the implementation of the Bolashak International Scholarship, it has members who are appointed directly by the President. The Commission's is chairman is the State Counselor of the Republic of Kazakhstan, the Minister of Science and Higher Education serving as Deputy Chairperson and the Vice-Minister as Secretary.


Applicants' materials for the third round are submitted to the Republican Commission for Training Personnel Abroad, along with the results of comprehensive testing and recommendations from the Independent Expert Commission (IEC).

In the third round, the Republican Commission reviews the results of the first and second rounds and makes a final decision on the award or refusal to award the Bolashak scholarship, which is communicated to the applicant by posting information on the administrator's official website after the signing of the meeting minutes.


Commission sessions are considered valid only with a quorum of two-thirds of members. The members adopt decisions by open vote, a minimum three-quarters majority is required for any resolution to take effect. Each granted scholarship is based on a transparent, merit-based decision through this framework. It ensures highly selective outcomes, as annual applicant numbers reach approximately 10,000, but only around 400–500 scholarships are granted. In 2013, 427 individuals were awarded the scholarship, including Mr. Taximov. Thus, the acceptance rate typically remains near 4–5\%, displaying the program’s exclusivity and competitive standards.




The letters state that Mr. Taximov will be fully funded by the Government of the Republic of Kazakhstan for the approved duration of his academic program at University College London.

Both CIP letters state that the Government of Kazakhstan, via CIP, serves as sponsor and guarantor \$60000 and covers the expenditures for the tuition fee, living costs (food and accommodation), round-trip travel, book allowance and medical examination for the academic year.



As documented in the record, the total scholarship funding allocated for the UCL academic year was approximately USD 100,000. The other half of the overall award was used for 1.5 years of preparatory courses prior to enrollment (language training, pre-sessional course, and pre-master training).



Mr. Taximov intended to pivot into Data Science and IT Project management work. However, under the Bolashak Scholarship the funded specialty abroud had to be related to the underground degree, therefore he undertook UCL's MSc degree program (Building and Urban Design in Development). To implement this interdisciplinary transition, at his MSc dissertation he used IT method the Spatial Decision Support System (SDSS) for affordable housing need assessment in Kazakhstan, with a working prototype illustrated in his thesis.  

The SDSS IT method included data collection layer, Java web crawler for collecting rental ads form the main source krisha.kz website, demographic statistics obtained from the national portal stat.gov.kz. 

Moreover, datasets were stored in a MongoDB database, GIS and base maps were used to prepare spatial boundaries, then display through Google Maps API.

The final part of the thesis, user interface and presentations which had included diagrams and page layout refinements were prepared in graphic softwares such as AutoCAD and CorelDRAW.

This above mentioned thesis method allowed Mr. Taximov to sharpen his IT experience in a real world project, ultimately serving as a bridge into IT Project Management. 







Bolashak is a national, presidential scholarship awarded through competitive, expert-reviewed selection with final decisions by a Republican Commission chaired by the State Counselor and comprising senior government officials appointed by the President. The three-round selection process rigorously evaluates Bolashak recipients, distinguishing them from the general applicant population with an acceptance rate of approximately 4-5\% in 2013. The CIP letters prove individual receipt by Mr. Taximov and substantial value (total USD 200,000). Although the funded master’s specialization was not focused on pure IT, Mr. Taximov’s MsC degree dissertation anchored his studies in information technologies and data systems, directly supporting his subsequent career in IT Project Management.






\ExhibitList{

  \ExhibitRef{BolashakFG_UCL}

  \ExhibitRef{BolashakFG_Embassy}

  \ExhibitRef{BolashakDecree2005}

  \ExhibitRef{BolashakDecreeAmend}

}



\pagebreak



% % =========================================================
% % PRESIDENT — SCO SUMMIT (2024)
% % =========================================================
% \subsubsection{President of the Republic of Kazakhstan — Letter of Appreciation for the SCO Summit (2024)}
% \label{subsubsec:PresSCO2024}

% In 2024, Mr.~Taximov received a formal \emph{Presidential Letter of Appreciation} signed by \textbf{Kassym\kern0.08em-Jomart Tokayev}, \textbf{President of the Republic of Kazakhstan}, for a significant contribution to the organization and conduct of the \emph{Shanghai Cooperation Organization (SCO) Summit} in Astana. The document bears state insignia and personally names Mr.~Taximov. \ExhibitRef{PresAlghys2024}

% \ParagraphQuoteByExhibit{``I express my gratitude for your active participation in preparing and holding the Shanghai Cooperation Organization summit in Astana at a high level.''}{President of Kazakhstan, Letter of Appreciation (2024) — Eng.\ transl.}{PresAlghys2024}

% \SubSubSubSection{Operational context and scope of contribution}
% Under Mr.~Taximov’s leadership, the \emph{iKOMEK109} Monitoring and Rapid Response Center executed an integrated operational program for the summit that combined organizational measures with citywide IT infrastructure:

% \paragraph{Organizational measures.}
% \begin{itemize}
%   \item \textbf{24/7 citizen-intake operations} across public safety, housing and utilities and other urban-infrastructure topics;
%   \item \textbf{Digital monitoring of public channels:} social-media operators tracked mentions and resident signals and escalated incidents in near real time;
%   \item \textbf{On-site multi-agency operations hub} hosted at iKOMEK109 to coordinate emergency and security services and ensure timely response to potential threats and incidents.
% \end{itemize}

% \paragraph{Use of IT infrastructurem hardware and software complexes.}
% \begin{itemize}
%   \item \textbf{City video-surveillance complex} (IP cameras, videowalls, processing servers) monitored mass-gathering sites, infrastructure facilities, rail/bus terminals, the airport and key roads and intersections;
%   \item \textbf{Situational video analytics} supported heat maps, crowding detection and tracking of pedestrian and vehicle flows;
%   \item \textbf{Cyber-protection measures} included protected data channels (VPN and encryption), server and system redundancy and network-activity monitoring to prevent unauthorized access;
%   \item \textbf{Systems integration with public-safety agencies} (police, emergency and medical) enabled automatic routing of alerts and instant interagency interaction.
% \end{itemize}

% \paragraph{Result recognized by the award.}
% The merger of these organizational workflows with surveillance analytics, cyber-defense and real-time digital communications ensured a high level of safety for summit guests and participants, stable functioning of city infrastructure and rapid response to threats in both physical and digital domains. The Presidential Commendation recognizes Mr.~Taximov’s key role and leadership in applying IT tools to address operations of national significance. % Source: explanatory note + Presidential letter (attached)

% The initiative required end-to-end ownership of mission-critical civic platforms: defining processes orchestrating cross-agency teams, integrating hardware–software systems, instrumenting analytics, enforcing reliability and security controls and operating at international-event scale—core responsibilities of product and program leadership in the IT Project Management domain.

% A named, signed \emph{Presidential} commendation tied to an international summit constitutes national-level recognition for excellence in the field and satisfies USCIS Criterion~1 for lesser nationally recognized awards.

% \textbf{Legal status of the Presidential Letter of Appreciation.}

% Under the official Regulation on the Presidential Letter of Appreciation of the Republic of Kazakhstan (Presidential Order No. 164 of January 12, 2021, updating Order No. 3230 of November 20, 1996), the “Letter of Appreciation of the President of the Republic of Kazakhstan” is defined as an official form of state recognition awarded by the Head of State for exceptional service and achievements benefiting society and the nation. The Regulation specifies that each Letter is personally signed by the President, bears national insignia, is formally registered by the Presidential Administration, and entered into the official Registry of Presidential Commendations. This codified procedure confirms that the Letter represents a formal governmental award rather than a ceremonial expression of gratitude. Accordingly, both personally addressed and signed Presidential Letter of Appreciation constitutes a nationally recognized distinction evidencing excellence and fulfills the evidentiary standard for a “lesser nationally recognized prize or award for excellence in the field of endeavor” under 8 C.F.R. § 204.5(h)(3)(i).


% \ExhibitList{\ExhibitRef{PresAlghys2024}}

% \pagebreak


\subsubsection{Letter of Appreciation for the SCO Summit. President of the Republic of Kazakhstan(2024)}



In 2024, Kassym-Jomart Tokayev, President of the Republic of Kazakhstan, awarded a formal Presidential Letter of Appreciation to Mr. Taximov for his significant contribution to organizing and conducting the Shanghai Cooperation Organization (SCO) Summit in Astana. The document bears state insignia.



“I express my gratitude for your active participation in preparing and holding the Shanghai Cooperation Organization summit in Astana at a high level.”



Under Mr. Taximov’s leadership, the iKOMEK109 Monitoring and Rapid Response Center executed an integrated operational program for the summit that combined organizational measures with citywide IT infrastructure.



Organizational measures:



24/7 citizen appeal operations across public safety, housing, utilities, and other urban infrastructure.


Digital monitoring of public channels. Tracked mentions  in social-media operators, resident signals and escalated incidents in near real time.

On-site multi-agency operations hub hosted at iKOMEK109 to coordinate emergency and security services and ensure timely response to potential threats and incidents.

Use of IT infrastructurem hardware and software complexes:

City video-surveillance complex (IP cameras, videowalls, processing servers) monitored mass-gathering sites, infrastructure facilities, rail/bus terminals, the airport and key roads and intersections.

Situational video analytics supported heat maps, crowding detection and tracking of pedestrian and vehicle flows.

Cyber-protection measures included protected data channels (VPN and encryption), server and system redundancy and network-activity monitoring to prevent unauthorized access.

By integrating the system with public-safety agencies (police, emergency and medical), automatic routing of alerts and instant interagency interaction was enabled.

The merger of these organizational workflows with surveillance analytics, cyber-defense, and real-time digital communications provided a high level of safety for summit guests and participants, ensured stable functioning of city infrastructure, and facilitated rapid response to threats in both physical and digital domains. The Presidential Commendation recognizes Mr. Taximov’s key role and leadership in applying IT tools to address operations of national significance.

The initiative required end-to-end ownership of mission-critical civic platforms: defining processes, orchestrating cross-agency teams, integrating hardware–software systems, instrumenting analytics, enforcing reliability and security controls, and operating at international-event scale—these are core responsibilities of product and program leadership in the IT Project Management domain.

The “Letter of Appreciation of the President” is defined as an official form of state recognition under the official Regulation on 'Presidential Appreciatoin'. The letter is awarded by the Head of State for exceptional service and achievements benefiting society and the country. The Regulation specifies that each Letter is personally signed by the President, bears national insignia. The Regulation states that the award is formally registered by the Presidential Administration, and entered into the official Registry of Presidential Commendations. This established procedure confirms that the Letter represents a formal governmental award rather than a ceremonial expression of gratitude. 

Accordingly, both personally addressed and signed Presidential Letter of Appreciation constitutes a nationally recognized distinction evidencing excellence and fulfills the evidentiary standard for a “lesser nationally recognized prize or award for excellence in the field of endeavor”.
% =========================================================
% PRESIDENT — ELECTION (2022)
% =========================================================
% \subsubsection{President of the Republic of Kazakhstan — Letter of Appreciation for the Extraordinary Presidential Election (2022)}
% \label{subsubsec:PresElection2022}

% In November 2022, Mr.~Taximov received a formal \emph{Presidential Letter of Appreciation} signed by \textbf{Kassym\kern0.08em-Jomart Tokayev}, President of the Republic of Kazakhstan, for his significant contribution to the preparation and conduct of the country’s extraordinary presidential election. \ExhibitRef{PresAlghys2022}

% \ParagraphQuoteByExhibit{``I thank you for your significant contribution to the preparation and conduct of the Presidential election of the Republic of Kazakhstan.''}{President of Kazakhstan, Letter of Appreciation (2022) — Eng.\ transl.}{PresAlghys2022}

% \SubSubSubSection{Election technology and data-governance program (delivered under Mr.~Taximov’s direction)}
% To ensure accuracy, transparency and security of the electoral process in the capital, Mr.~Taximov led an integrated program that combined organizational measures with a citywide technical implementation based on the \emph{Geonomics — Population Database} platform:

% \paragraph{Organizational measures.}
% \begin{itemize}
%   \item \textbf{Voter-roll accuracy and automated precinct:} updating voter lists and registration address codes(RAC), to ensure automatic polling station assignment;
%   \item \textbf{Identification of overcrowded registration addresses:} joint work with district mayors’ offices and the migration service to identify and correct anomalous multi-registrations;
%   \item \textbf{Generation of final voter list:} coordination with territorial commissions to form and approve final voter lists;
%   \item \textbf{Unified election call center at iKOMEK109:} operator training, a structured knowledge base and scripted escalation flows for citizen inquiries;
%   \item \textbf{Digital voter services:} launch of online tools and a Telegram bot for voters to check their polling station;
%   \item \textbf{Monitoring and analytics of citizen requests} throughout the election period.
% \end{itemize}

% \paragraph{Technical measures.}
% \begin{itemize}
%   \item \textbf{Core platform:} use and adaptation of the \emph{Geonomics — Population Database} information system;
%   \item \textbf{Data integrations:} linkage with the state \emph{Individuals} database and other sources to update records; automated attachment of voters to precincts by registered address to eliminate manual errors;
%   \item \textbf{GIS visualization:} digital precinct mapping, display of citizen distribution, territory analysis and precinct/district boundary construction;
%   \item \textbf{Correction of address geolocations:} ingestion and processing of vector, raster and attribute datasets with real-time editing and analysis;
%   \item \textbf{Security and access:} authenticated access (including e-signature login), protected export to approved formats (MDB, XLS) and service integrations via REST/SOAP/WSDL;
%   \item \textbf{Implementation stack:} development using \textbf{Python, JavaScript, SQL and Java} to achieve performance, scalability and reliability under high data volumes.
% \end{itemize}

% \paragraph{Result (recognized by the Presidential letter).}
% The program delivered highly accurate and up-to-date voter lists, transparent and convenient citizen services (online tools and a unified call center) and a resilient, secure information infrastructure for the national election. \ExhibitRef{PresAlghys2022}

% This initiative combined discovery (legal and stakeholder requirements), delivery (data pipelines, GIS services, voter tools, contact-center workflows) and operations (security controls, SLAs, quality gates)—the end-to-end lifecycle of public-sector product and program leadership at national scale.

% A \emph{Presidential} letter of appreciation tied to the conduct of a countrywide election is a nationally recognized distinction documenting excellence in a matter of national importance.

% \textbf{Legal status of the Presidential Letter of Appreciation.}

% Under the official Regulation on the Presidential Letter of Appreciation of the Republic of Kazakhstan (Presidential Order No. 164 of January 12, 2021, updating Order No. 3230 of November 20, 1996), the “Letter of Appreciation of the President of the Republic of Kazakhstan” is defined as an official form of state recognition awarded by the Head of State for exceptional service and achievements benefiting society and the nation. The Regulation specifies that each Letter is personally signed by the President, bears national insignia, is formally registered by the Presidential Administration, and entered into the official Registry of Presidential Commendations. This codified procedure confirms that the Letter represents a formal governmental award rather than a ceremonial expression of gratitude. Accordingly, both personally addressed and signed Presidential Letter of Appreciation constitutes a nationally recognized distinction evidencing excellence and fulfills the evidentiary standard for a “lesser nationally recognized prize or award for excellence in the field of endeavor” under 8 C.F.R. § 204.5(h)(3)(i).

% \textbf{Legal status of the Presidential Letter of Appreciation.}


% Under the Regulation on the Presidential Letter of Appreciation of the Republic of Kazakhstan (Presidential Order No.~164 of January 12, 2021, amending Order No.~3230 of November 20, 1996), the “Letter of Appreciation of the President of the Republic of Kazakhstan” is established as an official form of moral and state recognition awarded by the Head of State for merits before society and the nation (Clause 2). The Regulation defines a formal procedure for preparation, registration, announcement, and presentation of the Letter (Clause 1). Each Letter is personally signed by the President and bears state insignia (Clause 4 (2)); decisions to confer it are made by the President either on his own initiative or upon the recommendation of governmental bodies and organizations (Clause 5).  

% The Presidential Administration carries out official registration, documentation, and delivery of each Letter (Clause 9), while the record of all conferred Letters is maintained in an electronic registration database and the Book of Presidential Letters of Appreciation (Clause 10). The Regulation further provides that information on each award is entered into the recipient’s employment record and personal file (Clause 11).  

% This codified, state-supervised procedure confirms that the Presidential Letter of Appreciation is not a ceremonial expression of gratitude but a formal governmental distinction issued under presidential authority, bearing evidentiary equivalence to a national-level award. Accordingly, every personally addressed and signed Presidential Letter of Appreciation constitutes a nationally recognized prize or award for excellence in the field of endeavor within the meaning of 8 C.F.R. § 204.5(h)(3)(i).
% \ExhibitList{\ExhibitRef{PresAlghys2022}}


\subsubsection{Letter of Appreciation for the Extraordinary Presidential Election. President of the Republic of Kazakhstan (2022)}


In November 2022, Kassym-Jomart Tokayev, President of the Republic of Kazakhstan awarded Mr. Taximov with formal Presidential Letter of Appreciation, for his significant contribution to the preparation and conduct of the country’s extraordinary presidential election.

“I thank you for your significant contribution to the preparation and conduct of the Presidential election of the Republic of Kazakhstan.”

\textbf{Election technology and data-governance program delivered under Mr. Taximov’s direction}

To ensure accuracy, transparency and security of the electoral process in the capital, Mr. Taximov led an integrated program that combined organizational measures with a citywide technical implementation based on the “Geonomics — Population Database” platform.

\textbf{Organizational measures:}


\begin{itemize}

  \item Accuracy of voter list and automation of polling stations. Updating voter lists and registration address codes (RAC) to ensure automatic distribution across polling stations.

  \item Identification of overcrowded registration addresses: collaboration with district administrations and the migration service to identify and correct abnormal cases of multiple registration.

  \item Formation of the final voter list: coordination with territorial commissions on the formation and approval of final voter lists.

  \item Single election call center in iKOMEK109: training of operators, structured knowledge base, and scripted escalation flows for citizen inquiries.

  \item Digital services for voters: launch of online tools and a Telegram bot for voters to check their polling station.

  \item Monitoring and analysis of citizen inquiries throughout the election period.

\end{itemize}


\textbf{Technical architecture:}


\begin{itemize}

  \item Basic platform: use and adaptation of the 'Geonomics — Population Database' information system.

  \item Data integration: connection to the state database “Individuals” and other sources to update records; automatic linking of voters to polling stations by their registered address to eliminate manual errors.

  \item GIS visualization: digital mapping of polling stations, display of citizen distribution, analysis of territory, and construction of polling station/district boundaries.

  \item Address geolocation correction: reception and processing of vector, raster, and attribute data sets with the ability to edit and analyze in real time.

  \item Security and access: authenticated access (including login with electronic signature), secure export to approved formats (MDB, XLS), and service integration via REST/SOAP/WSDL.

\end{itemize}


The program delivered highly accurate and up-to-date voter lists, transparent and convenient citizen services (online tools and a unified call center) and a resilient, secure information infrastructure for the national election.


The program combined discovery (legal and stakeholder requirements), delivery (data pipelines, GIS services, voter tools, contact center workflows) and operations (security controls, SLAs, quality gates). It was an end-to-end lifecycle of public-sector program at national scale.


A Presidential letter of appreciation conferred for the successful conduct of a countrywide election constitutes a nationally recognized distinction evidencing excellence in a matter of national importance.

The “Letter of Appreciation of the President” is defined as an official form of state recognition under the official Regulation on 'Presidential Appreciatoin'. The letter is awarded by the Head of State for exceptional service and achievements benefiting society and the country. The Regulation specifies that each Letter is personally signed by the President, bears national insignia. The Regulation states that the award is formally registered by the Presidential Administration, and entered into the official Registry of Presidential Commendations. This established procedure confirms that the Letter represents a formal governmental award rather than a ceremonial expression of gratitude. 

Accordingly, both personally addressed and signed Presidential Letter of Appreciation constitutes a nationally recognized distinction evidencing excellence and fulfills the evidentiary standard for a “lesser nationally recognized prize or award for excellence in the field of endeavor”.



% =========================================================
% KASPERSKY (INTERNATIONAL) — APPRECIATION (2022)
% =========================================================
% \subsubsection{Kaspersky Lab (International) — Certificate of Appreciation for Contributions to Information Security (2022)}
% \label{subsubsec:KasperskyThanks2022}

% Kaspersky Lab’s Central Asia office issued Mr.~Taximov a signed and sealed \emph{Certificate of Appreciation} recognizing his contribution to the development of the information-security sector (also in connection with the professional holiday of Digitalization and IT Workers). % (DOCX source)

% \ParagraphQuoteByExhibit{``Certificate of Appreciation … for contribution to the development of the information security industry.''}{Kaspersky Lab (Central Asia), Certificate of Appreciation (2022) — Eng. transl.}{KasperskyThanks2022Ex}

% \SubSubSubSection{Cybersecurity leadership recognized by an international company}
% The basis for the recognition aligns with Mr.~Taximov’s cybersecurity leadership in practice:
% \begin{itemize}
%   \item \textbf{Strengthening the iKOMEK109 digital ecosystem:} deployment of modern protection and monitoring tools across a 24/7 city-scale digital platform;
%   \item \textbf{Public–private cooperation:} partnerships with leading vendors and integrators to improve resilience of critical municipal services;
%   \item \textbf{Institutionalization of incident-response practices:} standards and playbooks for government/quasi-government organizations, including privacy and data-protection measures;
%   \item \textbf{Digital literacy and secure-by-design promotion:} broad outreach to enhance security postures across state information systems.
% \end{itemize}
% These activities are consistent with Mr.~Taximov’s concurrent strategic work as an Independent Director at the national cyber operator (JSC “State Technical Service”)—on projects such as \emph{Synaq} (security testing portal), \emph{ScanKZ} (national exposure monitoring) and an internal cyber media-monitoring bot. % (DOCX source)

% The work involves defining security requirements, prioritizing features, coordinating multi-team delivery, setting acceptance criteria and measuring impact—product management applied to cybersecurity platforms and operations.

% Kaspersky is an internationally known cybersecurity company; its signed commendation constitutes professional recognition with \emph{international} scope. The company’s independent standing is evidenced by:
% \begin{itemize}
%   \item \textbf{BBC News coverage:} \ParagraphQuoteByExhibit{``Kaspersky identified the state-level ‘Flame’ malware … one of the most complex threats ever discovered.''}{BBC News report referencing work with the UN’s ITU — excerpt}{KasperskyBBC}
%   \item \textbf{AV-TEST Awards (2024):} \ParagraphQuoteByExhibit{``Kaspersky stood out in numerous tests in 2024, receiving a total of nine awards.''}{AV-TEST Institute — awards summary}{KasperskyLabsAwards}
%   \item \textbf{SE Labs (Q1–2024):} \ParagraphQuoteByExhibit{``Achieved 100\% Protection Accuracy, 100\% Legitimate Accuracy and 100\% Total Accuracy.''}{SE Labs, \emph{Endpoint Security: Small Business Protection}}{KasperskySELabs2024}
% \end{itemize}
% Accordingly, a personally addressed, signed certificate of appreciation from an independent, internationally recognized cybersecurity vendor such as Kaspersky constitutes a \emph{lesser internationally recognized award for excellence} and is probative of Mr.~Taximov’s distinction in the field.

% \SubSubSubSection{Conclusion}
% Taken together, the personally addressed, signed and sealed commendation and Kaspersky’s independently attested international standing provide credible, third–party recognition of Mr.~Taximov’s leadership impact on security–critical digital platforms. This honor is independent of his employing entity and grounded in concrete contributions described above. It therefore satisfies USCIS Criterion~1 for lesser internationally recognized awards and reinforces the broader pattern of sustained professional acclaim documented in this petition.

\subsubsection{Certificate of Appreciation for Contributions to Information Security. Kaspersky Lab International (2022)}

Kaspersky Lab’s Central Asia office issued Mr. Taximov a signed and sealed Certificate of Appreciation recognizing his contribution to the development of the information-security sector (also in connection with the professional holiday of Digitalization and IT Workers).

“Certificate of Appreciation … for contribution to the development of the information security industry.”

The basis for the recognition aligns with Mr. Taximov’s cybersecurity leadership in practice:

\begin{itemize}

  \item Improving the iKOMEK109 digital ecosystem: implementing robust protection and monitoring tools on a city-wide, 24/7 digital platform.
  \item Public-private cooperation: partnering with leading suppliers and integrators to improve the resilience of critical municipal services.
  \item Institutionalization of incident response practices: standards and guidelines for public/quasi-public organizations, including measures to ensure confidentiality and data protection.
  \item Promoting digital literacy and security by design: extensive information and awareness-raising activities to improve the security of public information systems.

\end{itemize}


These activities are consistent with Mr. Taximov’s concurrent strategic work as an Independent Director at the national cyber operator (JSC “State Technical Service”)—on projects such as Synaq (security testing portal), ScanKZ (national exposure monitoring) and an internal cyber media-monitoring bot.


The work involves defining security requirements, prioritizing features, coordinating delivery across multiple teams, setting acceptance criteria, and measuring impact. Essentially, this is product management applied to cybersecurity platforms and operations.


Kaspersky is an internationally known cybersecurity company; its signed commendation constitutes professional recognition with international scope. The company’s independent standing is evidenced by:



\begin{itemize}
  \item BBC News coverage: “Kaspersky identified the state-level ‘Flame’ malware … one of the most complex threats ever discovered.” (BBC News report referencing work with the UN’s ITU )
  \item AV-TEST Awards (2024): “Kaspersky stood out in numerous tests in 2024, receiving a total of nine awards.” 
  \item SE Labs (Q1–2024): “Achieved 100\% Protection Accuracy, 100\% Legitimate Accuracy and 100\% Total Accuracy.” (SE Labs, Endpoint Security: Small Business Protection)
\end{itemize}


Accordingly, a personally addressed, signed certificate of appreciation from an independent, internationally recognized cybersecurity vendor such as Kaspersky constitutes a lesser internationally recognized award for excellence and is probative of Mr. Taximov’s distinction in the field.







% =========================================================
% MAYOR — HONORARY DIPLOMA (2022)
% =========================================================
% \subsubsection{Mayor of Astana — ``Honorary Diploma'' for the 2022 Presidential Election}

% The Mayor of Astana conferred an \emph{Honorary Diploma} recognizing \emph{activity, high professionalism and organizational skill} during the preparation and conduct of the 2022 extraordinary presidential election. The commendation is personally addressed, signed and sealed. % (DOCX source)

% \ParagraphQuoteByExhibit{``For activity, high professionalism and organizational skill in organizing and conducting the extraordinary Presidential election of the Republic of Kazakhstan.''}{Mayor of Astana, Honorary Diploma (2022) — Eng. transl.}{AkimKurmet2022}

% \SubSubSubSection{City-scale execution recognized by the Mayor}
% The diploma reflects citywide execution led by Mr.~Taximov:
% \begin{itemize}
%   \item technical organization and updating of the voter database (verification and automated precinct assignment of citizens through registration address codes) by using IT technologies;
%   \item collaborative correction of overcrowded registration addresses with district administrations and the migration service to ensure data veracity;
%   \item formation and agreement of voter lists with district mayors’ offices and territorial commissions;
%   \item development of digital services (online polling place, analysis of voter inquiries) to support residents during the election;
%   \item establishment of a unified election call center at iKOMEK109; operator training and knowledge-base content creation.
% \end{itemize}
% Collectively, these IT measures improved accuracy, transparency and citizen trust in the electoral process. % (DOCX source)

% Owning the roadmap and delivery of mission-critical civic products (voter data services, contact-center operations) across multiple agencies and constraints is a direct application of product leadership.

% Although conferred by the capital’s chief executive, the distinction honors work performed for a \emph{national} electoral event; it is widely recognized within the country and sector.

% \ExhibitList{\ExhibitRef{AkimKurmet2022}}

\subsubsection{“Honorary Diploma” for the Presidential Election. Mayor of Astana (2022)}

The Mayor of Astana conferred an Honorary Diploma recognizing high professionalism and organizational skill during the preparation and conduct of the 2022 extraordinary presidential election. The commendation is signed and sealed.

“For active involvement, high professionalism, and for organizing and conducting the extraordinary Presidential election of the Republic of Kazakhstan.”

The diploma is awarded for  Mr. Taximov' citywide execution:

\begin{itemize}

  \item Technical organization and updating of the voter database (verification and automatic distribution of citizens to polling stations based on their registration address codes) using IT technologies.

  \item Correction of overcrowded registration addresses in cooperation with district administrations and the migration service to ensure data accuracy.

  \item Formation and coordination of voter lists with district administrations and territorial commissions.

  \item Development of digital services (online polling station, analysis of voter requests) to support residents during elections.

  \item Creation of a unified election call center in iKOMEK109 and training of operators and creation of a knowledge base.

\end{itemize}


Collectively, these systematic measures improved accuracy, transparency and citizen trust in the electoral process.

Owning the roadmap and delivery of mission-critical civic products (voter data services, contact-center operations) across multiple agencies and constraints is a direct application of product leadership.

Although conferred by the capital’s chief executive, the distinction honors work performed for a national electoral event. It is widely recognized within the country and sector.





% =========================================================
% MAYOR — DIGITALIZATION DAY (2022)
% =========================================================
% \subsubsection{Mayor of Astana — Letter of Appreciation for the Day of Digitalization and IT Workers (2022)}
% \label{subsubsec:AkimAlgys2022}

% Mr.~Taximov received an official \emph{Letter of Appreciation} from the Mayor of Astana for contributions to the development of the city’s digital infrastructure and for the introduction of modern technologies into city management (in honor of the Day of Digitalization and IT Workers). % (DOCX source)

% \ParagraphQuoteByExhibit{``I sincerely congratulate you on the Day of Digitalization and Information Technology Workers … I thank you for your contribution to the development of our city’s information technology sector.''}{Mayor of Astana, Letter of Appreciation (2022) — Eng. transl.}{AkimAlgys2022}

% \SubSubSubSection{Digital initiatives recognized by the Mayor}
% As Head of iKOMEK109 in 2022, Mr.~Taximov led:
% \begin{itemize}
%   \item \textbf{Expansion of digital feedback channels} with residents (mobile app, Telegram bots, social networks), enabling 24/7 submissions on utilities, maintenance and public safety;
%   \item \textbf{Strengthening of information security system} across the contact center and online services, protecting personal data and service continuity;
%   \item \textbf{Automation of request processing:} transition from a traditional call center to an intelligent analytics-driven platform, improving speed and transparency;
%   \item \textbf{Big-Data decision support} for the Mayor’s Office (dashboards, analytics) to guide incident response and infrastructure planning.
% \end{itemize}
% These improvements enhanced quality of life, increased reliability of city infrastructure and strengthened Astana’s position as a regional leader in digitalization. % (DOCX source)

% The outcomes reflect classic product leadership: multi-channel UX, backlog/roadmap control, security and reliability requirements, KPI-driven responsiveness and stakeholder alignment at the city executive level.

% A formal mayoral commendation in the country's capital is a recognized governmental award at the national center of administration.

% \ExhibitList{\ExhibitRef{AkimAlgys2022}}


% % =========================================================
% % Exhibits referenced in this section
% % =========================================================
% \ExhibitRef{PresAlghys2024}
% \ExhibitRef{PresAlghys2022}

\subsubsection{Letter of Appreciation for the Day of Digitalization and IT Workers. Mayor of Astana  (2022)}

Mr. Taximov received an official Letter of Appreciation from the Mayor of Astana for contributions to the development of the city’s digital infrastructure and for the introduction of modern technologies into city management (in honor of the Day of Digitalization and IT Workers).

“I sincerely congratulate you on the Day of Digitalization and Information Technology Workers … I thank you for your contribution to the development of our city’s information technology sector.”

As Head of iKOMEK109 in 2022, Mr. Taximov led:

\begin{itemize}

\item Expansion channels for digital feedback by citizens(mobile app, Telegram bots, social networks), allowing 24/7 appeals for utilities, technical maintenance, and public safety.
\item Strengthening the information security system in the contact center and online services, protecting personal data, and ensuring continuity of service.
\item Automating request processing: transitioning from a traditional call center to an analytical intelligent platform, increasing speed and transparency.
\item Development of dashboards and analytics to support city hall's management of incident response and infrastructure planning.

\end{itemize}

These improvements increased reliability of city infrastructure and strengthened Astana’s position as a regional leader in digitalization.

The outcomes reflect classic product leadership: multi-channel UX, backlog/roadmap control, security and reliability requirements, KPI-driven responsiveness and stakeholder alignment at the city executive level.

A formal mayor's commendation in the country's capital is a recognized governmental award at the national center of administration.


\pagebreak