\section{Final Merits Determination of \mrls Extraordinary Ability}
\label{sec:FinalMerits}

Consistent with USCIS (U.S.\ Citizenship and Immigration Services) guidance, this section evaluates the record \emph{as a whole} to determine whether \mrl{} has sustained national (or international) acclaim and risen to the small percentage at the very top of his field. 

\subsection{Presidential-Level Honors and Broad National Recognition}

\textbf{Presidential Letter of Appreciation for the Presidential Election (Elections, 2022).}
In November~2022, \mrl{} received a formal \emph{Presidential Letter of Appreciation} signed by \textbf{Kassym\kern0.08em-Jomart Tokayev}, President of the Republic of Kazakhstan, for a significant contribution to the preparation and conduct of the country’s extraordinary presidential election. \ExhibitRef{PresAlghys2022}
\ParagraphQuoteByExhibit{``I thank you for your significant contribution to the preparation and conduct of the Presidential election of the Republic of Kazakhstan.''}{President of Kazakhstan, Letter of Appreciation (2022) Eng.\ transl.}{PresAlghys2022}

The commendation corresponds to \mrls direction of a citywide data-governance and technology program to ensure accuracy, transparency and security in the capital’s electoral roll (integration of the \emph{Geonomics—Population Database} with state registries; automated polling-station attachment; identification of overcrowded registrations; unified call center and online voter tools; election-period analytics). \ExhibitRef{PresAlghys2022}

\textbf{Presidential Letter of Appreciation (SCO Summit, 2024).}
A second personally addressed, signed Letter of Appreciation from the \textbf{President of the Republic of Kazakhstan} commends \mrls contribution to the 2024 Shanghai Cooperation Organization (SCO) Summit in Astana, tied to his mission-critical leadership at the capital’s monitoring and rapid-response center (iKOMEK 109). \ExhibitRef{PresAlghys2024} This is direct national-level recognition that he was entrusted with high-profile, high-risk responsibilities and performed to the standard expected by the head of state.

\textbf{“Bolashak” Presidential Scholarship (2013–2014).}
The record documents \mrls selection for the \textbf{Bolashak International Scholarship of the President of the Republic of Kazakhstan}. Financial-guarantee letters to \textbf{the University College London (UCL)} and the British Embassy, together with governing decrees, confirm individual receipt via a competitive, expert-screened process and substantial support (tuition, travel, stipend, books, insurance). The acquired award further connects his UCL Master of Science (MSc degree) dissertation (Spatial Decision Support Systems, \emph{SDSS}) that paves the way to his leadership in the information technology (IT) industry.

\medskip
\noindent\textbf{National and Industrial commendations.}
To contextualize the continuity of \emph{national recognition} beyond head-of-state awards, the record also includes:
\begin{itemize}
  \item a \textbf{commendation from Kaspersky Lab (2022)} evidencing favorable evaluation by a global cybersecurity vendor for contributions aligned with national cyber priorities;
  \item \textbf{Honorary Diploma (2022) and Letter of Appreciation (2022) from the Mayor of Astana} formally recognizing citywide digital-operations leadership during the presidential election and municipal digitalization initiatives.
\end{itemize}


% =========================================================
% KASPERSKY (INTERNATIONAL) — APPRECIATION (2022)
% =========================================================
\subsubsection{Kaspersky Lab (International) — Certificate of Appreciation for Contributions to Information Security (2022)}
\label{subsubsec:KasperskyThanks2022}

\SubSubSubSection{What was awarded and how it was earned}
Kaspersky Lab’s Central Asia office issued Mr.~Taximov a signed and sealed \emph{Certificate of Appreciation} recognizing his contribution to the development of the information-security sector (also in connection with the professional holiday of Digitalization and IT Workers). % (DOCX source)

\ParagraphQuoteByExhibit{``Certificate of Appreciation … for contribution to the development of the information security industry.''}{Kaspersky Lab (Central Asia), Certificate of Appreciation (2022) — Eng. transl.}{KasperskyThanks2022Ex}

\SubSubSubSection{Cybersecurity leadership recognized by an international company}
The basis for the recognition aligns with Mr.~Taximov’s cybersecurity leadership in practice:
\begin{itemize}
  \item \textbf{Strengthening the iKOMEK109 digital ecosystem:} deployment of modern protection and monitoring tools across a 24/7 city-scale digital platform;
  \item \textbf{Public–private cooperation:} partnerships with leading vendors and integrators to improve resilience of critical municipal services;
  \item \textbf{Institutionalization of incident-response practices:} standards and playbooks for government/quasi-government organizations, including privacy and data-protection measures;
  \item \textbf{Digital literacy and secure-by-design promotion:} broad outreach to enhance security postures across state information systems.
\end{itemize}
These activities are consistent with Mr.~Taximov’s concurrent strategic work as an Independent Director at the national cyber operator (JSC “State Technical Service”)—on projects such as \emph{Synaq} (security testing portal), \emph{ScanKZ} (national exposure monitoring) and an internal cyber media-monitoring bot. % (DOCX source)

\SubSubSubSection{Why this is in the field (product leadership)}
The work involves defining security requirements, prioritizing features, coordinating multi-team delivery, setting acceptance criteria and measuring impact—product management applied to cybersecurity platforms and operations.

\SubSubSubSection{Why this is a \emph{lesser internationally recognized} award}
Kaspersky is an internationally known cybersecurity company; its signed commendation constitutes professional recognition with \emph{international} scope. The company’s independent standing is evidenced by:
\begin{itemize}
  \item \textbf{BBC News coverage:} \ParagraphQuoteByExhibit{``Kaspersky identified the state-level ‘Flame’ malware … one of the most complex threats ever discovered.''}{BBC News report referencing work with the UN’s ITU — excerpt}{KasperskyBBC}
  \item \textbf{AV-TEST Awards (2024):} \ParagraphQuoteByExhibit{``Kaspersky stood out in numerous tests in 2024, receiving a total of nine awards.''}{AV-TEST Institute — awards summary}{KasperskyLabsAwards}
  \item \textbf{SE Labs (Q1–2024):} \ParagraphQuoteByExhibit{``Achieved 100\% Protection Accuracy, 100\% Legitimate Accuracy and 100\% Total Accuracy.''}{SE Labs, \emph{Endpoint Security: Small Business Protection}}{KasperskySELabs2024}
\end{itemize}
Accordingly, a personally addressed, signed certificate of appreciation from an independent, internationally recognized cybersecurity vendor such as Kaspersky constitutes a \emph{lesser internationally recognized award for excellence} and is probative of Mr.~Taximov’s distinction in the field.

\SubSubSubSection{Conclusion}
Taken together, the personally addressed, signed and sealed commendation and Kaspersky’s independently attested international standing provide credible, third–party recognition of Mr.~Taximov’s leadership impact on security–critical digital platforms. This honor is independent of his employing entity and grounded in concrete contributions described above. It therefore satisfies USCIS Criterion~1 for lesser internationally recognized awards and reinforces the broader pattern of sustained professional acclaim documented in this petition.





% =========================================================
% MAYOR — HONORARY DIPLOMA (2022)
% =========================================================
\subsubsection{Mayor of Astana — ``Honorary Diploma'' for the 2022 Presidential Election}

\SubSubSubSection{What was awarded and how it was earned}
The Mayor of Astana conferred an \emph{Honorary Diploma} recognizing \emph{activity, high professionalism and organizational skill} during the preparation and conduct of the 2022 extraordinary presidential election. The commendation is personally addressed, signed and sealed. % (DOCX source)

\ParagraphQuoteByExhibit{``For activity, high professionalism and organizational skill in organizing and conducting the extraordinary Presidential election of the Republic of Kazakhstan.''}{Mayor of Astana, Honorary Diploma (2022) — Eng. transl.}{AkimKurmet2022}

\SubSubSubSection{City-scale execution recognized by the Mayor}
The diploma reflects citywide execution led by Mr.~Taximov:
\begin{itemize}
  \item technical organization and updating of the voter database (verification and automated precinct assignment of citizens through registration address codes) by using IT technologies;
  \item collaborative correction of overcrowded registration addresses with district administrations and the migration service to ensure data veracity;
  \item formation and agreement of voter lists with district mayors’ offices and territorial commissions;
  \item development of digital services (online polling place, analysis of voter inquiries) to support residents during the election;
  \item establishment of a unified election call center at iKOMEK109; operator training and knowledge-base content creation.
\end{itemize}
Collectively, these IT measures improved accuracy, transparency and citizen trust in the electoral process. % (DOCX source)

\SubSubSubSection{Why this is in the field (product leadership)}
Owning the roadmap and delivery of mission-critical civic products (voter data services, contact-center operations) across multiple agencies and constraints is a direct application of product leadership.

\SubSubSubSection{Why this is a \emph{lesser nationally recognized} award}
Although conferred by the capital’s chief executive, the distinction honors work performed for a \emph{national} electoral event; it is widely recognized within the country and sector.

\ExhibitList{\ExhibitRef{AkimKurmet2022}}


% =========================================================
% MAYOR — DIGITALIZATION DAY (2022)
% =========================================================
\subsubsection{Mayor of Astana — Letter of Appreciation for the Day of Digitalization and IT Workers (2022)}
\label{subsubsec:AkimAlgys2022}

\SubSubSubSection{What was awarded and how it was earned}
Mr.~Taximov received an official \emph{Letter of Appreciation} from the Mayor of Astana for contributions to the development of the city’s digital infrastructure and for the introduction of modern technologies into city management (in honor of the Day of Digitalization and IT Workers). % (DOCX source)

\ParagraphQuoteByExhibit{``I sincerely congratulate you on the Day of Digitalization and Information Technology Workers … I thank you for your contribution to the development of our city’s information technology sector.''}{Mayor of Astana, Letter of Appreciation (2022) — Eng. transl.}{AkimAlgys2022}

\SubSubSubSection{Digital initiatives recognized by the Mayor}
As Head of iKOMEK109 in 2022, Mr.~Taximov led:
\begin{itemize}
  \item \textbf{Expansion of digital feedback channels} with residents (mobile app, Telegram bots, social networks), enabling 24/7 submissions on utilities, maintenance and public safety;
  \item \textbf{Strengthening of information security system} across the contact center and online services, protecting personal data and service continuity;
  \item \textbf{Automation of request processing:} transition from a traditional call center to an intelligent analytics-driven platform, improving speed and transparency;
  \item \textbf{Big-Data decision support} for the Mayor’s Office (dashboards, analytics) to guide incident response and infrastructure planning.
\end{itemize}
These improvements enhanced quality of life, increased reliability of city infrastructure and strengthened Astana’s position as a regional leader in digitalization. % (DOCX source)

\SubSubSubSection{Why this is in the field (product leadership)}
The outcomes reflect classic product leadership: multi-channel UX, backlog/roadmap control, security and reliability requirements, KPI-driven responsiveness and stakeholder alignment at the city executive level.

\SubSubSubSection{Why this is a \emph{lesser nationally recognized} award}
A formal mayoral commendation in the country's capital is a recognized governmental award at the national center of administration.

\ExhibitList{\ExhibitRef{AkimAlgys2022}}



These awards are presented here to demonstrate \emph{continuity of national and industrial recognition}; they are distinct from and complementary to the presidential-level distinctions above.

\subsection{Institutional recognition within a leading academic and innovation ecosystem (ENU)}

Beyond head-of-state acknowledgments, Kazakhstan’s top academic institutions repeatedly recognize \mrls authority in his field.

\textbf{Permanent reviewer for ENU’s scientific journal.}
L.N.~Gumilyov Eurasian National University (ENU) formally confirmed that \mrl{} “\emph{is indeed a reviewer of the scientific journal ‘Vestnik ENU’ and on a permanent basis participates in the evaluation of scientific articles}” on topics including information and innovative technologies, IT trends, data science and analytics, with accept/revise/reject outcomes grounded in novelty and practical significance. \ExhibitRef{ENUReviewer}

\textbf{ENU expert invitation and alumni interview.}
ENU’s Endowment Fund issued an expert invitation to the \emph{IV International Endowment Forum: “Digitalization and Technological Innovations in the Management of Endowment Funds”} (1~Oct~2024), citing \mrls “\emph{enormous experience in IT project management}.” \ExhibitRef{ENUInvite}\ExhibitRef{ENUForumProgram}
ENU’s Media Club recorded and published an interview with \mrl{} as a distinguished alumnus and head of iKOMEK 109, positioning his role within national digital-transformation narratives (unified 1-0-9 services, chatbots and digital channels). \ExhibitRef{ENUMediaClubInterview}

\midskip
\textbf{ENU standing in QS World University Rankings.}

For context, L.N.\ Gumilyov ENU has demonstrated consistent excellence in international university rankings over more than a decade. The university was the \textbf{first Kazakhstani institution to enter the QS (Quacquarelli Symonds) World University Rankings top 400} when it achieved \textbf{369th place in 2012}. Since then, ENU has maintained its position within the top 400 worldwide, with its \textbf{most recent ranking of 317th place in \emph{QS World University Rankings 2026: Top global universities}}, representing continued improvement and international recognition.

In regional rankings, ENU holds the \textbf{\#2 position in Central Asia} according to the \emph{QS Asia University Rankings 2025}, demonstrating its leading role among Central Asian universities. The university has shown remarkable consistency in subject-specific rankings.

ENU's sustained performance across multiple ranking cycles from 2012 through 2026 and its achievement of top-tier status in specialized subject areas contextualizes the weight of ENU's institutional recognitions throughout this record.

\subsection{Independent expert testimony}

% The record includes detailed letters from qualified professionals with \emph{independent vantage points}. Each letter explains the author’s authority, the concrete problem addressed and Mr.~Taximov’s technical/managerial contribution.

\textbf{Dr.~Shyngys Kenshimov (PhD; Associate Professor).}
In his letter, Dr.~Kenshimov underscores Mr.~Taximov’s role in shaping product direction and architecture (market needs, product concepts, research-team guidance) and documents concrete outcomes in computer vision and city traffic analytics, including a reported accuracy gain of 15\%.

\noindent\emph{As stated in the letter:}
\begingroup
\sloppy\setlength{\emergencystretch}{3em}%
\ParagraphQuoteByExhibit{“Askar is a \HL{true professional in information technology and innovative development}. His contribution to digitalization and to integrating cutting-edge technologies has \HL{long-term impact}. Askar Taximov provided \HL{invaluable assistance} in the formation and development of our startups—ABY Applied Systems and Verigram. He \HL{identified market needs}, \HL{developed product concepts}, \HL{set technical direction} for the research group, offered \HL{consulting support} and \HL{helped recruit high-caliber specialists}. Thanks to his \HL{strategic recommendations} and professional approach, we \HL{brought products to the next level} and \HL{strengthened our market position}. He also created an \HL{effective data pipeline} (auto-labeling → model training → integration into commercial solutions) that \HL{improved model prediction accuracy by 15\%}, raising product quality and customer satisfaction. I am confident his \HL{specialized expertise}, \HL{strategic thinking} and \HL{innovative solutions} will achieve high results in the development of IT technologies.”}{KenshimovLetter}
\endgroup

\noindent Dr.~Kenshimov’s testimony is technically specific (frameworks, deployment model, microservices, production pipeline) and \emph{metric-bearing} (\textbf{+15\%} accuracy), directly tying Mr.~Taximov to outcomes that indicate field-level significance and repeatability in operational machine-learning deployments.

\medskip

\textbf{Kakhar Kashimov (CTO; Chief Software Architect).}
Mr.~Kashimov(MSc in Visual Information Processing, Machine Learning. Imperial College London) in his letter highlights co-founding work with Mr.~Taximov on wireless geophone sensor networks and the “Life Signal” emergency-location workflow, emphasizing end-to-end architecture and the translation of research (SDSS) into city-scale systems with public-safety impact.

\noindent\emph{As he writes:}

\begingroup
\sloppy\setlength{\emergencystretch}{3em}%
\ParagraphQuoteByExhibit{“Mr. Taximov co-founded a startup with me to build \HL{wireless Wi-Fi geophone arrays} for seismic prospecting, developing a \HL{two-tier high-throughput wireless design}, \HL{satellite-based positioning with cooperative localization} and \HL{time synchronization} so sensors record in step. He also led an end-to-end public-safety integration nicknamed \HL{‘Life Signal’} that links a caller’s device to \HL{112 dispatch centers and mobile operators for precise geolocation}. He is a \HL{strategic and technical leader} who \HL{translates research concepts into city-scale solutions} that \HL{improve public safety and digital governance}. These qualities will enable him to \HL{contribute strongly to U.S. Smart City and IT security programs}.”}{KaharLetter}
\endgroup

\noindent This independent account documents \emph{cross-domain systems engineering} (industrial sensing ↔ public safety) and demonstrates \emph{deployment beyond a single employer}, a persuasive indicator of field-wide impact.

\medskip

\textbf{Azamat Sanatov (Department of Information Resources Protection, Presidential Administration).}
Mr.~Sanatov provides a government-operations perspective, crediting Mr.~Taximov with measurable cybersecurity and infrastructure outcomes (Data Loss Prevention policy and incident response; 17\%/28\% risk reductions; 99.99\% fault tolerance; next-generation firewalls at 11 agencies; data-center reliability) and recommending him as a top expert.

\noindent\emph{As stated in the letter:}

\begingroup
\sloppy\setlength{\emergencystretch}{3em}%
\ParagraphQuoteByExhibit{``At that time, I unequivocally noted Askar's \HL{professional competence in information and cybersecurity}, which are \HL{key sectors} for our country. The projects described above demonstrate \HL{high technical and professional competence} and show his \HL{expert role} in solving current tasks in the development of information-technology systems. During the \HL{development of a DLP system} to protect data for \HL{second-tier banks}, Askar was responsible for the \HL{technical and methodological} components: he \HL{developed the DLP policy} (data-classification criteria; acceptable-use policy), \HL{incident/DDoS response procedures}, measures to \HL{prevent data leakage} (flow controls) and \HL{regular review and software updates}. As a result, financial institutions \HL{reduced incidents of illegal external data transfers by 17\%}, \HL{reduced undesired destruction of personal data by an average of 28\%} and \HL{improved support response times from 60 to 15 minutes}. Askar also proposed a \HL{modern structured cabling network} and recommended \HL{100\,Gb/s Ethernet switches}, which \HL{increased network fault tolerance to 99.99\%} and accelerated intra–data-center traffic. One of Askar's \HL{significant contributions} to the \HL{improvement and development of the IT sector} was the \HL{design and implementation of the digital project "Data Processing Center,"} which ensured \HL{high fault tolerance and uninterrupted operation} of the \HL{IT infrastructure of government agencies}, as well as \HL{information systems that are key components of e-government}. I would also like to note that Askar \HL{made substantial contributions} to his \HL{professional field in information technology and digitalization} through the development of his own practical methodologies and guidelines on \critical issues in the IT industry, which were reflected in his scientific and practical articles.''}{SanatovLetter}
\endgroup

\noindent \textit{Abbreviations used in the excerpt:} DLP = Data Loss Prevention; DDoS = Distributed Denial of Service; Gb/s = gigabits per second.

% \noindent Mr.~Sanatov’s senior-government vantage point and the quantified outcomes he cites—\textit{17\%} fewer illicit data transfers, \textit{28\%} fewer unwanted data destructions, \textit{60$\to$15 minutes} support-response improvement, \textit{99.99\%} network fault tolerance, \textit{11} agencies secured—provide operations-based corroboration of Mr.~Taximov’s leadership in IT project management, cybersecurity architecture and large-scale government infrastructure modernization.

\medskip

\textbf{A.~Zhunisbek (Chairman of the Board, State Technical Service JSC).}
Chairman Zhunisbek’s statement links Mr.~Taximov by name to national-level information-security deployments and improved resilience of the Kazakhstani Internet segment.

\noindent\emph{As he states:}

\begingroup
\sloppy\setlength{\emergencystretch}{3em}%
\ParagraphQuoteByExhibit{“In carrying out the assigned tasks, Askar\ Taximov demonstrated a \HL{high level of analytical thinking and professionalism}; his \HL{technical knowledge and innovative approach} made it possible to achieve the set goals and \HL{improve the effectiveness} of JSC ‘STS’. He played a \HL{key role in the development and implementation of information-security systems at the national level} and had a \HL{tangible impact on increasing the resilience and efficiency of the Kazakhstani segment of the Internet}.”}{STSContribution}
\endgroup


% \noindent This board-level assessment links Mr.~Taximov personally to \emph{national-level} security implementations and measurable \emph{resilience} outcomes, reinforcing independent, outcome-based recognition.

\subsection{Unsolicited invitations to participate as an expert in nationally significant forums}

Governmental and sector organizations repeatedly seek \mrls participation for plenary and panel roles within his specialization, which indicates that his expertise is \emph{recognized and appreciated by field practitioners}, as follows: 
\begin{itemize}
  \item \emph{Iteca / ICA Events Company} invited \mrl{} personally to the \textbf{Plenary Session} \emph{“Interaction between the state and business to ensure the security of cities in Kazakhstan”} at the Securex Kazakhstan Exhibition, March~2024, Almaty. \ExhibitRef{SecurexInvite2024};
  \item MOST Hub Almaty (in partnership with the \emph{Ministry of Defense of the Republic of Kazakhstan}) invited \mrl{} and his organization “\emph{as experts in IT and contact-center feedback to citizens from government agencies}” for a defense-sector digitalization panel, March~2023, Almaty. \ExhibitRef{MOSTMoDInvite2023};
  \item The \emph{Deputy Mayor of Zhambyl Region} invited \mrl{} personally \textbf{as a panel speaker} for the \emph{Situation Center} panel at \emph{Google DevFest}, November~2023, Taraz. \ExhibitRef{DevFestTarazInvite2023};
  % \item \textbf{Digital Almaty 2023} — annual international forum on digital transformation (“Digital partnership in a new reality”); EAEU (Eurasian Economic Union) prime-ministerial plenary; exhibition and Digital Almaty Awards (2--3~Feb~2023, Almaty). \ExhibitRef{MDDADADigitalAlmaty2023};
  % \item \textbf{Digital Almaty 2024} — large-scale “Industry~X” forum with EAEU prime-ministerial plenary, SCO Digital Forum, sector panels and themed districts/exhibitions (1--3~Feb~2024, Almaty). \ExhibitRef{TechGardenDA2024};
  % \item \textbf{KazHackStan 2024} — Central Asia's largest practical cybersecurity conference; 6{,}000+ visitors, 30+ international speakers; CyberKumbez attack/defense competition with smart-city simulations (11--13~Sep~2024, Almaty). \ExhibitRef{KazHackStan2024Invite}
  \item The \emph{Ministry of Digital Development, Innovations and Aerospace Industry of the Republic of Kazakhstan} invited \mrl{} (iKOMEK~109) to \textbf{participate} in the \emph{Digital Almaty 2023} forum (2--3~Feb~2023, Almaty). \ExhibitRef{MDDADADigitalAlmaty2023} 
  \item \emph{Almaty Tech Garden (Tech Garden)} invited \mrl{} and representatives of iKOMEK~109 to \textbf{take part} in the \emph{Digital Almaty 2024 (``Industry~X'')} forum (1--3~Feb~2024, Almaty). \ExhibitRef{TechGardenDA2024} 
  \item \emph{TsARKA — Center for Analysis and Investigation of Cyberattacks} invited iKOMEK~109 and its specialists to \textbf{participate} in \emph{KazHackStan~2024} (11--13~Sep~2024, Almaty). \ExhibitRef{KazHackStan2024Invite}
\end{itemize}

\subsection{National media reporting} Independent press and broadcast records show that \mrl{} is identified publicly as a leading figure in Kazakhstan’s IT-governance ecosystem. 

\textbf{\emph{Forbes Kazakhstan}.} 
On \textbf{29~June~2022}, \emph{Forbes Kazakhstan} reported that by order of the municipal agency (\emph{Administration for Control and Quality of the Urban Environment of Astana}), Mr.~Taximov was appointed head of the Center for Monitoring and Rapid Response (iKOMEK 109). The article notes the \emph{Presidential Bolashak Scholarship}, his University College London education, and his executive roles at Nazarbayev University Technopark \emph{within the Nazarbayev University Research and Innovation System (NURIS, 2018–2019)} and Astana Innovations JSC (2019–2021). \ExhibitRef{ForbesKZ2022} (URL: \href{https://forbes.kz/news/newsid_279040}{https://forbes.kz/news/newsid\_279040})

\textbf{\emph{HubTalks} (Digital Bridge 2023).} 
A recorded \emph{HubTalks} discussion titled “Smart City at Digital Bridge 2023” features \mrl{} as the capital’s municipal digital-operations representative, addressing 24/7 intake, video monitoring, integration with transport and public-safety operators, startup interfaces and data-driven policy for traffic management, modal rebalancing and resource optimization. \ExhibitRef{HubTalksDB2023Transcript}

\subsection{Government-recognized software authorship "NextITSM"} \label{subsubsec:Merits_NextITSM} 
\textbf{State registration and authorship.} 
Kazakhstan’s National Copyright Office issued \textbf{Certificate No.~54827} dated \textbf{18~February~2025} for the software work titled \emph{NextITSM}, recording the \textbf{creation date} as \textbf{05~December~2024} and listing the \textbf{authors} as \emph{Anuar~Beisenbayev}, \emph{Askar~Taximov} and \emph{Bill~Seitkazin}. \ExhibitRef{NextITSMCertificate} 

\textbf{What it does (scope).} 
An Information Technology Infrastructure Library (ITIL)-aligned platform that \textbf{automates the full appeals and incident lifecycle} for public- and private-sector service organizations (registration → execution → monitoring → analytics), with service-level agreement (SLA) control, prioritization, lifecycle statuses, knowledge-base mailings, problem management, root-cause analysis, analytics and key performance indicators (KPIs), external integrations and role-based access. 

\textbf{How it’s built (stack).} 
Client–server architecture: \emph{Next.js/React} client; \emph{Node.js} server with \emph{tRPC} (TypeScript Remote Procedure Calls); \emph{PostgreSQL} via \emph{Prisma} object–relational mapping (ORM); \emph{MinIO} object storage; \emph{Tailwind CSS}; implemented in \textbf{TypeScript}; browser-delivered; deployable in \textbf{cloud}, \textbf{on-premises} or \textbf{hybrid} environments. 

\textbf{Public validation.}
The practical impact of NextITSM is demonstrated through its daily use across the entire iKOMEK 109 ecosystem among call-center operators, municipal service providers, and government agencies, and through results publicly reported in national media and the Astana Mayor's Office press center. In 2024, the system processed over 2{,}326{,}000 citizen appeals, achieving 82\% first-contact resolution, 98\% on-time referrals, integration of more than 12{,}000 integrated cameras and the introduction of AI-based predictive monitoring, with early-2025 figures showing continued growth. These results are not generic call-center statistics but a direct outcome of the automation, traceability and ITIL-aligned processes enabled by NextITSM.

% \textbf{State copyright certificate (NextITSM).} 
% Kazakhstan’s National Copyright Office issued \textbf{Certificate No.~54827} on \textbf{18~February~2025} for a “computer software” titled \emph{NextITSM}. The certificate lists the authors as \emph{Anuar~Beisenbayev, Askar~Taximov and Bill~Seitkazin} and records the creation date as \emph{5~December~2024}. \ExhibitRef{NextITSMCertificate} \textit{English translation of certificate excerpts:} “Certificate No.~54827, dated 18~February~2025. Type of copyright object: computer software. Title: NextITSM. Date of creation: 05~December~2024. Authors: Beisenbayev~A., Taximov~A., Seitkazin~B.”

\textbf{NextITSM's Functionality.} 
NextITSM is a comprehensive IT service-management platform that enables full-cycle automation of appeal registration, routing, processing and analytics within government and enterprise ecosystems. It provides data-driven tools for classifying and monitoring citizen appeals, enforcing service-level agreements and generating operational insights to support informed management decisions. Core functional areas include Appeal Management, Knowledge Base, Problem Management, Analytics and Reporting, and Administration modules that ensure transparency, accountability and measurable efficiency across all service workflows.

\subsection{Nationwide 'Population Database' Information System (Geonomics)}

\textbf{Election registries and address data (Geonomics).}
Within the Geonomics system for managing voter registries and address data in Astana, Mr.\ Taximov developed a Python-based data module that synchronized address records with the national Address Register, raising the official voter registry accuracy from 82\% to 100\%, as confirmed by the Central Election Commission of the Republic of Kazakhstan. This result and methodology were also documented in the 2024 \emph{Bulletin of Computer and Information Technologies} article titled "Use of information technologies in updating and forming address data." The system's successful deployment in the 2022 presidential election earned Mr.~Taximov a Letter of Appreciation from President Kassym-Jomart Tokayev for his significant contribution to election preparation and conduct (see \S\ref{subsubsec:PresElection2022}).
(DO NOT FORGET THE EXHIBITS)
% Repeated \emph{unsolicited} invitations to national forums and sector panels (Securex; MOST/Ministry of Defense; DevFest; Digital Almaty; KazHackStan) reflect that \mrls practical work on registry integrity, city platforms, analytics and cybersecurity is not only visible but also \emph{valued by domain experts} who lead these forums. \ExhibitRef{SecurexInvite2024}\ExhibitRef{MOSTMoDInvite2023}\ExhibitRef{DevFestTarazInvite2023}\ExhibitRef{TechGardenDA2024}\ExhibitRef{KazHackStan2024Invite}

\subsection{TV interview evidence of operational leadership—iKOMEK 109 (June 2022)}
In a June~17~2022 live broadcast of the television news and interview program “By Trends,” \mrl{} was presented as the newly appointed head of iKOMEK 109, responsible for service-quality management, staffing, digital-channel integration and interagency coordination. The hosts characterized iKOMEK 109 as modeled on U.S. 3-1-1 non-emergency unified service systems. In a media interview, \mrl{} described a daily number of \textbf{6,000 to 10,000} appeals, continuous \textbf{24/7} operations with \textbf{50–60} operators per shift within a team of \textbf{132} qualified specialists, multilingual service (Kazakh/Russian; English as needed) and coverage of life-support issues such as healthcare, public transport, seasonal matters and power outages, with urgent items registered and targeted for resolution within \textbf{24 hours}. He reported that social-media channels comprised \textbf{23\%} of all appeals and were increasing compared with the prior year. The broadcast further documented key performance indicator (KPI) frameworks (weekly analytics identifying top performers, a “Wall of Fame,” bonus incentives), staff-wellbeing measures (on-site psychologist, break room, supportive supervision), inclusive hiring (open to all population groups, including older workers and persons with disabilities) and compensation policy, which included a 25\% increase in operator base pay in June 2022. It highlighted the production of weekly analytics for the Mayor’s Office and surge planning by data scientists to forecast spikes around major events, with temporary staffing increases as needed. As to ecosystem integration, \mrl{} described approximately \textbf{12{,}000+} cameras citywide, of which about \textbf{3{,}500} are integrated for iKOMEK’s public-order and life-safety monitoring, with police staff co-monitoring on site;  He also discussed ongoing efforts to expand integration with homeowners' associations (Housing Owners Cooperation) amid current legal and organizational constraints. Additionally, he noted that the Police Department of Astana has transitioned to a service-oriented policing model, emphasizing high-quality public services and cooperation between law enforcement and residents to identify safety and security issues. A live “test call” during the program confirmed operator courtesy and boundaries of competence while surfacing an actionable improvement (faster language routing), which \mrl{} immediately logged for follow-up (script audits; accelerated menu options). Finally, he noted that iKOMEK 109 \emph{consults other cities across Kazakhstan} adopting the capital’s unified call-center model. \ExhibitRef{LiveInterview_IKomek109_Jun2022}

\subsection{Final Merits Conclusion}
\noindent Viewed in the \emph{totality} and under a \emph{preponderance of the evidence} standard, the record shows sustained national acclaim and top-of-field standing. Presidential-level honors (2022, 2024) and the Bolashak scholarship establish high-level recognition; institutional roles at a QS-ranked university (reviewer/invited expert) corroborate scholarly stature; independent expert letters detail \emph{specific technical mechanisms} and \emph{verifiable outcomes}; government press and official metrics attribute city-scale results to his leadership; and state-registered authorship of \emph{NextITSM}, together with repeated invitations to nationally significant forums. Therefore, Mr.~Taximov has \emph{risen to the small percentage at the very top of his field} and maintains \emph{sustained acclaim}.

\pagebreak