\subsection{%
    Evidence that \mrl has been asked to judge the work of others in the same or an allied field%
}
\label{subsec:Judging}

% USCIS Criterion~4 requires proof that the beneficiary was \emph{invited} to judge and \emph{actually participated} in judging the work of others in the same or allied field. The record below provides documentary evidence of both invitation and completed judging for two scholarly venues in information technology and adjacent disciplines.

% =========================================================
% AIU — scholarly peer review
% =========================================================
\subsubsection{Astana International University (AIU) — Permanent independent peer reviewer of the university journal}
\label{subsubsec:JudgingAIU}

\SubSubSubSection{Proof of invitation and the role assigned}
The President of Astana International University confirms on institutional letterhead that \mrl{} \emph{``is a permanent independent reviewer of the scientific journal of our university \textbf{International Science Reviews. Natural Sciences and Technologies series}.''} The letter specifies that, considering \mrls expertise in IT and innovation, he \emph{``considers and evaluates scientific works and articles in innovative and information-technology directions,''} including topics such as \emph{``use of Big Data in managing national companies; introduction of information technologies in startup projects; creation of technologies for data analysis in social projects; use of artificial intelligence in engineering systems; [and] the use of Data Science when forming information security.''} (English translation of the official letter). \ExhibitRef{AIUReviewer}

\SubSubSubSection{Proof of \emph{actual} judging (editorial decisions rendered)}
The same AIU letter describes the substantive peer-review functions performed by \mrl: he \emph{``assesses the relevance of the topic studied, the authenticity of the presented facts, the argumentation and clarity of the author's exposition and conclusions''} and, crucially, \emph{``formulates a decision on the admission of the article, the possibility or impossibility of publication in the above-mentioned journal, or the need for further revision.''} (English translation). \ExhibitRef{AIUReviewer}  
These statements evidence \textbf{actual participation} with publish / revise / decline outcomes, as required by USCIS.

\SubSubSubSection{Venue identity, scope, and periodicity (same or allied field)}
AIU’s journal portal identifies the reviewed venue as \emph{International Science Reviews. Natural Sciences and Technologies Series} with: \emph{``ISSN: 2707-4862; Owner: `Astana International University' LLP (Astana, Kazakhstan).''} Its thematic focus is explicitly \emph{``devoted to research in the field of natural sciences \dots as well as technologies such as information technology, information security, engineering, metallurgy, and oil and gas production and processing,''} and the periodicity is \emph{``4 times a year.''} \ExhibitRef{AIUScienceSite}  
Because the journal’s scope \textbf{expressly includes information technology and information security}, the works judged are in the same or allied field to \fie.

\SubSubSubSection{Institutional context (why the forum is professional)}
AIU’s own overview states the university’s mission is \emph{``to provide a high level of knowledge and competence, \dots through academic excellence, research and innovation to serve the nation and the world,''} and its vision is to be \emph{``a modern global university generating and disseminating knowledge, research and innovation for the Eurasian space.''} Among listed priorities are \emph{``conducting fundamental and applied research''} and training in \emph{``information and communication technologies.''} \ExhibitRef{AIUSite}  
This confirms that \mrl{} was entrusted with peer review in a \textbf{scholarly, research-driven venue}.

\SubSubSubSection{Why this satisfies USCIS Criterion~4 (AIU)}
The exhibits establish (i) formal \textbf{appointment} as a reviewer; (ii) \textbf{completed judging} with editorial recommendations; and (iii) a \textbf{direct connection to \fie} via the journal’s IT and information-security scope. \ExhibitRef{AIUReviewer,AIUScienceSite,AIUSite}

\bigskip

% =========================================================
% ENU — scholarly peer review
% =========================================================
\subsubsection{L.N.\ Gumilyov Eurasian National University (ENU) — Permanent reviewer of the university journal \emph{Vestnik ENU}}
\label{subsubsec:JudgingENU}

\SubSubSubSection{Proof of invitation and the role assigned}
The Department of Science and Commercialization of L.N.\ Gumilyov Eurasian National University confirms that \mrl{} \emph{``is indeed a reviewer of the scientific journal `Vestnik of L.N.\ Gumilyov Eurasian National University' and on a permanent basis participates in the evaluation of scientific articles''} on topics including \emph{``the introduction of information and innovative technologies in companies; trends in IT technologies and their effective influence on regional development; Data Science as an instrument to increase business profitability; SQL and Data analytics.''} (English translation of the official letter). \ExhibitRef{ENUReviewer}

\SubSubSubSection{Proof of \emph{actual} judging (criteria and outcomes)}
ENU specifies that \mrl{} reviews submissions for \emph{``scientific novelty, the relevance of the problem, scientific and practical significance of the research, depth of elaboration of the topic, style of presentation, and innovative approach to the scientific work,''} and, based on that assessment, \emph{``makes a conclusion on the advisability of publishing the article, or the need for rejection/revision.''} (English translation). \ExhibitRef{ENUReviewer}  
This demonstrates that \mrl{} \textbf{actually judged} manuscripts and issued accept / revise / reject decisions.

\SubSubSubSection{Institutional research profile (professional forum; allied field)}
ENU’s official \emph{Science} pages describe a large research ecosystem with \emph{``research divisions closely co-operate with faculties, university departments \dots schools of thought \dots [and] more than 160 scientific projects \dots under fundamental and applied programs of research,''} including \emph{``mathematical modeling and innovative technologies''} and \emph{``physicists and high technologies.''} \ExhibitRef{ENUScienceSite}  
The university overview further notes ENU’s status and international recognition, including memberships and accreditations, describing ENU as \emph{``a university with special status \dots an implementer of academic innovative technologies and continuer of the best research traditions.''} \ExhibitRef{ENUSite}  
Given the topics ENU assigned to \mrl{} (Data Science, SQL and analytics, IT trends and innovation), the peer-review work is plainly in the \textbf{same or allied field} to \fie.

\SubSubSubSection{Why this satisfies USCIS Criterion~4 (ENU)}
The exhibits provide (i) official \textbf{invitation and appointment}; (ii) evidence of \textbf{completed judging} with formal outcomes; and (iii) clear \textbf{field alignment} with computer science / IT / data analytics. \ExhibitRef{ENUReviewer,ENUScienceSite,ENUSite}

% =========================================================
% Public Foundation “ITeachMe” — OrleTECH jury & expert work
% =========================================================

\SubSubSubSection{Public Foundation ``ITeachMe'' — Independent Expert and Jury Member (OrleTECH finals)}
\label{subsubsec:JudgingITeachMeNew}

\paragraph{Proof of invitation and role.}
The Public Foundation ``ITeachMe'' (Center for Competence Development) formally invited \mrl{} to serve as an \textbf{honorary jury member} for the OrleTECH finals and awards ceremony. The 2024 invitation states (English translation): \textit{``We invite you to participate in the awards ceremony for OrleTECH graduates \dots also invite you to act as an \textbf{honorary member of the jury} during the defense of students' course projects. The defense and ceremony will take place on \textbf{28~November~2024} at \textbf{Wyndham Garden Astana}, conference hall `Altai'.''} \ExhibitRef{ITeachMeInvitation2024}. 
The 2023 invitation likewise asks \mrl{} \textit{``to take part in the final of the seventh season \dots and to become an honorary member of the jury''} with the venue/date specified as \textbf{Astana Hub, 02~November~2023, 16:30}. \ExhibitRef{ITeachMeInv2023} (see :contentReference[oaicite:2]{index=2}, :contentReference[oaicite:3]{index=3}, :contentReference[oaicite:4]{index=4}).

\paragraph{Proof of \emph{actual} judging.}
The official agenda shows \emph{defenses of course projects} before the jury across specific tracks. For 2023: \textit{``Room 1: UI/UX Design; Room 2: Motion Design; Room 3: SMM and copywriting; Room 4: Mobile videography; Room 5: Graphic design''} followed by the awards blocks. \ExhibitRef{ITeachMeInv2023} (see :contentReference[oaicite:5]{index=5}, :contentReference[oaicite:6]{index=6}). 
For 2024, the program explicitly lists the three juryed defenses: \textit{``1.~NoCode; 2.~UX/UI+Web Master; 3.~AI Specialist''} with \textit{``Presentation of jury members''} and jury meeting. \ExhibitRef{ITeachMeInvitation2024} (see :contentReference[oaicite:7]{index=7}, :contentReference[oaicite:8]{index=8}). 
Beyond invitations and programs, photographic and social-media records capture \mrl{} \emph{in the jury room during live defenses}. In his English-language caption he writes: \textit{``I participated as a member of the jury in iTeachMe \dots It was my responsibility \dots to evaluate [participants].''} \ExhibitRef{OrleJudgingInsta} (see also \ExhibitRef{OrleJudgingPhoto} for on-site photos).

\paragraph{Same or allied field of specialization.}
The juryed tracks—\textbf{NoCode}, \textbf{UX/UI + Web}, and \textbf{AI Specialist}—are squarely within computer science/IT and applied AI. The 2024 program labels these explicitly (English translation). \ExhibitRef{ITeachMeInvitation2024} (see :contentReference[oaicite:9]{index=9}). The 2023 rooms likewise cover digital disciplines (UI/UX, Motion Design, SMM/copywriting, mobile videography, graphic design) evaluated by the jury. \ExhibitRef{ITeachMeInv2023} (see :contentReference[oaicite:10]{index=10}).

\paragraph{Professional level and selectivity of the works judged.}
The invitations describe a multi-stage national selection and graduation pipeline. For OrleTECH~2024: \textit{``More than \textbf{1{,}800} applications \dots \textbf{232} students selected after a three-stage competition \dots \textbf{3.5} months of training \dots over \textbf{120} graduates completed and presented projects online; \textbf{50} travel to Astana for the \emph{offline} defense before the jury.''} \ExhibitRef{ITeachMeInvitation2024} (see :contentReference[oaicite:11]{index=11}). The 2023 invitation similarly notes \textit{``more than one and a half thousand applications''} with \textasciitilde\textbf{150} students passing the selection for four months of instruction before the juryed final. \ExhibitRef{ITeachMeInv2023} (see :contentReference[oaicite:12]{index=12}, :contentReference[oaicite:13]{index=13}).

\paragraph{Public presence and verification (program identity and tracks).}
The OrleTECH site describes the three tracks (English translation from the site screenshots): \textit{``NO CODE—building websites and apps without coding; UX/UI DESIGN + WEB—usable, visually pleasing sites; AI SPECIALIST—using AI to create texts, images, animation and video''}; it also shows the curriculum timeline and cumulative results (\textit{``180 participants completed courses and defended projects; 90\% employed; 80+ attended Soft Skills camp; 40+ employer partners''}). \ExhibitRef{OrleTechSite}.  

\paragraph{Ongoing expert engagement (foundation certificate).}
The foundation’s certificate confirms \mrl{} has served on an \textbf{ongoing basis since November~2022} as \textit{``external expert, jury member, and consultant''} for finals (ITeachMe~6.0, 7.0; OrleTECH~2.0), including \textit{independent professional evaluation of projects (UX/UI, graphic/motion design, SMM, copywriting, mobile videography, no-code, AI), preparation of expert recommendations, and advisory on digital transformation and information security}. \ExhibitRef{ITeachMeCertificate} (see :contentReference[oaicite:14]{index=14}, :contentReference[oaicite:15]{index=15}).  
The foundation also runs allied national events (e.g., online job fairs with Enbek.kz/Astana~Hub); this context appears in the foundation’s circulars. \ExhibitRef{ITeachMe1024} (see :contentReference[oaicite:16]{index=16}, :contentReference[oaicite:17]{index=17}).

\paragraph{Conclusion.}
Across 2023–2024 (and ongoing), the record shows \emph{formal invitations with dates/venues}, \emph{jury agendas listing the defended tracks}, and \emph{on-site evidence} of \mrl’s active jury participation, all within his IT/AI field; the foundation’s certificate documents continued expert/jury work and deliverables (written conclusions and recommendations). This satisfies 8~CFR~204.5(h)(3)(iv) for judging in the same/allied specialization.

\medskip

% =========================================================
% Kaspersky Lab — expert commission (IT, data security, cybersecurity)
% =========================================================

\SubSubSubSection{Kaspersky Lab KZ — Expert commission on IT, Data Protection, and Cybersecurity}
\label{subsubsec:JudgingKasperskyNew}

\paragraph{Proof of invitation and role.}
Kaspersky Lab (Kazakhstan) confirms on corporate letterhead that \mrl{} \textbf{``since September~2019 to the present''} is \textit{engaged on a permanent basis as a leading expert and consultant} to participate in an \textbf{expert commission} for the \textit{development, evaluation, and analysis of business projects in information technology and data security, as well as the digitalization of infrastructure projects and cybersecurity}. (English translation.) \ExhibitRef{KasperskyExpert}.

\paragraph{Proof of \emph{actual} judging (functions and outcomes).}
The same letter details that within this expert role \mrl{}:
\begin{itemize}
  \item \textit{researches and analyzes global trends in municipal service digitalization using Data~Analytics tools};
  \item \textit{analyzes projects on cybersecurity, data protection, and cloud solutions};
  \item conducts \textit{information-technology expert review of business projects for feasibility and applicability given available tools and resources};
  \item \textit{provides expert conclusions with comments and clarifications on reviewed initiatives and proposes ideas/developments for improvement}.
\end{itemize}
(English translation from the Kaspersky letter.) \ExhibitRef{KasperskyExpert}. These responsibilities evidence \emph{actual judging activity} with written expert opinions and adopt/revise/optimize outcomes.

\paragraph{Same or allied field of specialization.}
All topics judged—enterprise IT projects, data protection, cloud solutions, cybersecurity, and analytics-driven digitization—are directly within \mrl’s field of \fie{}.

\paragraph{Professional level of the works judged.}
The forum is an \emph{industry expert commission} at a major cybersecurity vendor; the evaluated works are business-critical IT/security projects and infrastructure digitalization initiatives. The requirement to produce formal expert conclusions and propose technical improvements shows that \mrl{} judges the work of professional engineering and product teams against established technical and security standards. \ExhibitRef{KasperskyExpert}.

\paragraph{Public verification details.}
The certificate bears Kaspersky’s corporate letterhead (Kazakhstan office address/phones, corporate email/website), the institutional seal, and the Managing Director’s signature, providing direct points of verification. \ExhibitRef{KasperskyExpert}.

\paragraph{Conclusion.}
Kaspersky’s official correspondence documents both the \emph{invitation} and \emph{actual service} by \mrl{} as a permanent expert/consultant in an industry commission judging high-impact IT and cybersecurity projects in the same/allied field, with written expert conclusions—meeting 8~CFR~204.5(h)(3)(iv).

\SubSubSubSection{iKOMEK109 (Administration of Astana) — Permanent member of the Commission on Digital Development}
\label{subsubsec:JudgingIKomek}

\paragraph{Proof of invitation and standing on the panel.}
The City Center of Monitoring and Rapid Response of the Administration of Astana (\emph{iKOMEK109}) confirms on official letterhead (seal and signature) that \mrl{} \textbf{has served since September~2022 as a permanent member of the Commission on Digital Development and the Use of Information Technologies}, performing expert activities focused on the analysis, evaluation, and development of digital initiatives. (\ExhibitRef{IkomekCommission}.)

\paragraph{Proof of \emph{actual} judging — functions and decision outcomes.}
The same letter specifies the judging work \mrl{} performs and the outcomes of his reviews:
\begin{enumerate}
  \item \textbf{Assessment and expert evaluation of digital projects and initiatives}: studies proposals for digital transformation; analyzes expediency, economic efficiency, and alignment with enterprise strategy; evaluates business cases and techno–economic rationales for new digital solutions, applying \emph{TOGAF} for architecture assessment, \emph{SWOT} and scenario analysis for risk, and \emph{ROI} to compute expected economic efficiency.
  \item \textbf{Development and correction of internal regulatory documents}: analyzes existing regulations, policies, and methodological recommendations governing IT/innovation; studies international standards and practices including \emph{ISO~27001}, \emph{GDPR}, and the \emph{NIST Cybersecurity Framework}; for business–process impacts uses \emph{BPMN} and for IT governance review uses \emph{COBIT}.
  \item \textbf{Control of implementation and effectiveness}: participates in monitoring implementation of approved IT projects; analyzes KPI data; develops optimization proposals; reviews reports and provides expert evaluation of impact on business processes.
  \item \textbf{Information security and data protection}: reviews compliance with cybersecurity requirements including \emph{Zero Trust Architecture (ZTA)}, \emph{ISO~27001} and national personal-data laws; analyzes risks related to data processing/storage and proposes mitigation (MFA, encryption, monitoring anomalous network activity).
  \item \textbf{Monitoring of innovative technologies and trends}: researches AI, big data, process automation, and digital platforms; analyzes potential use; evaluates alignment with strategic priorities; recommends the most promising solutions.
\end{enumerate}
Based on these evaluations, \mrl{} \emph{forms recommendations} on adoption/approval, coordination, revision, or refusal of the reviewed documents and initiatives, issuing written conclusions where inconsistencies are found. (\ExhibitRef{IkomekCommission}.)

\paragraph{Same or allied field of specialization.}
All reviewed matters—enterprise IT, digital platforms, AI/big data initiatives, automation, and information security/compliance (\emph{ZTA, ISO~27001, GDPR, NIST})—belong to \mrl’s field of \fie{}, satisfying USCIS’s “same or allied field” requirement.

\paragraph{Professional level and public mandate (verification).}
iKOMEK109 is the City’s 24/7 monitoring \& rapid-response center. The official site shows mission/vision, operations, and city metrics (e.g., CCTV footprint) and lists the administration roster, corroborating scale and mandate. (\ExhibitRef{IKomekSite}.) The verified Instagram profile provides an additional public footprint. (\ExhibitRef{IKomekInstagram}.)

\paragraph{Conclusion.}
The government letter evidences both \emph{invitation} and \emph{actual participation} with adopt/revise/reject outcomes in the same/allied field, meeting 8~CFR~204.5(h)(3)(iv).


\SubSubSubSection{JSC ``State Technical Service'' (STS) — Expert commission on information security \& digitalization; Independent Director}
\label{subsubsec:JudgingSTS}

\paragraph{Proof of invitation and role.}
JSC ``State Technical Service'' certifies on official letterhead (seal/signature) that since \textbf{January~2022} \mrl{} has been engaged on a permanent basis as (i) an external expert on technology transfer, information security, and digitalization and (ii) an \textbf{Independent Director/Board member}. He takes part as a lead expert–analyst in the \emph{expert commission} evaluating the information-security posture of e-government informatization facilities to identify threats/incidents and ensure secure operation and data protection. (\ExhibitRef{STSCommission}.)

\paragraph{Proof of \emph{actual} judging.}
The STS certificate details concrete judging work and outcomes, including:
\begin{itemize}
  \item \textbf{Expert review of submissions} on IS posture of e-government facilities; analysis of incidents/threats with mitigation and data-protection recommendations.
  \item \textbf{Line-by-line review of draft normative/legal acts} on information security, digitalization, and AI at informatization objects; written expert comments and conclusions.
  \item \textbf{Independent Director oversight of technical projects}: business-process design for trials of the \emph{Synaq} portal; pilot testing of the National video-monitoring system; data-collection/processing design for \emph{CyberDigest}; review of an \emph{IP-address packet-filtering module}.
  \item \textbf{Issuance of formal expert opinions} recommending adoption, revision, or rejection of reviewed projects/normative acts.
\end{itemize}
(\ExhibitRef{STSCommission}.)

\paragraph{Same or allied field of specialization.}
All judged matters—information-security architectures and controls, cybersecurity compliance, AI use within state informatization systems, and national digital platforms—are within \mrl’s field of \fie{}.

\paragraph{Institutional standing and public mandate (verification).}
STS presents itself as \emph{the technological core of Kazakhstan’s cyber-shield}; official pages list mission and state-monopoly functions (e.g., Unified Internet/e-mail gateways for e-government, testing e-government facilities for IS compliance, national coordination/monitoring of incidents, operation of the National Video Monitoring System, SOC functions, and certification center). (\ExhibitRef{STSSite}; \ExhibitRef{STSAbout}.)

\paragraph{Conclusion.}
Official correspondence plus STS’s public mandate demonstrate invitation and \emph{actual service} judging high-impact IS/AI \& digitalization work in the same/allied field, meeting USCIS Criterion~4.


\SubSubSubSection{Elorda Qurylys Kompaniyasy (EQK) — Enterprise expert commissions}
\label{subsubsec:JudgingEQK}

\paragraph{Proof of invitation and role.}
Elorda Qurylys Kompaniyasy (EQK) confirms that since \textbf{March 15, 2022} \mrl{} has been engaged on an ongoing basis as an \emph{expert in information technologies and innovation} to review matters and projects related to the introduction and development of these directions in the company. (\ExhibitRef{EQKExpert}.)

\paragraph{Proof of \emph{actual} judging (functions and outcomes).}
The letter, signed by the General Director (seal), specifies that \mrl{}:
\begin{itemize}
  \item analyzes technological solutions proposed for optimization of construction processes and asset management;
  \item evaluates innovative technologies to increase the efficiency and quality of construction projects;
  \item conducts detailed research of automation/digitalization projects to determine applicability for each site;
  \item analyzes risks/opportunities related to introducing IT solutions in civil construction;
  \item consults on integration of innovative systems and technologies into existing business processes.
\end{itemize}
Based on the above, \mrl{} \emph{prepares analytical reports and expert conclusions} on feasibility and implementation for each matter considered. (\ExhibitRef{EQKExpert}.)

\paragraph{Same or allied field of specialization.}
The judging concerns enterprise digitalization, automation, and integration of IT solutions—squarely within \mrl’s field of \fie{}.

\paragraph{Institutional/public footprint (verification).}
EQK’s official website describes the company’s mission and portfolio of residential/infrastructure projects and publishes corporate news; the official Instagram account provides an additional public presence. (\ExhibitRef{EQKSite}; \ExhibitRef{EQKInstagram}.)

\paragraph{Conclusion.}
EQK’s correspondence evidences invitation and \emph{actual participation} as an expert judging enterprise IT/digitalization projects with written conclusions—satisfying 8~CFR~204.5(h)(3)(iv).
