\subsection{%
    Evidence of \mrls performance of a leading or critical role for organizations with a distinguished reputation%
}
\label{subsec:Role}

% USCIS criterion reference (keep for context)
% Criterion 8: The person has performed in a leading or critical role for organizations or establishments that have a distinguished reputation.

% ======================================================================
% iKOMEK109 — City Monitoring & Rapid Response Center (3.5–4 pages)
% ======================================================================

\subsubsection{Municipal State Enterprise “iKOMEK109” — City Monitoring \& Rapid Response Center}
\label{subsubsec:RoleIKomek}

\SubSubSubSection{Institutional context and distinguished reputation}
\textbf{iKOMEK109} is the capital city’s unified service center operating as: (1) a 24/7 omnichannel \textit{Contact Center}; (2) a \textit{Situation Center} integrating CCTV and Internet-of-Things feeds to maintain real-time situational awareness; and (3) an \textit{Analytics Unit} that leverages Big Data for systemic-issue detection and mayoral escalations. The Deputy Mayor’s letter describes the organization’s scope explicitly:
\begin{quote}
\textit{“iKOMEK represents the city’s unified Situation Center comprised of: (1) the iKOMEK109 contact center [\textbf{more than 2.2 million citizen appeals per year}], (2) the monitoring Situation Center with integrated camera networks, fire-prevention systems and IoT solutions and (3) the Analytics Center that works with Big Data to identify issues and escalate to the city’s leadership.”} \ExhibitRef{IKomekDeputyAkimLetter}
\end{quote}
Independent materials in the record corroborate iKOMEK109’s \textbf{distinguished reputation}: the official site outlines its citywide mandate and volumes; major press coverage reports multi-million appeals throughput; and the verified Instagram account shows sustained public-facing operations and outreach. In addition, the national government portal confirms iKOMEK’s \textbf{unified, 24/7} role and official intake channels (short number 109, Telegram bot, mobile app, mayor’s website, “Smart Astana” app), listing a broad catalog of services and high first-call resolution. The municipal transport operator (CTS) independently directs all public-transport inquiries through iKOMEK, evidencing centralization of citizen service. \ExhibitRef{IKomekSiteShot}\ExhibitRef{IKomekPress}\ExhibitRef{IKomekInstagramShot}\ExhibitRef{IKomekGov}\ExhibitRef{IKomekCTS}

\SubSubSubSection{Objective corroboration of mandate and intake channels (government \& operator sources)}
\noindent\textbf{Government portal (gov.kz).} The official \emph{About iKOMEK 109} page confirms consolidation of municipal hotlines into a \textbf{single 24/7} contact point, enumerates all intake channels (Akimat web portal, Telegram bot, iKOMEK109 mobile apps, Smart Astana, email and short code \textbf{109}) and notes a catalog of \textbf{2{,}500+ services} with \textbf{85\%} first-call resolution. \ExhibitRef{IKomekGov}

\noindent\textbf{City Transportation Systems (CTS).} The municipal operator directs \textbf{all public-transport questions} to iKOMEK109, listing the same official channels (109, mobile apps, mayor’s website, Telegram bot, Smart Astana, email), independently corroborating iKOMEK109’s centralized role for city services. \ExhibitRef{IKomekCTS}

\SubSubSubSection{Public communications footprint (verified social media)}
The verified \textbf{iKOMEK109} Instagram profile evidences sustained public outreach and scale (profile statistics shown in the screenshot), reinforcing the Center’s prominence as the city’s unified 109 operator. \ExhibitRef{IKomekInstagramShot}

\SubSubSubSection{Appointment, scope of authority and remit}
The Deputy Mayor of Astana city confirms that Mr.\ Taximov has served as \textbf{Head of iKOMEK109} since \textbf{May 27, 2022}, accountable for end-to-end operations across the Contact Center, Situation Center and Analytics Unit, as well as for the \textbf{digital transformation} agenda (“iKOMEK 2.0”). The remit combines executive leadership (process, policy, budgeting, inter-agency coordination) with hands-on product and engineering direction. \ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{Evidence of a leading and critical role — executive governance, measurable reductions and systemic closures}
\{Executive prioritization cadence with the Mayor.}
Under Mr.\ Taximov’s leadership, iKOMEK institutionalized \textbf{weekly executive reporting} to the Mayor, focused on the most acute citywide issues. The result was a \textbf{76\% reduction} in unresolved “especially important/very urgent” items (\textbf{112 $\rightarrow$ 27}) over 2023 and 1H2024:
\begin{quote}
\textit{“The weekly practice at the Mayor’s executive meeting on prioritizing the most resonant citizen problems reduced unresolved items from \textbf{112} to \textbf{27} (−\textbf{76\%}).”} \ExhibitRef{IKomekDeputyAkimLetter}
\end{quote}

\{Backlog liquidation and throughput improvement.}
A comprehensive liquidation of long-standing “Waiting” tickets accompanied a lift in annual throughput to \textbf{426{,}542} closed appeals in 2023—a \textbf{+28.4\%} increase vs.\ 2022 (\textbf{332{,}178}). This required workflow redesign, stricter SLAs and structured escalation routines—core hallmarks of \textbf{critical} operational leadership. \ExhibitRef{IKomekDeputyAkimLetter}

\{Systemic urban fixes (lighting, public space, utilities).}
The record ties iKOMEK’s governance to citywide remediation: modernization of \textbf{80+} playgrounds; reconstruction of \textbf{43} sports grounds; installation of \textbf{378 km} of street lighting across problem segments. The letter links these to improved safety and a \textbf{27.3\%} reduction in crime. \ExhibitRef{IKomekDeputyAkimLetter}

\{Expanded sensor footprint and infrastructure hazard closure.}
Camera coverage expanded from \textbf{9{,}752} to \textbf{10{,}581} (\textbf{+8.5\%}); the cross-agency workgroup remediated \textbf{13{,}927} open manholes; and service-disruption nodes (e.g., water supply/drainage) were closed via targeted inter-agency action. \ExhibitRef{IKomekDeputyAkimLetter}

\{Situation Center enforcement enablement and fiscal outcomes.}
Refined detection algorithms and procedures increased efficacy against criminal behaviors (e.g., drug “stashers”):
\begin{itemize}
  \item \textbf{+17\%} increase in registered cases related to drug stashing vs.\ the prior year;
  \item \textbf{23} criminal cases and \textbf{19{,}384} administrative offenses supported, of which \textbf{13{,}015} were protocolled;
  \item \textbf{KZT 52{,}008{,}750} in fines recorded.
\end{itemize}
\ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{Evidence of a leading role — digital channels, talent and incentives, targeted social programs}
\{Digital channel strategy.}
A focused product strategy to move citizen intake to the Telegram bot and mobile app led to a \textbf{22\%} rise in online submissions in 2023. \ExhibitRef{IKomekDeputyAkimLetter}

\{Workforce performance and compensation modernization.}
To sustain higher service standards, Mr.\ Taximov secured budget approval for a compensation update: \textbf{+51\%} for production staff; \textbf{+31\%} for administrative staff; and a KPI-linked annual bonus (up to four salaries). \ExhibitRef{IKomekDeputyAkimLetter}

\{Employee housing access and loyalty.}
An \textbf{MOU with Otbasy Bank} supported long-term savings for housing; the staff loyalty index improved to \textbf{42}. \ExhibitRef{IKomekDeputyAkimLetter}

\{Healthcare complaints reduction line.}
Following a ministerial visit (March 2024), Mr.\ Taximov launched a \textbf{direct complaints channel to medical institutions}; weekly, \textbf{150+} calls are routed to \textbf{four} pilot facilities for faster resolution and lower complaint loads. \ExhibitRef{IKomekDeputyAkimLetter}

\{Youth practice and inclusion.}
A modernized youth practice program trained \textbf{60+} participants; employment of persons with disabilities rose from \textbf{6} to \textbf{10}, contributing to employer-of-the-capital recognition for youth and vulnerable-group hiring (2023). \ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{Project-portfolio governance and inter-agency delivery model}
\{Creation of a Project Management Department within iKOMEK109.}
By city decision in early 2023, the Mayor’s Office Project Office was transformed into a \textbf{Department of Project Management} based at iKOMEK109. Mr.\ Taximov coordinated SCRUM cadences across \textbf{23} line departments, \textbf{5} district offices, \textbf{2} territorial departments (Police, Emergencies) and \textbf{75} quasi-public companies. \ExhibitRef{IKomekDeputyAkimLetter}

\{Templating of national-priority projects.}
He led the decomposition and templating of \textbf{32} projects covering Presidential directives (utilities wear reduction to 40\%; heating and gas plant commissioning; pumping-station expansion; completion of 16 shared-equity sites; LRT acceleration; EXPO and riverfront transformations; substation build-out; major road reconstructions; neighborhood improvements), plus items under the \textit{Plan of Priority Actions for Economic Growth in 2024}. \ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{R\&D function, election-period data engineering and list integrity}
\{R\&D creation (Data Science/Big Data).}
Mr.\ Taximov formed a dedicated “Department of IT and Development (R\&D)” specializing in Data Science and Big Data (Python, R, Hadoop, Spark, TensorFlow, SQL/NoSQL) to sustain analytical operations. \ExhibitRef{IKomekDeputyAkimLetter}

\{Election lists: 84\% $\rightarrow$ 100\% accuracy, geocoding and deduplication.}
The team delivered election-period data engineering that \textbf{raised register accuracy from 84\% to 100\%}, geolocated \textbf{513} addresses (\textbf{25{,}036} voters) and corrected \textbf{1{,}000+} addresses via Python/Pandas/NumPy algorithms and cartographic reconciliation—high-stakes civic data quality showing \textbf{hands-on leadership} tied to public trust. \ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{Product leadership: iKOMEK~2.0 roadmap and stack}
\{Team, stack and delivery model.}
Mr.\ Taximov staffed an in-house product/engineering team (frontend/backend devs, BA, UX/UI, Scrum master) and executed the \textbf{iKOMEK~2.0} roadmap:
\begin{itemize}
  \item new CRM for intake and case lifecycle;
  \item external integrations;
  \item analytics and management tooling with executive rankings;
  \item database optimization;
  \item unified online channels with SSO and improved UX.
\end{itemize}
Stack: \textbf{TypeScript, React.js, Next.js, tRPC, Prisma ORM, Tailwind CSS, PostgreSQL}. Delivery followed \textbf{Agile/Scrum} with two-week sprints; Mr.\ Taximov also completed \textbf{SAFe Product Owner} certification (2024). \ExhibitRef{IKomekDeputyAkimLetter}
\medskip

\SubSubSubSection{Operating model artifacts (slides and talk track)}
The \textit{iKOMEK 2.0} presentation and companion script visualize and narrate the operating model (governance cadence, KPIs, Situation Center pipeline, channels strategy, enforcement linkage, data-engineering flows and roadmap). These artifacts provide objective, process-level corroboration of the leadership role and delivery model. \ExhibitRef{IKomekPresentation}\ExhibitRef{IKomekPresentationScript}

\SubSubSubSection{Public record corroboration (official site and press)}
A snapshot of the official \textbf{iKOMEK109} site evidences mandate, 24/7 operations, channels, KPIs, leadership and public-admission schedule. Independent press coverage in leading outlets further corroborates organizational scale and leadership status. \ExhibitRef{IKomekSiteShot}\ExhibitRef{IKomekPress}

\SubSubSubSection{Why this meets USCIS Criterion 8}
The organization prong is satisfied by iKOMEK109’s official citywide mandate and scale (multi-million appeals volumes; integrated safety/IoT/CCTV analytics) and corroborating public record. The performance prong is met by documented \textbf{leadership} (mayoral cadence; cross-agency project office; platform roadmap/team building) and \textbf{critical outcomes} (crime reduction; enforcement/fines; systemic hazard remediation; backlog liquidation; 100\% election-list accuracy; digital-channel adoption; compensation reform; healthcare complaints line). These enterprise-level results are tied directly to Mr.\ Taximov’s role. \ExhibitRef{IKomekDeputyAkimLetter}

\ExhibitList{
  \ExhibitRef{IKomekDeputyAkimLetter}
  \ExhibitRef{IKomekSiteShot}
  \ExhibitRef{IKomekPress}
  \ExhibitRef{IKomekInstagramShot}
  \ExhibitRef{IKomekPresentation}
  \ExhibitRef{IKomekPresentationScript}
  \ExhibitRef{IKomekGov}
  \ExhibitRef{IKomekCTS}
}

\pagebreak

% ======================================================================
% JSC “State Technical Service” (STS) — National Cybersecurity (now expanded)
% ======================================================================

\subsubsection{Joint-Stock Company “State Technical Service” (STS) — National Cybersecurity Operator}
\label{subsubsec:RoleSTS}

\SubSubSubSection{Institutional context and distinguished reputation}
\textbf{STS} is the \textit{national cybersecurity operator} responsible for the protection of e-government systems and critical information infrastructure. It operates \textbf{KZ-CERT}, maintains national coordination centers and performs state-mandated security testing and monitoring. Public-facing materials (site snapshots; corporate communications) emphasize national-scale services, training and community engagement, underscoring a sustained public mission and visibility appropriate to a distinguished organization. \ExhibitRef{STSSiteShot1}\ExhibitRef{STSSiteShot2}\ExhibitRef{STSInstagramShot}
The official role letter on STS letterhead confirms mandate and daily operational use of the platforms described below. \ExhibitRef{STSRoleLetter}

\SubSubSubSection{Public record corroboration (official site \& verified channel)}
Official site snapshots show the organization’s national mission, incident/attack statistics and high-level partner landscape; the \emph{About} pages list national-scale functions across the information security of e-government and critical infrastructure. A verified Instagram channel provides additional public-facing communication by the national enterprise. Together these exhibits corroborate STS’s public mandate and standing. \ExhibitRef{STSSiteShot1}\ExhibitRef{STSSiteShot2}\ExhibitRef{STSInstagramShot}

\SubSubSubSection{Appointment and mandate}
Mr.\ Taximov has served as \textbf{Independent Director} and Board member since \textbf{January 18, 2022} (per KNB Committee Chairman’s order dated 14.01.2022). He \textbf{chairs the Strategic Development Committee} and coordinates information- and cybersecurity directions—combining board-level governance with hands-on program leadership. The role letter further notes his participation as a \textbf{chief expert–analyst} in commissions evaluating the security of e-government information systems, placing him in a permanent technical gatekeeping function on top of committee leadership. \ExhibitRef{STSRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role — governance, national workflows and operational tooling}
\{Board-level strategy and permanent expert authority.}
The Strategic Development Committee chairship situates Mr.\ Taximov in oversight of innovation and cybersecurity priorities, while his \emph{chief expert–analyst} duties anchor day-to-day conformity with state requirements for information-system security. This dual positioning (governance plus technical gatekeeping) is probative of a \textbf{leading and critical} role at an organization with a national mandate. \ExhibitRef{STSRoleLetter}

\{Closed operational media-monitoring bot.}
STS documents a production \textbf{Telegram bot} used by STS units with keyword/user management, scheduled searches every four hours across subscribed channels, programmable web queries via \textbf{Google Programmable Search}, notifications, logging and a dedicated database. These features correspond to an \emph{operational early-warning} capability for emerging issues in open sources, allowing cyber operators to triage items into formal response workflows. 
\begin{quote}
\textit{“The Telegram bot was implemented for STS divisions and is used in everyday work.”} \ExhibitRef{STSRoleLetter}
\end{quote}
The internal contribution memorandum reiterates the bot’s role as a \textit{working} tool embedded in daily practice, evidencing production maturity rather than pilot status. \ExhibitRef{STSContribution}

\{\textit{Synaq} — end-to-end digitization of testing and \emph{electronic protocols}.}
\textbf{Synaq} automates attestation testing of e-government and critical-infrastructure information systems. It comprises a web application for applicants and testing personnel, a unified data store and an administration module with role control and audit logging. Critically, it supports formation/approval/signing of \textbf{appeals for quotations} (with automated cost calculation), formation/approval/signing of \textbf{test appeals} and issuance/download of \textbf{electronic protocols} with digital signatures. By replacing paper-heavy processes with authenticated e-protocols, Synaq strengthens evidentiary chains, reduces administrative cycle time and standardizes national testing artifacts for audit and oversight. 
\begin{quote}
\textit{“Development of Synaq automated the testing process, significantly reduced paperwork and is used in STS operations.”} \ExhibitRef{STSRoleLetter}
\end{quote}
The contribution memo confirms these functions and frames Synaq as a core element of the national testing workflow now conducted in digital form. \ExhibitRef{STSContribution}

\{\textit{ScanKZ} — nationwide exposure collection and CERT notifications.}
\textbf{ScanKZ} continuously collects device/service exposure data across Kazakhstan’s IP ranges and domains to feed KZ-CERT prevention work. Data collected include subdomains; DNS for domains/subdomains; IPs; open ports/services; device versions and OS fingerprints; TLS/SSL certificates; WHOIS; titles/favicons/hashes; and identification of \textbf{vulnerable hosts/services} and public resources. This capability serves as a \emph{national attack-surface inventory} that increases coverage and timeliness of vulnerability notifications, aligning with CERT best practices for proactive defense.
\begin{quote}
\textit{“\ldots improves KZ-CERT prevention by automatically identifying vulnerable objects; expands the capacity to assess security of devices in Kazakhstan connected to the Internet.”} \ExhibitRef{STSRoleLetter}
\end{quote}
STS’s internal memorandum corroborates that ScanKZ outputs flow into operational teams for continuous prevention and notification, demonstrating \textbf{ongoing} use rather than one-off analysis. \ExhibitRef{STSContribution}

\{Coherence of the national toolchain (bot $\rightarrow$ Synaq $\rightarrow$ ScanKZ).}
The three documented systems form a coherent toolchain aligned to STS’s national mission: (i) the \emph{monitoring bot} surfaces emergent risks from open sources and sector chatter for situational awareness; (ii) \emph{Synaq} codifies formal testing/attestation with signed artifacts and audit trails; and (iii) \emph{ScanKZ} discovers live exposures across national address space, enabling KZ-CERT to notify owners and track remediation. Mr.\ Taximov’s leadership across this portfolio—spanning \textbf{governance}, \textbf{process digitization} and \textbf{exposure intelligence}—is evidence of a \textbf{critical} role at the core of STS’s prevention and assurance functions. \ExhibitRef{STSRoleLetter}\ExhibitRef{STSContribution}

\{Operational controls and auditability.}
Each platform, as described, embeds \emph{control points} that are foundational for a national operator: user/keyword management and persistent logging in the bot; role administration and audit logging in Synaq; and repeatable asset discovery in ScanKZ, which supports notification trails to owners and KZ-CERT follow-up. The recorded use of \emph{electronic protocols} with digital signatures in Synaq and the daily operational character of the bot and ScanKZ, provide the sort of \textbf{traceability and accountability} expected in state-mandated cyber functions. \ExhibitRef{STSRoleLetter}\ExhibitRef{STSContribution}

\SubSubSubSection{Why this meets USCIS Criterion 8}
STS’s status as national cyber operator satisfies the organization prong (distinguished reputation) through mandate, scale and public record. The performance evidence shows \textbf{leadership} (Independent Director; Strategic Development Committee chair; chief expert–analyst in security commissions) and \textbf{critical} delivery (bot used daily by STS units; \textit{Synaq} e-protocols for formal testing; \textit{ScanKZ} for national exposure management) with detailed features and operational impact. These are core national-security functions squarely within USCIS’s conception of “leading or critical,” and the exhibits confirm not only build/launch but \textbf{continued operational use} in STS’s day-to-day mission. \ExhibitRef{STSRoleLetter}\ExhibitRef{STSContribution}

\ExhibitList{
  \ExhibitRef{STSRoleLetter}
  \ExhibitRef{STSContribution}
  \ExhibitRef{STSSiteShot1}
  \ExhibitRef{STSInstagramShot}
}

\pagebreak


\subsubsection{Limited Liability Partnership “Elorda Qurylys Kompaniyasy” (Municipal Developer)}
\label{subsubsec:RoleEQK}

\SubSubSubSection{Institutional context and distinguished reputation}
\textbf{EQK} is the municipal developer created to resolve problem shared-equity housing, finish stalled sites and deliver apartments to equity holders—a high-visibility public mission documented through continuous operations and sustained communications since 2018. Public materials report completion of \textbf{141} buildings and re-housing of \textbf{15{,}500+} families; the verified Instagram profile shows frequent stakeholder engagement and handovers. These items establish EQK’s distinguished reputation as the city’s principal mechanism for problem-project resolution. \ExhibitRef{EQKSiteShot}\ExhibitRef{EQKInstagramShot}

\SubSubSubSection{Public record corroboration (official site \& verified channel)}
\noindent\textbf{Official EQK website (site snapshots).} Site pages present EQK’s mandate to resolve shared-equity housing and display a portfolio of delivered residential complexes with current news posts. These snapshots corroborate the scope and continuity of operations. \ExhibitRef{EQKSiteShot1}

\noindent\textbf{Verified Instagram profile.} The official account shows sustained public communications and stakeholder engagement. The screenshot reflects \textbf{4{,}385 followers} and \textbf{468 posts} (as of 2025) and references delivery of \textbf{141} buildings for \textbf{15{,}500+} families, reinforcing EQK’s visibility and mission execution. \ExhibitRef{EQKInstagramShot}

\SubSubSubSection{Appointment and mandate}
From \textbf{March–June 2022}, Mr.\ Taximov served as \textbf{First Deputy CEO for Finance \& IT}. His remit covered capital programming, enterprise controls, \textbf{1C:ERP} implementation, \textbf{BIM} rollout and site automation (video/computer vision)—with the overarching goal of accelerating completions while improving transparency and safety. \ExhibitRef{EQKRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role — capital programming, enterprise controls and investor mobilization}
\{Budget capital programmed to unlock deliveries.}
Mr.\ Taximov \textbf{secured KZT 51 billion} from the National Fund and local budgets, financing completions at \textbf{10} problem sites spanning \textbf{27} buildings and enabling \textbf{3{,}000+} families to receive apartments. 
\begin{quote}
\textit{“Secured KZT \textbf{51} billion, finishing \textbf{10} sites (\textbf{27} buildings), delivering homes to \textbf{3{,}000+} families.”} \ExhibitRef{EQKRoleLetter}
\end{quote}

\{Digital financial model and enterprise control via 1C:ERP.}
He designed and deployed a multi-level control system in \textbf{1C:ERP} (strategic $\rightarrow$ operational) with plan–fact analysis; predictive ratios (liquidity/solvency/profitability); an MCP KPI dashboard; and an integrated \textbf{Budgeting} module. Results:
\begin{itemize}
  \item \textbf{KZT 156.9 million} in annual savings (30\% reduction of previously uncoordinated costs);
  \item average delivery time reduced by \textbf{11\%} (from \textbf{24} to \textbf{21} months).
\end{itemize}
\ExhibitRef{EQKRoleLetter}

\{Private co-investment to accelerate completions.}
Through negotiations, Mr.\ Taximov \textbf{attracted KZT 30 billion} in private capital (including \textbf{BI Group}); one major project of \textbf{three} buildings delivered homes to \textbf{147} families. \ExhibitRef{EQKRoleLetter}

\SubSubSubSection{Evidence of a critical role — construction-site automation, safety and transparency}
\{Computer-vision monitoring and stakeholder trust.}
He introduced site video/computer-vision monitoring for remote workforce presence checks and real-time transparency to equity holders (online viewing). Outcomes:
\begin{itemize}
  \item \textbf{35\%} fewer equity-holder complaints;
  \item \textbf{46\%} reduction in site theft;
  \item \textbf{2.3$\times$} reduction in workplace injuries (and improved discipline).
\end{itemize}
\ExhibitRef{EQKRoleLetter}

\SubSubSubSection{Evidence of a leading role — BIM institutionalization and quality gains}
\{Ten-step BIM pipeline (Model Studio Soft).}
Mr.\ Taximov institutionalized \textbf{BIM} via a ten-stage pipeline and a common data environment (CDE), ensuring role-based access to current information across the lifecycle. On the \textbf{Turan–Syganak} complex (2022), the Model Studio Soft suite (“Construction Solutions,” “Heating and Ventilation,” “Telecom Network,” “CADlib Model \& Archive”) produced detailed 3D models, reduced exam errors by \textbf{3.5$\times$} and accelerated realization. \ExhibitRef{EQKRoleLetter}

\SubSubSubSection{Why this meets USCIS Criterion 8}
The organization prong is met by EQK’s scale and mission in resolving problem housing. The CEO letter demonstrates \textbf{leadership} (deputy CEO remit across finance/IT; ERP, BIM, investor relations) and \textbf{critical} outcomes (\textbf{KZT 51B} budget capital; \textbf{KZT 30B} private capital; \textbf{3{,}000+} families housed; \textbf{KZT 156.9M} annual savings; \textbf{11\%} delivery-time reduction; strong safety and complaint reductions). These are direct advances of the entity’s core public mission. \ExhibitRef{EQKRoleLetter}

\ExhibitList{
  \ExhibitRef{EQKRoleLetter}
  \ExhibitRef{EQKSiteShot}
  \ExhibitRef{EQKInstagramShot}
}

\pagebreak

\subsubsection{Joint-Stock Company “Astana Innovations” (Smart City Operator)}
\label{subsubsec:RoleAIN}

\SubSubSubSection{Institutional context and distinguished reputation}
\textbf{Astana Innovations} is the city’s Smart City operator, responsible for the Big Data platform, the transition from open data to \textbf{open APIs} and the telecom-duct infrastructure underpinning broadband connectivity. Public-facing materials (site snapshots; social presence) reflect long-running platform stewardship. The Board Chairman’s role letter details mandate, scope and the programs delivered under Mr.\ Taximov’s leadership. \ExhibitRef{AINSiteShot}\ExhibitRef{AINInstagramShot}\ExhibitRef{AINRoleLetter}

\SubSubSubSection{Public record corroboration (official site \& verified channel)}
\noindent\textbf{Official website snapshots.} Site pages present AIN’s mission and scope across Smart Astana, Big Data, Open Data/Open APIs and telecom-duct management, with platform/service descriptions captured in the snapshot. These pages corroborate the institutional remit cited in the role letter. \ExhibitRef{AINSiteShot1}

\noindent\textbf{Verified Instagram profile.} The official account evidences sustained public communications and outreach on smart-city, Big Data and Open Data initiatives; the screenshot shows \textbf{3,283 followers} and \textbf{836 posts} (as of 2025). This public footprint supports AIN’s visibility as the city operator. \ExhibitRef{AINInstagramShot}

\SubSubSubSection{Appointment and scope}
Mr.\ Taximov led cross-functional programs spanning \textbf{(i) Big Data \& analytics}, \textbf{(ii) Open Data $\rightarrow$ Open APIs}, \textbf{(iii) telecom ducts} and \textbf{(iv) data-driven policy projects} (transport planning, social compliance, policing analytics), with direct outcomes summarized below. \ExhibitRef{AINRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role — Big Data platform and applied models}
\{Platform governance and advanced analytics.}
As operator of the city Big Data platform (\textbf{76} databases), the team \textbf{implemented 12 analytical models} plus a \textbf{text/graphical visualization block}. The letter enumerates concrete pipelines:
\begin{itemize}
  \item \textit{Self-employed detection} (vacancy boards; phone–ID linkage; pension-payment checks) to assist social-insurance enrollment;
  \item \textit{Transport model} updates (stop load; weekday/weekend flows) using card validations and mobile payments; \textbf{+17\%} transport efficiency via route optimization on the digital city map;
  \item \textit{“Rubber apartments”} detection (multi-registered residents), addressing inconsistent address spellings with \textbf{ML} to surface the \textbf{TOP-40} addresses with \textbf{76{,}000} registrations for law-enforcement review;
  \item \textit{Profile of large families}: \textbf{14{,}601} families and \textbf{92{,}957} children profiled with geocoordinates for targeted social support planning.
\end{itemize}
\ExhibitRef{AINRoleLetter}

\{Police-precinct analytics and city-map integration.}
A police-precinct analysis tool unified \textbf{104 data layers} (from \textbf{76} databases) on the city map to support decisions within precinct boundaries, including age-group breakdowns and service placement. \ExhibitRef{AINRoleLetter}

\SubSubSubSection{Evidence of a leading role — Open Data $\rightarrow$ Open APIs}
\{Programmatic, secure data exchange.}
Mr.\ Taximov drove the modernization from static downloads to \textbf{automated open APIs} (xls, csv, json) across \textbf{9} categories/\textbf{20} datasets (education, healthcare, transport, utilities, city services, internet, ecology, news/events)—enabling scripted, secure integrations and a modern developer experience. \ExhibitRef{AINRoleLetter}

\SubSubSubSection{Evidence of a critical role — telecom-duct turnaround and revenue growth}
\{Process transparency and throughput.}
As manager of the telecom ducts, Mr.\ Taximov:
\begin{itemize}
  \item cut permit/technical-conditions timelines from \textbf{30} to \textbf{14} days;
  \item restored full technical documentation and audited networks (exposing illegal users);
  \item resolved disputed segments and enforced transparent, anti-corruption processes.
\end{itemize}
Contracts grew from \textbf{20} to \textbf{73}; revenue rose from \textbf{KZT 38M} (2019) to \textbf{KZT 152M} (2021). Clients include \textbf{Kazakhtelecom}, \textbf{Transtelecom}, \textbf{Kaztranscom} and \textbf{Beeline Kazakhstan}. \ExhibitRef{AINRoleLetter}

\SubSubSubSection{Evidence of a critical role — election automation and data integrity}
\{Accuracy lift and civic services.}
Under Mr.\ Taximov’s direction, AIN delivered:
\begin{itemize}
  \item voter-register accuracy lift from \textbf{84.4\%} to \textbf{100\%};
  \item \textbf{248} precinct passports produced and uploaded;
  \item online voter-check services across \textbf{mobile app}, \textbf{Telegram bot} and \textbf{city portal};
  \item an ELK-style analytics pipeline for citizen queries;
  \item Python/Pandas $\rightarrow$ PostgreSQL log ingestion (via SQLAlchemy) for daily reporting;
  \item processing of lists from agencies/enterprises in \textbf{10 waves} covering \textbf{100{,}000+} people;
  \item \textbf{15{,}000} temporary registrations ingested and reconciled;
  \item \textbf{5{,}000+} inclusion/exclusion applications processed;
  \item geometry corrections and deduplication for \textbf{4{,}000} addresses.
\end{itemize}
\ExhibitRef{AINRoleLetter}

\SubSubSubSection{Why this meets USCIS Criterion 8}
Astana Innovations’ platform responsibilities (Big Data, open APIs, telecom ducts) demonstrate a \textbf{distinguished reputation}. The letter provides direct, quantitative evidence of \textbf{leading} (platform/product governance; cross-agency analytics; duct operations) and \textbf{critical} (transport efficiency, social targeting, law-enforcement analytics, revenue growth, election integrity) performance attributable to Mr.\ Taximov. \ExhibitRef{AINRoleLetter}

\ExhibitList{
  \ExhibitRef{AINRoleLetter}
  \ExhibitRef{AINSiteShot}
  \ExhibitRef{AINInstagramShot}
}

% -------------------------------------------
% Credentials (CVs) for testimonial/authority weight (if cited in main)
% -------------------------------------------

\ExhibitList{
  \ExhibitRef{BeisenbayevCV}
  \ExhibitRef{KudaiBergenovCV}
  \ExhibitRef{SidelkovskayaCV}
  \ExhibitRef{TokayevCV}
  \ExhibitRef{SanatovCV}
  \ExhibitRef{SanatovCV2}
  \ExhibitRef{EsmagambetovCV}
}


\pagebreak