\subsubsection{Limited Liability Partnership “Elorda Qurylys Kompaniyasy” (Municipal Developer)}
\label{subsubsec:RoleEQK}

\SubSubSubSection{Context and distinguished reputation}
\textbf{EQK} is Astana’s municipal developer created to \emph{finish stalled shared–equity housing}, restore trust, and deliver apartments to equity holders. Public materials show long-running operations, a large portfolio, and sustained communications:
\begin{itemize}
  \item Since 2018 the company reports completion of \textbf{141} buildings and rehousing of \textbf{15{,}500+} families. \ExhibitRef{EQKSiteShot}
  \item The official Instagram profile (government organization) documents monthly activity, public handovers, and stakeholder meetings. \ExhibitRef{EQKInstagramShot}
\end{itemize}
Scale, longevity, and mission show a \textbf{distinguished reputation} as the city’s principal mechanism for problem-project resolution.

\SubSubSubSection{Appointment and mandate}
From \textbf{March–June 2022} Mr.\ Taximov served as \textbf{First Deputy CEO for Finance \& IT}. His written mandate covered (i) \textbf{program finance} for problem portfolios, (ii) enterprise \textbf{ERP} and financial model, (iii) \textbf{BIM} rollout, and (iv) \textbf{site automation} (video/computer vision). \ExhibitRef{EQKRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role (with quantified results)}
\paragraph{1) Portfolio financing to unlock deliveries.}
\ParagraphQuoteByExhibit{“He secured \textbf{KZT 51 billion} from the National Fund and local budgets to complete \textbf{10} problematic sites (\textbf{27} buildings), enabling \textbf{3{,}000+} families to receive apartments.”}{EQK CEO Letter}{EQKRoleLetter}  
Raising and programming capital at this level is \textbf{mission-critical} for EQK’s purpose.

\paragraph{2) Enterprise digital financial model and ERP.}
\ParagraphQuoteByExhibit{“He built a \textbf{1C:ERP}–based control system with plan–fact analysis, real-time liquidity/solvency/profitability ratios, budget control, and KPI dashboards.”}{EQK CEO Letter}{EQKRoleLetter}  
\ParagraphQuoteByExhibit{“The system produced annual savings of \textbf{KZT 156.9 million} and reduced average delivery time by \textbf{11\%} (24$\rightarrow$21 months).”}{EQK CEO Letter}{EQKRoleLetter}  
This is \textbf{leading} product/process transformation with \textbf{critical} financial and schedule impact.

\paragraph{3) Private co-investment to accelerate completions.}
\ParagraphQuoteByExhibit{“He attracted \textbf{KZT 30 billion} of private capital (including BI Group), finishing additional sites; one major project delivered homes to \textbf{147} families.”}{EQK CEO Letter}{EQKRoleLetter}  
Investor mobilization complements budget funds and directly translates to \textbf{apartments delivered}.

\paragraph{4) Site automation and public transparency.}
\ParagraphQuoteByExhibit{“Video/computer-vision monitoring reduced theft by \textbf{46\%} and equity-holder complaints by \textbf{35\%}; stakeholders could view progress online.”}{EQK CEO Letter}{EQKRoleLetter}  
Risk reduction and stakeholder trust are \textbf{core} to municipal development outcomes.

\paragraph{5) BIM rollout and quality gains.}
\ParagraphQuoteByExhibit{“A ten-step \textbf{BIM} pipeline (Model Studio Soft) was introduced across design/construction. On the Turan–Syganak complex, exam errors dropped by \textbf{3.5$\times$}.”}{EQK CEO Letter}{EQKRoleLetter}  
BIM institutionalization is a \textbf{leading} capability that materially improves quality and compliance.

\SubSubSubSection{Why this meets USCIS Criterion 8}
The organization prong is met by EQK’s scale and public role. The CEO letter quantifies Mr.\ Taximov’s \textbf{critical} performance (billions raised; thousands housed; theft/complaints cut; savings/time gains) and \textbf{leading} role (ERP/BIM deployments; investor negotiations), matching USCIS’s emphasis on \emph{performance-based} evidence.

\ExhibitList{
  \ExhibitRef{EQKRoleLetter}
  \ExhibitRef{EQKSiteShot}
  \ExhibitRef{EQKInstagramShot}
}
