% ==============================
% EB-1A — Criterion 9 (High Salary)
% ==============================

\subsection{Evidence that ~\mrl\ has commanded a high salary relative to others in the field}
\label{subsec:Salary}

% USCIS Criterion 9: The person has commanded a high salary or other significantly high remuneration for services, in relation to others in the field.

~\mrl\ works in the IT Project Management field. Below are independent, location-specific compensation surveys for \textbf{Astana, Republic of Kazakhstan} covering the relevant role of \emph{IT Project Manager}. These sources provide the benchmark salaries against which ~\mrl’s remuneration is compared.

\subsubsection{2024 market compensation for Astana (independent sources)}

\paragraph{HR Praktika — formal salary certificate (methodology + median).}
HR Praktika issued a signed certificate that (i) defines job duties and qualification requirements, (ii) describes the averaging methodology across multiple surveys and vacancy samplings and (iii) presents the \textbf{2024 final average monthly salary} for Astana:
\begin{itemize}
  \item \textbf{IT Project Manager:} 
    \begin{itemize}
      \item People Consulting — 485 000 KZT; EY — 510 000 KZT; Habr — 450 000 KZT; hh.ru (Astana sample) — 515 000 KZT (min 386 000; max 643 000). \ExhibitRef{HRPraktikaPMSources}
      \item \emph{Final average monthly salary (certificate):} \textbf{500 000 KZT}. \ExhibitRef{HRPraktikaPMFinal}
      \item \emph{Annualized (12 months):} \(500 000 \times 12 = \mathbf{6 000 000}\) KZT.
    \end{itemize}
\end{itemize}
Each certificate includes duties/qualifications, methodology and data-source list (People Consulting, EY, Habr, hh.ru), signed and stamped. \ExhibitRef{HRPraktikaPMMethodology}

\paragraph{HeadHunter.kz (hh.kz) — official letter with arithmetic average.}
HeadHunter Kazakhstan issued a signed letter presenting the 2024 arithmetic average monthly salary for Astana based on vacancies posted on hh.kz:
\begin{itemize}
  \item \textbf{IT Project Manager: 442 000 KZT per month.} \ExhibitRef{HHPM2024Letter}
\end{itemize}
\noindent
\emph{Annualized equivalent:}
\[
442 000 \times 12 = \mathbf{5 304 000}\ \text{KZT.}
\]

\paragraph{RecCom Recruiting — market overview letter (with seal).}
RecCom provided a 2024 salary overview for Astana with key role definitions and methodology summary:
\begin{itemize}
  \item \textbf{IT Project Manager: 558 000 KZT per month → \(558 000 \times 12 = \mathbf{6 696 000}\) KZT annually.} \ExhibitRef{RecComAstana2024Salaries}
\end{itemize}
The overview explains data sources and methodology and is signed and sealed by the Executive Director. \ExhibitRef{RecComAstana2024Methodology}


\paragraph{Bureau of National Statistics (Astana Department) — official government letter (methodology + average).}
The \emph{Department of the Bureau of National Statistics (Agency for Strategic Planning and Reforms) for the city of Astana} issued an official response letter (No.~ЖТ-2025-03546738, dated 13~October~2025; signed by the Head, N.~Kozhakov) prepared under the \emph{Methodology for calculating average wages of employees} approved by Order No.~20 of 17~November~2023 and based on the nationwide statistical observation \emph{“Report on the structure and distribution of wages”} (index \textbf{2-T (wages)}). Occupational mapping follows the \emph{National Classifier of Occupations of the Republic of Kazakhstan (НКЗ)} per Order No.~130-од of 11~May~2017. The letter provides the following 2024 benchmark for Astana:\ExhibitRef{BNSAstanaICTPM2024Letter}

\begin{itemize}
  \item \textbf{IT Project Manager: \(\mathbf{758\,791}\) KZT per month (nominal average).}
  \item \emph{Annualized (12 months):} \(758\,791 \times 12 = \mathbf{9\,105\,492}\) KZT.
\end{itemize}

The letter also points to the official portal \emph{stat.gov.kz} (section: \emph{Labor and Income} \textrightarrow{} \emph{Wages and Working Conditions} \textrightarrow{} \emph{Electronic Tables} \textrightarrow{} \emph{“Wages of employees in the city of Astana by main professions and positions”}) for current tables and definitions.\ExhibitRef{BNSAstanaMethodology}


\subsubsection{\mrl’s salary and multipliers over market}
\label{subsubsec:HighSalaryPlacement}

\paragraph{\mrl’s salary for the relevant period (calendar year 2024).}
A signed \emph{Salary Statement} from the municipal enterprise (Astana) confirms \mrl’s position as \textbf{IT Project Manager} and covers \textbf{1 January 2024 – 31 December 2024}. The statement shows:
\begin{itemize}
  \item \textbf{Total earnings (“Sum of earnings”):} \(\mathbf{36 280 907.91}\) KZT (gross). 
  \item Pension contributions and income tax lines are listed; for comparison with market data, the gross figure is used.
\end{itemize}
\ExhibitRef{SalaryStatement2024}

\paragraph{USD context (single conversion using NBK full-year daily average).}
To provide a single, consistent USD context, the 2024 gross total is converted once using the \textbf{official daily USD/KZT rates of the National Bank of Kazakhstan (NBK)} averaged across \textbf{all 365 calendar days of 2024}. The arithmetic mean of NBK’s daily series is \(\mathbf{468.99}\) KZT per USD (see exhibit). \ExhibitRef{NBK\_USD\_KZT\_2024Daily}
\[
\textbf{USD equivalent (context only):}\quad
\frac{36 280 907.91\ \text{KZT}}{468.99\ \text{KZT/USD}} \approx \mathbf{77 360}\ \text{USD.}
\]
\emph{Method note:} The NBK is Kazakhstan’s central bank; its published daily rates are official. The average above is the simple mean of all daily NBK USD/KZT fixes for 2024 (no trimming or weighting).

\paragraph{9.3 \mrl’s multiplier over market medians (gross vs. gross).}
Because the benchmark surveys report \emph{gross} salaries, \mrl’s comparison uses the documented gross total of \(36 280 907.91\) KZT (2024):
\begin{itemize}
  \item \textbf{Over HR Praktika (IT Project Manager, 6 000 000 KZT/yr):}\quad \(\displaystyle\frac{36 280 907.91}{6 000 000}= \mathbf{6.0\times}\). \ExhibitRef{HRPraktikaPMFinal}
  \item \textbf{Over HeadHunter (IT Project Manager, 5 304 000 KZT/yr):}\quad \(\displaystyle\frac{36 280 907.91}{5 304 000}= \mathbf{6.8\times}\). \ExhibitRef{HHPM2024Letter}
  \item \textbf{Over RecCom (IT Project Manager, 6 696 000 KZT/yr):}\quad \(\displaystyle\frac{36 280 907.91}{6 696 000}= \mathbf{5.4\times}\). \ExhibitRef{RecComAstana2024Salaries}
  \item   \item \textbf{Over Bureau of National Statistics (IT Project Manager, 9\,105\,492 KZT/yr):}\quad 
  \(\displaystyle\frac{36\,280\,907.91}{9\,105\,492}= \mathbf{4.0\times}\). \ExhibitRef{BNSAstanaICTPM2024Letter}

\end{itemize}

\noindent The Bureau of National Statistics is Kazakhstan’s central statistical authority. Its occupation figures are built from the annual 2-T wage survey, use the national occupations classifier (НКЗ) and follow a published government methodology. This provides an official, independently produced benchmark for Astana that complements private-sector surveys.

\noindent
\emph{Note.} USCIS evaluates foreign compensation relative to local benchmarks. Thus, all comparisons are in KZT; the single USD figure above is provided only for context using NBK’s full-year average rate.

\SubSubSubSection{Exhibits}
\ExhibitList{
  % HR Praktika — IT Project Manager
  \ExhibitRef{HRPraktikaPMMethodology}
  \ExhibitRef{HRPraktikaPMSources}
  \ExhibitRef{HRPraktikaPMFinal}
  % HeadHunter.kz letter
  \ExhibitRef{HHPM2024Letter}
  % RecCom overview
  \ExhibitRef{RecComAstana2024Salaries}
  \ExhibitRef{RecComAstana2024Methodology}
  % Pay statement (iKOMEK)
  \ExhibitRef{SalaryStatement2024}
  % NBK daily rates (USD/KZT, 2024)
  \ExhibitRef{NBK\_USD\_KZT\_2024Daily}
}

\pagebreak