\subsubsection{Joint-Stock Company “State Technical Service” (STS)}
\label{subsubsec:RoleSTS}

\SubSubSubSection{Context and distinguished reputation}
\textbf{STS} is Kazakhstan’s \emph{national cybersecurity operator}. Its official site presents STS as the technological core of the national cyber shield: it operates \textbf{KZ-CERT}, maintains the National Information Security Coordination Center, and runs state-monopoly functions for testing, monitoring, and safeguarding e-government and critical communication infrastructure. \ExhibitRef{STSSiteShot1}\ExhibitRef{STSSiteShot2}  
The corporate Instagram account and communications emphasize national-scale services, training, and community engagement. \ExhibitRef{STSInstagramShot}  
By statutory mandate, infrastructure footprint, and public record, STS clearly has a \textbf{distinguished reputation}.

\SubSubSubSection{Appointment and mandate}
Mr.\ Taximov serves as \textbf{Independent Director} on the Board of Directors and as a \textbf{chief expert–analyst} in national commissions on information security. His responsibilities combine \textbf{governance} (Board/committee leadership) and \textbf{technical program oversight} (e.g., Synaq testing portal, ScanKZ exposure collection, operational tooling). \ExhibitRef{STSRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role}
\paragraph{1) Board-level governance and permanent expert authority.}
\ParagraphQuoteByExhibit{“Since January 2022, Mr.\ Taximov has continuously served as chief expert–analyst in commissions that evaluate the security of e-government information systems. He chairs the \textbf{Strategic Development Committee} of the Board, coordinating innovation and cybersecurity.”}{STS Letter}{STSRoleLetter}  
This places him \textbf{both} in leadership over corporate strategy \textbf{and} in a \textbf{critical} technical gatekeeping role for national systems.

\paragraph{2) \emph{Synaq} portal — automating national testing workflows.}
\ParagraphQuoteByExhibit{“He coordinated design and business processes for \textbf{Synaq}, the national portal that automates testing of e-government systems, issues electronic protocols, and reduces paperwork; it is used daily by STS.”}{STS Letter}{STSRoleLetter}  
This is country-level \textbf{platform modernization} with measurable administrative efficiency.

\paragraph{3) Cyber situational-awareness tooling.}
\ParagraphQuoteByExhibit{“He developed a Telegram bot with Google programmable search integration for monitoring media sources; it provides real-time alerts and a dedicated database for STS units.”}{STS Letter}{STSRoleLetter}  
Hands-on delivery of operational tools shows \textbf{direct technical leadership}, not merely oversight.

\paragraph{4) \emph{ScanKZ} data program — exposure collection at national scale.}
\ParagraphQuoteByExhibit{“He contributed to \textbf{ScanKZ}, an automated system that collects device/vulnerability data (ports, versions, weaknesses) to help KZ-CERT assess risks and notify system owners.”}{STS Letter}{STSRoleLetter}  
ScanKZ enhances national attack-surface visibility; contributing to such a core capability is \textbf{critical} to STS’s mission.

\SubSubSubSection{Why this meets USCIS Criterion 8}
STS’s status and mission meet the organization prong. The letter demonstrates Mr.\ Taximov’s \textbf{leading} (Board/committee chair, strategic coordination) and \textbf{critical} (expert commissions, Synaq, ScanKZ, operational bot) contributions tied to \textbf{national cybersecurity outcomes}. The combination of governance and technical delivery aligns with USCIS’s examples of lead or critical roles for distinguished organizations.

\ExhibitList{
  \ExhibitRef{STSRoleLetter}
  \ExhibitRef{STSSiteShot1}
  \ExhibitRef{STSSiteShot2}
  \ExhibitRef{STSInstagramShot}
}
