% \subsection{Evidence of Mr. Taximov's membership in associations in the field that require outstanding achievement of their members}
% \label{subsec:Associations}

% \subsubsection{Kazakhstan Information Security Association}
% \label{subsubsec:AssociationsKISA}

% \textbf{Proof of Mr. Taximov being a member of Kazakhstan Information Security Association}

% The membership of Mr. Taximov is confirmed by the signed admission decision of July 1 2025 with outgoing No. 010725 2. The decision bears the seal of the Association and the signature of the Chair Mr. Viktor Pokusov.
% \ParagraphQuoteByExhibit{Approve and include Askar Taximov as a member of the community of information security and information technology professionals}{KISA Admission Decision}{KaibAdmissionLetter}
% The quoted language is from the English translation of the decision. This decision is the authoritative proof of membership. \ExhibitRef{KaibAdmissionLetter}

% \textbf{Proof that Kazakhstan Information Security Association is a community in Mr. Taximov's field of endeavor}

% The record and independent materials describe a national professional association in information security and information technology. It operates across Kazakhstan and unites organizations that work directly in digital systems and security.
% \ParagraphQuoteByExhibit{The Association unites thirty organizations in the Republic of Kazakhstan including competence centers testing laboratories manufacturers of information protection tools universities research bodies and major operators of personal data}{KISA Admission Decision}{KaibAdmissionLetter}
% The count is as of the decision date in 2025. Public sources confirm continuous national activity and scope. \ExhibitRef{KISAArticle2017}\ExhibitRef{KISASite}
% This places the Association squarely in the field of IT project management and cybersecurity in which Mr. Taximov works.

% \textbf{Proof that outstanding achievements are required for membership}

% The admission decision is on association letterhead and shows date signature stamp and outgoing number on the face of the record. It states that membership is granted for work significant experience and professional achievements in information technology cybersecurity and project management. It also lists objective prerequisites and confirms that admission is not automatic and is not based on payment of dues. \ExhibitRef{KaibAdmissionLetter}

% % \ParagraphQuoteByExhibit{Higher technical education more than ten years of professional and research activity including at least five years in leadership international project management certificates successful completion of qualification modules expert recommendations own effective developments and methodologies and speaking at national and international conferences}{KISA Admission Decision}{KaibAdmissionLetter}

% These prerequisites match the documentary record provided by Mr.~Taximov.
% % The enumerated achievement-based criteria include:
% \begin{itemize}
%   \item Advanced technical education confirming expertise in IT, cybersecurity,
%         systems architecture, digitalization and innovation. \ExhibitRef{KaibAdmissionLetter}
%   \item \emph{More than 10 years of professional and research experience, with at least 5 years
%         in IT leadership positions}. \ExhibitRef{KaibAdmissionLetter}
%   \item International project-management certifications (including Product Owner
%         and Product Manager). \ExhibitRef{KaibAdmissionLetter}
%   \item Successful completion of advanced qualification examinations such as
%         \emph{Program Increment (PI) Planning, Leadership for PI Planning, Iteration Execution,
%         and PI Execution}. \ExhibitRef{KaibAdmissionLetter}
%   \item Written recommendations from recognized experts in IT and digitalization,
%         confirming impeccable professional reputation. \ExhibitRef{KaibAdmissionLetter}
%   \item \emph{Authorship of original and effective developments and methodologies in IT,
%         innovation and technology transfer}. \ExhibitRef{KaibAdmissionLetter}
%   \item \emph{Presentations delivered at national and international conferences}
%         (with international participation considered a distinct advantage). \ExhibitRef{KaibAdmissionLetter}
% \end{itemize}

% As corroboration, Mr.~Taximov provides his SAFe Product Owner and Product Manager
% version~6.0 certificate, ID~13095832--8742, issued on December~11,~2023. \ExhibitRef{PMCertificate}


% The decision does not use the word outstanding. The level of achievement follows from the multi factor prerequisites the documented record and the expert review that leads to selective admission.

% \textbf{Proof that applicants are judged by recognized national or international experts}

% % The decision states that admission is made by the Association Council. The Council is described as a body of leading experts in information technology and cybersecurity certified information security officers and project managers of national and international level. \ExhibitRef{KaibAdmissionLetter}

% \ParagraphQuoteByExhibit{A candidate is admitted by the decision of the Association Council. The Council consists of leading professional experts in information technology and cybersecurity certified information security officers and project managers of national and international level}{KISA Admission Decision}{KaibAdmissionLetter}

% For clarity the record identifies the decision makers by name and title as shown in the decision and on the association roster such as the Chair Viktor Pokusov and named council members who hold national leadership roles in cybersecurity and I T. This shows that applicants are judged by recognized experts consistent with 8 C F R 204.5 h 3 ii.

% \textbf{Independent corroboration of authority and role}

% An official entry on the national portal Career enbek kz shows accreditation by the National Chamber of Entrepreneurs Atameken as a Center for Recognition of Professional Qualifications in information security and in information and communication technologies.
% \ParagraphQuoteByExhibit{Functions include development of professional standards standardized competency assessments with employer participation and certification of qualifications in core specialties of information security and information and communication technologies}{Career enbek kz registry entry}{KISAEnbek2025}
% This confirms an expert evaluation function in the same field.

% Public materials also describe founding and national activity.
% \begin{itemize}
%   \item Founding in August 2017 to consolidate scientific industrial and governmental expertise for national priorities in security and informatization \ExhibitRef{KISAArticle2017}
%   \item University and industry councils on cybersecurity education and workforce \ExhibitRef{KISAMeeting}
%   \item Public talks by the Chair Mr. Viktor Pokusov on policy and security \ExhibitRef{PokusovTalk}
%   \item National roundtables and advisory events in Astana \ExhibitRef{RoundTable}
% \end{itemize}


% The record shows a professional association in information security and information technology. The membership is conditioned on objective achievements that include education leadership certifications methods and public speaking. The selection is made by recognized experts who serve on the Association Council. There is independent national accreditation for qualification recognition and competency assessment. Accordingly, the record satisfies the membership criterion for associations that admit members on the basis of outstanding achievements, as judged by recognized experts.

% \pagebreak

\subsection{Evidence of Mr. Taximov's membership in associations in the field that require outstanding achievement of their members}



\subsubsection{Kazakhstan Information Security Association}



\textbf{Proof of Mr. Taximov being a member of Kazakhstan Information Security Association}



The membership of Mr. Taximov is confirmed by the signed admission decision of July 1, 2025, with outgoing No. 010725 2. The decision bears the seal of the Association and the signature of the Chair, Mr. Viktor Pokusov.


From the letter:
\emph{“Approve and include Askar Taximov as a member of the community of information security and information technology professionals.”}



\textbf{Proof that Kazakhstan Information Security Association is a community in Mr. Taximov's field of endeavor}



The record and independent materials describe a national professional association in information security and information technology. It operates across Kazakhstan and unites organizations that work directly in digital systems and security.


It is stated in the letter that:
\emph{“The Association unites thirty organizations in the Republic of Kazakhstan including competence centers, testing laboratories, manufacturers of information protection tools, universities, research bodies and major operators of personal data.”}



KISA Admission Decision (English translation).



\textbf{Proof that outstanding achievements are required for membership}



The admission decision is on association letterhead and shows date, signature, stamp and outgoing number on the face of the record. It states that membership is granted for work, significant experience and professional achievements in information technology, cybersecurity and project management. It also lists objective prerequisites and confirms that admission is not automatic and is not based on payment of dues.



They include:



\begin{itemize}

 \item Advanced technical education confirming expertise in IT, cybersecurity, systems architecture, digitalization and innovation.

 \item More than 10 years of professional and research experience, with at least 5 years in IT leadership positions.

 \item International project-management certifications (including Product Owner and Product Manager).

 \item Successful completion of advanced qualification examinations such as Program Increment (PI) Planning, Leadership for PI Planning, Iteration Execution and PI Execution.

 \item Written recommendations from recognized experts in IT and digitalization, confirming impeccable professional reputation.

 \item Authorship of original and effective developments and methodologies in IT, innovation and technology transfer.

 \item Presentations delivered at national and international conferences.

\end{itemize}



The decision does not use the word “outstanding.” The level of achievement follows from the multifactor prerequisites, the documented record and the expert review that leads to selective admission.



\textbf{Proof that applicants are judged by recognized national or international experts}


The letter says:
\emph{“A candidate is admitted by the decision of the Association Council. The Council consists of leading professional experts in information technology and cybersecurity, certified information security officers and project managers of national and international level.”}



KISA Admission Decision (English translation).



The record identifies the decision-makers by name and title as shown in the decision and on the association roster, such as the Chair, Viktor Pokusov, and council members who hold national leadership roles in cybersecurity and IT. This shows that applicants are judged by recognized experts consistent with the regulatory standard for expert evaluation.



An official entry on the national portal Career.enbek.kz shows accreditation by the National Chamber of Entrepreneurs “Atameken” as a Center for Recognition of Professional Qualifications in information security and in information and communication technologies.


As stated in the letter:
\emph{“Functions include development of professional standards, standardized competency assessments with employer participation and certification of qualifications in core specialties of information security and information and communication technologies.”}



Career.enbek.kz registry entry (English translation).



This confirms an expert evaluation function in the same field.



Publicly available materials also describe the following activities related to the establishment and national activities:



\begin{itemize}

 \item Established in August 2017 with the aim of consolidating scientific, industrial, and government expertise to implement national priorities in the field of security and informatization.

 \item University and industry councils on education and staffing in the field of cybersecurity.

 \item Public speeches by Chairman Viktor Pokusov on policy and security issues.

 \item National round tables and consultative events in Astana.

\end{itemize}



The record shows a professional association in information security and information technology. Membership is conditioned on objective achievements that include education, leadership, certifications, methods and public speaking. The selection is made by recognized experts who serve on the Association Council. There is independent national accreditation for qualification recognition and competency assessment. Accordingly, the record satisfies the membership criterion for associations that admit members on the basis of outstanding achievements, as judged by recognized experts.

\pagebreak