% ==============================
% EB-1A — Criterion 5 (Major Significance)
% Expanded analysis from expert letters and corroborating exhibits
% ==============================

\subsection{Evidence of \mrls original scientific and business-related contributions of \emph{major significance} to the field}
\label{subsec:Contributions}

\noindent\textbf{USCIS framework.} Under Criterion~5, adjudicators first verify that the person’s work is \emph{original}, and then determine whether those contributions are of \emph{major significance} to the field. Each independent expert letter below is analyzed using a consistent structure:
(i) author’s authority and basis of knowledge; (ii) the concrete technical problem; (iii) the solution as implemented; (iv) objective operational outcomes (including any quantitative metrics noted by the author);
(v) why this evidence meets the USCIS “major significance” standard; and (vi) the exhibit(s) substantiating the author’s authority.

% =========================================================
% Letter A — Deputy Mayor (Institutional executive context)
% =========================================================
\subsubsection{Official Letter A — Yerzhan Baiken (Deputy Mayor of Astana): Modernization of iKOMEK109 as a city situation center; project portfolio governance; and verified registry accuracy for elections}
\label{subsubsec:LetterBaiken}

\SubSubSubSection{Author’s authority and vantage point}
As \emph{Deputy Mayor of Astana}, Mr.~Baiken is responsible for citywide operations, including iKOMEK109 (the capital’s service and incident-response center). His letter presents the executive scope of work overseen and the outcomes attributable to the Development Department led by Mr.~Taximov. \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\SubSubSubSection{Problem and mandate}
The city required a situation center that would (a) unify and manage citizen requests through the ``109'' single-contact line and digital channels; (b) provide transparent, auditable workflows from intake to resolution; and (c) ensure the accuracy of foundational registries used for essential functions, including the assignment of voters to precincts during elections. \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\SubSubSubSection{Solution as implemented (portfolio, platforms, and data)}
Mr.~Baiken describes a portfolio-managed modernization program executed under Mr.~Taximov’s leadership: standardized project management practices; executive dashboards and KPIs; and end-to-end data plumbing connecting intake channels to operational units. The Deputy Mayor also details an \emph{automated} address-to-precinct binding pipeline that added \emph{513 addresses} and bound \emph{25{,}036 voters} during the election cycle, evidencing continuous registry hygiene and geospatial correctness. \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\SubSubSubSection{Operational outcomes documented by the official}
The letter ties the modernization to measurable improvements at the city level: throughput in processing citizens’ appeals; executive visibility into backlogs and SLAs; and, specifically for elections, verifiable counts of newly added addresses and voters bound to correct precincts through a documented, auditable workflow. \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\SubSubSubSection{Why this meets USCIS Criterion~5}
\emph{Originality} is demonstrated by authoring and institutionalizing the city’s situation-center operations and the automated geospatial registry pipeline. \emph{Major significance} is shown by the citywide scope (situation center governance), by the election-period registry accuracy work with explicit counts, and by the Deputy Mayor’s own attestation. \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\SubSubSubSection{Authority exhibit}
Deputy Mayor’s official letter: \ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}

\bigskip

% =========================================================
% Letter B — Beisenbayev (iKOMEK109 Development Director)
% =========================================================
\subsubsection{Expert Letter B — Anuar Beisenbayev (Director of Development, iKOMEK109): Omnichannel CRM/automation backbone; election data engineering to 100\%; and registered platform IP}
\label{subsubsec:LetterBeisenbayev}

\SubSubSubSection{Author’s authority and vantage point}
Mr.~Beisenbayev is \emph{Director of the Development Department} at iKOMEK109; he directly supervised platform engineering and data pipelines where Mr.~Taximov’s work was central. \ExhibitRef{BeisenbayevCV}

\SubSubSubSection{Problem}
Fragmented intake channels (109 phone line, mobile app, Telegram bots) and legacy processes created duplications and opacity; prior to Mr.~Taximov’s work, there was no single, modern backbone to integrate channels, automate workflows, and provide authoritative analytics to executives. \ExhibitRef{BeisenbaevLetter}

\SubSubSubSection{Solution: unified platform and data engineering}
Mr.~Beisenbayev attributes three core results to Mr.~Taximov:
\begin{enumerate}
  \item \textbf{Omnichannel CRM/automation.} Authored the technical architecture and led delivery of a modern platform stack (React, TypeScript, Next.js, Prisma, PostgreSQL) unifying 109 calls, the mobile app, and Telegram bots, with workflow automation and analytics dashboards.
  \ParagraphQuoteByExhibit{\textit{``Mr.~Taximov authored the new CRM platform (React, TypeScript, Next.js, Prisma, PostgreSQL), coordinated the engineering team, and integrated omnichannel intake (call center 109, mobile app, Telegram bots), with automation and analytics dashboards.''}}{Anuar Beisenbayev (Eng. transl.)}{BeisenbaevLetter}
  \item \textbf{Election voter-roll accuracy from 84\% to 100\%.} Implemented Geonomics/ArcGIS plus Python/SQL pipelines to automate address binding and perform large-scale corrections (more than \emph{50{,}000} records), lifting election-period list accuracy from \emph{84\%} to \emph{100\%}.
  \ParagraphQuoteByExhibit{\textit{``Using Geonomics, ArcGIS, and Python/SQL pipelines, Mr.~Taximov corrected more than 50,000 address records and increased voter-list accuracy from 84\% to 100\% for the election period.''}}{Anuar Beisenbayev (Eng. transl.)}{BeisenbaevLetter}
  \item \textbf{Registered IP (NextITSM).} The \emph{NextITSM} platform was registered in the national intellectual-property system, evidencing the originality of the workflow/data-model solution.
  \ParagraphQuoteByExhibit{\textit{``The NextITSM platform was registered in the intellectual property system, confirming the originality of the solution.''}}{Anuar Beisenbayev (Eng. transl.)}{BeisenbaevLetter}
\end{enumerate}

\SubSubSubSection{Implementation notes}
The letter describes an engineered pipeline rather than ad hoc fixes: geospatial binding to precinct polygons; scripted corrections; and a consistent data load path feeding executive dashboards. \ExhibitRef{BeisenbaevLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
\emph{Originality:} authored a new omnichannel architecture and an IP-registered platform; \emph{Major significance:} citywide adoption and election-critical accuracy (84\%$\to$100\%, 50{,}000+ records corrected) with continuing operational use. \ExhibitRef{BeisenbaevLetter,BeisenbayevCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{BeisenbaevLetter}
\ExhibitRef{BeisenbayevCV}

\bigskip

% =========================================================
% Letter C — Kudaibergenov (Chief Inspector, Digitalization & IT)
% =========================================================
\subsubsection{Expert Letter C — Azat Kudaibergenov (Chief Inspector for Digitalization and IT, Mayor’s Office of Astana): First-proposed algorithmic registry maintenance and replication to other cities}
\label{subsubsec:LetterKudaibergenov}

\SubSubSubSection{Author’s authority and vantage point}
Mr.~Kudaibergenov serves in the Mayor’s Office with responsibility over digitalization/IT inspections and cross-jurisdictional diffusion, giving him a field-wide view of what gets adopted by peer cities. \ExhibitRef{KudaibergenovCV}

\SubSubSubSection{Problem}
Static lists compiled by manual canvassing could not keep pace with urban dynamics; precinct-binding relied on episodic updates and risked inaccuracies during election cycles.

\SubSubSubSection{Solution and diffusion}
Mr.~Kudaibergenov states Mr.~Taximov \emph{first proposed} an algorithm that automatically updates resident data and maintains relevance \emph{in real time}, forming lists from a \emph{single authoritative source}; he further writes the approach became an example for other regions and influenced similar systems in other cities.
\ParagraphQuoteByExhibit{\textit{``Taximov first proposed an innovative algorithm for automatically updating residents’ data … its implementation formed lists from a single source, eliminated door-to-door checks, and enabled real-time relevance. The algorithm became an example for other regions and influenced the development of similar systems in other cities.''}}{Azat Kudaibergenov (Eng. transl.)}{KudaiBergenovLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
\emph{Originality} is explicit (“first proposed”); \emph{major significance} is shown by adoption beyond the originating city and by the role of this registry integrity in essential governance processes. \ExhibitRef{KudaiBergenovLetter,KudaibergenovCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{KudaiBergenovLetter}
\ExhibitRef{KudaibergenovCV}

\bigskip

% =========================================================
% Letter D — Sidelkovskaya (National Big-Data leader)
% =========================================================
\subsubsection{Expert Letter D — Ainur Sidelkovskaya (Managing Partner, A2DATA; national Big-Data leader): Implementable city-scale analytics; public dissemination; top-decile standing}
\label{subsubsec:LetterSidelkovskaya}

\SubSubSubSection{Author’s authority and vantage point}
Ms.~Sidelkovskaya is a senior Big-Data executive and educator with national-level leadership across ministries and enterprises; her CV demonstrates broad program ownership and teaching roles. \ExhibitRef{SidelkovskayaCV}

\SubSubSubSection{Assessment of Mr.~Taximov’s contribution}
The letter emphasizes \emph{implementability}: city-scale data collection and channeling; analytics that directly improve management; and public dissemination through articles and major events. She concludes Mr.~Taximov is in the \emph{top 10\%} of specialists in IT, digital tech, urban management, and innovation.
\ParagraphQuoteByExhibit{\textit{``He offers practical mechanisms to collect, channel, and analyze city-scale data so that it directly improves urban management … Therefore, I am convinced that Askar is among the top 10\% of specialists in Kazakhstan in the field of IT, digital technologies, urban management and innovation projects.''}}{Ainur Sidelkovskaya (Eng. transl.)}{SidelkovskayaLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
\emph{Originality} is seen in the mechanisms and architectures her letter describes; \emph{major significance} is supported by her credentials, public dissemination, and cross-departmental use in the municipal setting. \ExhibitRef{SidelkovskayaLetter,SidelkovskayaCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{SidelkovskayaLetter}
\ExhibitRef{SidelkovskayaCV}

\bigskip

% =========================================================
% Letter E — Tokayev (Information Security Officer)
% =========================================================
\subsubsection{Expert Letter E — Aidos Tokayev (Information Security Officer): Government-wide cybersecurity architectures; quantified reductions in risk and response time}
\label{subsubsec:LetterTokayev}

\SubSubSubSection{Author’s authority and vantage point}
A practicing Information Security Officer with formal certifications (incl. ISO/IEC 27001, Fortinet) and state roles, Mr.~Tokayev evaluates operational security outcomes in government systems. \ExhibitRef{TokayevCV}

\SubSubSubSection{Problem}
Prior to the cited work, government systems faced data-exfiltration and personal-data handling risks, and fragmented processes that prolonged support response times.

\SubSubSubSection{Solution and outcomes}
Mr.~Tokayev writes that Mr.~Taximov’s solutions and policies are applied \emph{across government systems}, reporting: \emph{17\%} reduction in unlawful data transfers; \emph{28\%} decrease in unwanted personal-data deletions; and support response time cut from \emph{60} to \emph{15 minutes}.
\ParagraphQuoteByExhibit{\textit{``He reduced unlawful data transfers by 17\%, decreased unwanted personal-data deletions by 28\%, and cut support response time from 60 to 15 minutes … his solutions and policies are applied across government systems.''}}{Aidos Tokayev (Eng. transl.)}{TokayevLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
\emph{Originality} is present in the architectures/policies deployed; \emph{major significance} is shown by government-wide application and quantified improvements that reduce risk and accelerate response. \ExhibitRef{TokayevLetter,TokayevCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{TokayevLetter}
\ExhibitRef{TokayevCV}

\bigskip

% =========================================================
% Letter F — State Technical Service (national cyber operator)
% =========================================================
\subsubsection{Official Letter F — JSC ``State Technical Service'' (national cyber operator): Platforms in daily use — \emph{Synaq}, \emph{ScanKZ}, and a closed cyber media-monitoring bot}
\label{subsubsec:LetterSTS}

\SubSubSubSection{Author’s authority and vantage point}
The national operator for cybersecurity of e-government and critical infrastructure confirms three platforms to which Mr.~Taximov contributed that are \emph{used in daily operations}. \ExhibitRef{STSContribution}

\SubSubSubSection{Solution components and usage}
\begin{itemize}
  \item \textbf{Closed cyber media-monitoring bot.} Manages keywords; provides a closed review chat; runs scheduled searches every four hours (including Google Programmable Search); sends notifications; handles user management and logging; and is used by STS units \emph{every day}.
  \item \textbf{\emph{Synaq} — digital security testing/attestation.} Orchestrates formation/approval/signing/sending of requests for quotations; receives electronic quotations with \emph{automated cost calculation}; forms/approves/signs \emph{test requests}; and generates \emph{electronic protocols} downloadable by applicants.
  \item \textbf{\emph{ScanKZ} — nationwide vulnerability discovery.} Automatically searches IP ranges and domains for open ports, device versions, services, and known vulnerabilities (including TLS/SSL certificates and OS fingerprints), enabling identification of vulnerable assets and owner notifications for remediation via KZ-CERT.
\end{itemize}
\ExhibitRef{STSContribution}

\SubSubSubSection{Why this meets USCIS Criterion~5}
Originality is reflected in the digitized attestations (e-protocols), persistent national scanning, and operational media monitoring; major significance is established by daily use in core national cybersecurity work. \ExhibitRef{STSContribution}

\SubSubSubSection{Authority exhibit}
\ExhibitRef{STSContribution}

\bigskip

% =========================================================
% Letter G — Dastan Esmagambetov (Digital transformation & cybersecurity)
% =========================================================
\subsubsection{Expert Letter G — Dastan Esmagambetov (Digital transformation and cybersecurity leader): Sector standards, diffusion, and life-safety outcomes via ``Life Signal'' and Big-Data methods}
\label{subsubsec:LetterEsmagambetov}

\SubSubSubSection{Author’s authority and vantage point}
A senior leader across public/private programs, Mr.~Esmagambetov evaluates sector-wide standards, diffusion, and public-interest outcomes; his CV confirms the breadth of responsibility. \ExhibitRef{EsmagambetovCV}

\SubSubSubSection{Problem and contribution}
His letter characterizes Mr.~Taximov’s work as \emph{setting new standards} in three domains: geospatially-aware registry integrity (\emph{Geonomics}); emergency response integration for the 112 service (\emph{Life Signal}); and cybersecurity combining sandboxing with machine learning.

\SubSubSubSection{Outcomes (as stated by the author)}
He reports that \emph{Life Signal} reduced emergency response time from \emph{10} to \emph{7 minutes} and reduced harm by \emph{25\%}. He further notes dissemination through major events (e.g., GITEX Global; Digital Bridge) and public-sector strategies. \ParagraphQuoteByExhibit{\textit{``‘Life Signal’ cut 112 response from 10 to 7 minutes and reduced harm by 25\%, saving dozens of lives.''}}{Dastan Esmagambetov (Eng. transl.)}{EsmagambetovLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
The emergency telematics and cyber ML/sandboxing patterns are \emph{original} contributions, and the quantified public-safety improvements and diffusion demonstrate \emph{major significance}. \ExhibitRef{EsmagambetovLetter,EsmagambetovCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{EsmagambetovLetter}
\ExhibitRef{EsmagambetovCV}

\bigskip

% =========================================================
% Letter H — Panchenko (Operational computer vision)
% =========================================================
\subsubsection{Expert Letter H — Dmitry Panchenko: City-scale computer vision — \emph{Target AI} pilot (600{+} cameras), enforcement uplift, and integration to standards}
\label{subsubsec:LetterPanchenko}

\SubSubSubSection{Author’s vantage point}
Mr.~Panchenko writes after multiple years of joint work, with specific attention to productization and the bridge from lab models to stable city operations. \ExhibitRef{PanchenkoLetter}

\SubSubSubSection{Problem}
Before the pilot, vision analytics existed in limited, siloed deployments without a production-grade stream-processing backbone or broad device integration across the city.

\SubSubSubSection{Solution and outcomes}
Under Mr.~Taximov’s leadership, the \emph{Target AI} pilot connected \emph{over 600 digital cameras}, integrated specialized modules (face, smoke, abandoned/lost objects, license plates), complied with international standards (including IEC~60529 and PAL), and optimized stream-processing for dashboards, reports, and APIs. The letter documents enforcement outcomes: \emph{+37\%} in license-plate violation detection and \emph{3{,}755} illegal-dumping incidents recorded via AI. \ExhibitRef{PanchenkoLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
The deployment architecture and integration are \emph{original} in their scale and completeness; the measurable enforcement gains demonstrate \emph{major significance} for urban governance. \ExhibitRef{PanchenkoLetter}

\SubSubSubSection{Authority exhibit}
\ExhibitRef{PanchenkoLetter} % If your key is PunchenkoLetter, adjust this reference.

\bigskip

% =========================================================
% Letter I — Dr. Shyngys Kenshimov (PhD; Associate Professor)
% =========================================================
\subsubsection{Expert Letter I — Dr.~Shyngys Kenshimov (Associate Professor, PhD): Productization leadership enabling ML adoption}
\label{subsubsec:LetterKenshimov}

\SubSubSubSection{Author’s vantage point}
An academic expert in computer vision and machine learning, Dr.~Kenshimov focuses on the transition from research prototypes to operational systems. \ExhibitRef{KenshimovLetter}

\SubSubSubSection{Contribution described}
His letter emphasizes Mr.~Taximov’s leadership in \emph{productization}: designing the data and deployment pipelines, reliability controls, and team processes needed for organizations to adopt ML systems \emph{in practice}. \ExhibitRef{KenshimovLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
By enabling the research-to-operations bridge at scale, the contribution is \emph{original} (systems/process design) and of \emph{major significance} (wider ML adoption in real-world settings). \ExhibitRef{KenshimovLetter}

\SubSubSubSection{Authority exhibit}
\ExhibitRef{KenshimovLetter}

\bigskip

% =========================================================
% Letter J — Kakhar Kashimov (CTO; Chief Software Architect)
% =========================================================
\subsubsection{Expert Letter J — Kakhar (Kakhar) Kashimov (CTO; Chief Software Architect): Wireless Wi-Fi geophone arrays and ``Life Signal'' 112 integration — independent implementations}
\label{subsubsec:LetterKashimov}

\SubSubSubSection{Author’s authority and vantage point}
Mr.~Kashimov signs as \emph{CTO, Chief Software Architect}; his CV confirms deep industry experience in distributed systems. \ExhibitRef{KaharCV}

\SubSubSubSection{Technical problems addressed}
(a) Seismic prospecting systems constrained by kilometers of cable and limited spatial density; (b) emergency response workflows lacking precise mobile-caller geolocation integration.

\SubSubSubSection{Solutions and implementation}
He details two solutions co-designed with Mr.~Taximov:
\begin{itemize}
  \item \textbf{Wireless Wi-Fi geophone arrays.} A two-tier, high-throughput network architecture using Wi-Fi at the collection and backhaul tiers, with satellite-based positioning/cooperative localization and time synchronization, enabling high-density seismic data without cabled layouts.
  \item \textbf{``Life Signal'' 112 integration.} A connection scheme for emergency calls that integrates Android/iOS caller geolocation with dispatch center workflows to accelerate response.
\end{itemize}
The letter specifies that these solutions were \emph{implemented by independent organizations} in industrial sensing and public safety. \ExhibitRef{KaharLetter}

\SubSubSubSection{Why this meets USCIS Criterion~5}
Cross-organizational implementations are strong evidence of field-level significance; the architectures themselves reflect \emph{original} cross-domain systems engineering. \ExhibitRef{KaharLetter,KaharCV}

\SubSubSubSection{Authority exhibits}
\ExhibitRef{KaharLetter}
\ExhibitRef{KaharCV}

\bigskip

% =========================================================
% Letter K — General Director (EKK / Elorda Construction Company)
% =========================================================
\subsubsection{Official Letter K — R.\,S. Auekelov (General Director, ``Elorda Construction Company'' LLP): Digital finance, BIM/CV adoption, and quantified efficiencies}
\label{subsubsec:LetterEKK}

\SubSubSubSection{Author’s authority and vantage point}
The General Director of a large developer attests to the operational and financial outcomes attributable to Mr.~Taximov’s contributions. \ExhibitRef{Рекомендательное_письмо_ЕКК_Таксимов_А_Б_1}

\SubSubSubSection{Problems addressed}
Long-standing ``problem'' housing projects requiring financing and completion; high logistics costs; lagging field visibility and coordination; and lengthy design/approval cycles.

\SubSubSubSection{Solutions and outcomes}
The letter credits Mr.~Taximov with: securing \emph{51 million} tenge in financing to resume/completed projects; a \emph{digital financial model} that reduced logistics costs by \emph{30\%}, saving \emph{156.9 million} tenge annually, and increasing profit by \emph{7–9\%}; completion of \emph{8} problem sites (including \emph{12} multi-apartment complexes); deployment of \emph{computer-vision} site surveillance; and \emph{BIM} workflows (Model Studio Soft modules for building/HVAC/telecom/CAD library) to optimize decisions and accelerate approvals. \ExhibitRef{Рекомендательное_письмо_ЕКК_Таксимов_А_Б_1}

\SubSubSubSection{Why this meets USCIS Criterion~5}
Quantified cost savings and profit growth, the completion of multi-complex sites, and the adoption of BIM/CV practices demonstrate \emph{major significance} within the sector; the underlying financial and engineering models show \emph{original} applied program leadership. \ExhibitRef{Рекомендательное_письмо_ЕКК_Таксимов_А_Б_1}

\SubSubSubSection{Authority exhibit}
\ExhibitRef{Рекомендательное_письмо_ЕКК_Таксимов_А_Б_1}

\bigskip

% =========================================================
% Synthesis across letters
% =========================================================
\subsubsection{Synthesis across independent letters and records}
\label{subsubsec:ContributionsSynthesisExpanded}
Across municipal and national institutions—and across government and industry—the independent authors (Deputy Mayor, development director, chief inspector for digitalization, national Big-Data leader, information-security officer, the national cyber operator, CTO/architect, an academic ML faculty member, and a construction CEO) converge on the same picture:
\begin{itemize}
  \item \textbf{Original platforms, algorithms, and architectures.} A unified omnichannel CRM/automation backbone; automated geospatial registry and election pipelines; national cyber platforms used daily (\emph{Synaq}, \emph{ScanKZ}, and a closed cyber media-monitoring bot); city-scale computer-vision productization over \emph{600+} cameras; emergency-response telematics (``Life Signal''); wireless Wi-Fi geophone arrays; and sectoral BIM/CV implementations.
  \item \textbf{Operational outcomes (with metrics stated by the authors).} Election voter-list accuracy \emph{84\%$\to$100\%} with \emph{50{,}000+} address corrections; additional election-period registry work of \emph{513} addresses and \emph{25{,}036} voters bound; enforcement uplift (\emph{+37\%} license-plate violations; \emph{3{,}755} illegal-dumping cases); cybersecurity effects (\emph{−17\%} unlawful data transfers; \emph{−28\%} unwanted personal-data deletions; response time \emph{60$\to$15} minutes); emergency response (\emph{10$\to$7} minutes; \emph{−25\%} harm); and construction efficiencies (\emph{−30\%} logistics; \emph{+7–9\%} profit).
  \item \textbf{Adoption and replication.} The registry algorithm and city-information-center model influencing other cities; platforms operated daily by the national cyber operator; and cross-industry implementations in public safety and industrial sensing.
  \item \textbf{Authority and credibility.} Each author’s letter provides detailed substance; CVs and official positions establish the basis of knowledge; outcomes and usage are embedded in public-interest operations (elections, safety, cybersecurity, housing).
\end{itemize}
\noindent \textbf{Conclusion.} Under Criterion~5, Mr.~Taximov’s contributions are both \emph{original} and of \emph{major significance} to municipal digital governance, national cybersecurity operations, computer-vision deployment at city scale, emergency-response telematics, and construction informatics.

% =========================================================
% Exhibits referenced in this section
% =========================================================
\SubSubSubSection{Exhibits referenced in this section}
\ExhibitRef{Рекомендательное_письмо_зам_акима_Байкен_Е_}
\ExhibitRef{BeisenbaevLetter}
\ExhibitRef{BeisenbayevCV}
\ExhibitRef{KudaiBergenovLetter}
\ExhibitRef{KudaibergenovCV}
\ExhibitRef{SidelkovskayaLetter}
\ExhibitRef{SidelkovskayaCV}
\ExhibitRef{TokayevLetter}
\ExhibitRef{TokayevCV}
\ExhibitRef{STSContribution}
\ExhibitRef{EsmagambetovLetter}
\ExhibitRef{EsmagambetovCV}
\ExhibitRef{PanchenkoLetter} % If the uploaded file is `PunchenkoLetter`, change this key here and above.
\ExhibitRef{KenshimovLetter}
\ExhibitRef{KaharLetter}
\ExhibitRef{KaharCV}
\ExhibitRef{Рекомендательное_письмо_ЕКК_Таксимов_А_Б_1}
