\subsubsection{Municipal State Enterprise “iKOMEK109” — City Monitoring \& Rapid Response Center}
\label{subsubsec:RoleIKomek}

\SubSubSubSection{Context and the organization's distinguished reputation}
\textbf{iKOMEK109} is the capital city’s unified 3-1-1–style situation center under the Administration of Astana. It integrates (1) a 24/7 omnichannel \emph{Contact Center}, (2) a \emph{Situation Center} that fuses CCTV/IoT feeds for urban safety and (3) a \emph{Data \& Analytics Unit} that drives executive decision-making across utilities, transport, housing and public space maintenance. The organization’s scale and visibility are evidenced by:
\begin{itemize}
  \item \textbf{Operational scale:} The official site describes iKOMEK’s role as the citywide hub for appeals and rapid response; it reports \textbf{over 2.2 million} annual citizen requests. \ExhibitRef{IKomekSiteShot}
  \item \textbf{Independent press coverage:} Forbes Kazakhstan covered Mr.\ Taximov’s appointment as Head (2022) and later reported \textbf{7.5 million+} requests processed over four years; additional national media document operational outcomes (e.g., million+ appeals, fines for code violations). \ExhibitRef{IKomekPress}
  \item \textbf{Public engagement:} The verified Instagram account \emph{@ikomek109} shows \textbf{230{,}000 followers} and \textbf{5{,}900+ posts}, confirming continuous public-facing operations. \ExhibitRef{IKomekInstagramShot}
  % --- Added evidentiary bullets that use the new exhibits ---
  \item \textbf{Official government confirmation of mandate and scale:} The Government of Kazakhstan portal (“About iKomek 109”) confirms that iKOMEK is the city’s \textbf{unified, 24/7} contact center, lists all official intake channels (Akimat web service, Telegram bot, iKOMEK109 mobile app on Play Market and App Store, Smart Astana app, email \texttt{109@ikomekastana.kz} and the free short number \textbf{109}) and notes a catalog of \textbf{2{,}500+ services} with \textbf{85\%} of requests resolved on the first call. \ExhibitRef{IKomekGov}
  \item \textbf{Independent municipal operator corroboration:} JSC “City Transportation Systems” (CTS) instructs residents that \textbf{all public-transport inquiries} are to be submitted through iKOMEK via the same official channels (short number 109, iKOMEK109 app, mayor’s official website, Telegram bot, Smart Astana app and email), independently validating iKOMEK’s centralized role and public authority. \ExhibitRef{IKomekCTS}
\end{itemize}
These materials collectively establish iKOMEK109 as a \textbf{distinguished municipal service and analytics enterprise} by mandate, scale and sustained public visibility. \ExhibitRef{IKomekSiteShot}\ExhibitRef{IKomekPress}\ExhibitRef{IKomekInstagramShot}

\SubSubSubSection{Appointment and scope of authority}
Mr.\ Taximov was appointed \textbf{Head of iKOMEK109} on \textbf{May 27, 2022}. His remit spanned executive program management of the contact center, the situation center and the data/analytics portfolio, with a mandate to design and implement \textbf{iKOMEK~2.0} (CRM, omnichannel intake, analytics and executive dashboards). \ExhibitRef{IKomekDeputyAkimLetter}

\SubSubSubSection{Evidence of a leading and critical role (with quantified results)}
Consistent with USCIS guidance, the Deputy Mayor's letter provides detailed, probative metrics that tie Mr.\ Taximov’s performance to city outcomes. Key items include:

\paragraph{1) Executive problem-solving cadence for the Mayor’s office.}
\ParagraphQuoteByExhibit{“He institutionalized weekly analytical reporting to the Mayor, reducing unresolved urgent issues from \textbf{112} to \textbf{27} (\textbf{−76\%}).”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
This is executive-level governance supported by \textbf{analytics and IT-driven dashboards}, i.e., leadership over the core outcome the center exists to deliver.

\paragraph{2) Systematic backlog eradication.}
\ParagraphQuoteByExhibit{“Legacy ‘Waiting’ tickets were liquidated; in 2023 alone the center closed \textbf{426{,}542} appeals, a \textbf{+28.4\%} increase vs.\ 2022.”}{Deputy MayorLetter}{IKomekDeputyAkimLetter}  
Such throughput gains are only possible with \textbf{workflow redesign, automation and KPI management}, demonstrating a critical operational role.

\paragraph{3) Digital channel growth and product management.}
\ParagraphQuoteByExhibit{“He expanded the digital channels (e.g., Telegram bot, mobile app), raising online submissions by \textbf{22\%}.”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
This shows \textbf{product leadership} over citizen interfaces and measurable adoption.

\paragraph{4) Situation Center enablement for urban safety and quality of life.}
\ParagraphQuoteByExhibit{“He coordinated modernization of more than \textbf{80} playgrounds and \textbf{43} sports grounds; \textbf{378 km} of lighting was installed; these efforts contributed to a \textbf{27.3\%} reduction in crime.”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
The role here is \textbf{critical orchestration}—connecting analytics to enforcement and infrastructure improvements.

\paragraph{5) Enforcement support and fiscal outcomes.}
\ParagraphQuoteByExhibit{“Workflows in the Situation Center supported \textbf{23} criminal cases and \textbf{19{,}384} administrative offenses, enabling collection of \textbf{KZT 52{,}008{,}750} in fines.”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
This links IT-enabled monitoring to \textbf{verified enforcement and budget impact}.

\paragraph{6) Election data integrity (data engineering leadership).}
\ParagraphQuoteByExhibit{“He led a Python/Pandas/NumPy pipeline to correct over \textbf{1{,}000} address errors and geocode \textbf{513} addresses (\textbf{25{,}036} voters), achieving \textbf{100\%} accuracy of voter lists.”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
High-stakes civic data quality shows \textbf{hands-on technical leadership} aligned with public trust.

\paragraph{7) Building the IT organization and the roadmap (‘iKOMEK 2.0’).}
\ParagraphQuoteByExhibit{“He staffed a full IT function and delivered a roadmap covering CRM, external integrations, executive ratings, DB optimization and unified channels with SSO.”}{Deputy Mayor Letter}{IKomekDeputyAkimLetter}  
Standing up the team and platform plan is a \textbf{leading role} by any corporate standard.

\SubSubSubSection{Why this meets USCIS Criterion 8}
USCIS asks whether the person’s role was \emph{leading} or \emph{critical} and whether the organization has a \emph{distinguished reputation}. iKOMEK’s statutory mandate, multi-million-appeal scale and national press coverage satisfy the organization prong. The Deputy Mayor’s detailed letter ties Mr.\ Taximov’s actions to \textbf{city-level outcomes} (crime reduction, enforcement, backlog liquidation, digital adoption, election integrity), which demonstrates both \textbf{leadership} (organizational building, strategy, executive dashboards) and \textbf{criticality} (measurable improvements to core KPIs). In addition, the \textbf{official government portal} confirms iKOMEK’s unified 24/7 mandate, service breadth and performance (2{,}500+ services; 85\% first-call resolution) and an \textbf{independent municipal operator} (CTS) directs residents to iKOMEK for all public-transport inquiries, underscoring citywide centralization and authority. \ExhibitRef{IKomekGov,IKomekCTS}

\SubSubSubSection{Corroboration in the record}
We include an internal presentation and accompanying script used to brief stakeholders on the iKOMEK 2.0 vision and the operating model, which visually shows the governance, process and analytics stack of the center. \ExhibitRef{IKomekPresentation}\ExhibitRef{IKomekPresentationScript}

\ExhibitList{
  \ExhibitRef{IKomekDeputyAkimLetter}
  \ExhibitRef{IKomekSiteShot}
  \ExhibitRef{IKomekPress}
  \ExhibitRef{IKomekInstagramShot}
  \ExhibitRef{IKomekPresentation}
  \ExhibitRef{IKomekPresentationScript}
  \ExhibitRef{IKomekGov}
  \ExhibitRef{IKomekCTS}
}
