\subsection{Published material about \mrl\ in professional or major media relating to his work}
\label{subsec:Published}

One of the key indicators of extraordinary ability is the publication of
material about the individual's work in professional, major trade
publications, or other major media outlets.
\mrls work in \fie has garnered substantial recognition in both industry and
media, demonstrating the impact and significance of his contributions.
Below are some examples of such published material:

\begin{itemize}
% \textbf{Kazakhstanskaya Pravda}
\item \textbf{\underline{Kazakhstanskaya Pravda}} is a national newspaper that has been published since 1920 and is distributed throughout the country. The newspaper's historical circulation ranges from 80,000 to 110,000 copies, and it has offices in cities throughout the country. It also received state honors, the Order of the Red Banner of Labour in 1958. The newspaper has active digital channels (its Instagram account has around 160,000 followers) and online portal with a wide national audience. These factors allow it to be classified as a major media outlet in Kazakhstan.
This national newspaper article displays iKOMEK109 under \mrl’s leadership as a 24/7 digital response and analytics ecosystem. It highlights integration with 12,000+ Sergek cameras, lists the breadth of connected agencies and notes omnichannel intake and analytics to surface risks. The piece also references \mrls academic background, 10+ publications, creation of iKOMEK~2.0 and NextITSM, the “Life Signal” geolocation service (with Google and Apple) and GIS/SDSS research for planning. 
The piece is \emph{about \mrl\ and his work}. It quotes him directly and describes results, systems, projects and researches with operational metrics. %

“Urban governance Digitalization” \emph{Kazakhstanskaya Pravda}, 18 July 2025,  Asya Petrova.\\
URL: \url{https://kazpravda.kz/n/%
tsifrovizatsiya-v-gorodskom-upravlenii/}

% \textbf{PROFIT kz}
\item \textbf{\underline{ProfIT kz}} is a specialized IT market portal. It has been operating since 2004 with professionak coverage for the information technology community in Kazakhstan. The outlet has been awarded with the National Kazakhstan Internet Award (Award.kz) in 2007 (ranked 3rd among 30 competitors in the "Mass Media" category) and 2009 (ranked 2nd among 60 competitors in "Industry and Regional Portals"). The awards display its recognition within the industry and Kazakhstan. The portal sponsors major regional and international IT conferences and exhibitions. It maintains partnerships with leading technology companies. Hence, the above factors show sustained professional standing in the IT technology-focused press.

This IT-market feature covers \mrls PROFIT Contact Day 2025 presentation of iKOMEK 2.0. It cites operational volumes, reasons for replacing the legacy system and goals of cost reduction and scalability. Features include a unified portal, field staff app, updated management panel, and AI-driven knowledge base. The article also notes the planned “Situational Map,” BI tools (Power BI, Tableau), security testing, and integration with the eOtinish system.

“iKOMEK 2.0: A new generation of digital response,” \emph{PROFIT.kz}, 13 June 2025. no individual author listed.  \\
URL:   \url{https://profit.kz/news/70858/ \\
iKOMEK-2-0-novoe-pokolenie-cifrovogo-reagirovaniya/}. 

% \textbf{Elorda info}
\item \textbf{\underline{Elorda info}} is a registered news outlet under Elorda Aqparat. The newspaper publishes daily news on capital city, national, and international developments. It has a significant audience with 69,000+ followers in the Instagram account. The publications are posted both in Kazakh and Russian languages.
This interview highlights \mrls impact on improving iKOMEK109 center. It describes the 2022 shift to a “situational center,” showing significant results and \mrls research (six peer-reviewed publications, Big Data/“Geonomics,” civic IT transformations). Also notes his presence at international forums, AI tests for classification/routing and continued infrastructure and service upgrades.

“iKOMEK109: More than 15 million requests - how the single contact center changes the capital’s cife,” \emph{Elorda.info}, 26 May 2025, Sanjar Tashibai. \\
URL: \url{https://ru.elordainfo.kz/novosti-stolicy-ru/%
ikomek109-bolee-15-millionov-obrashcheniy-kak-edinyy-kontakt-centr-menyaet-zhizn-stolicy}. 

% \textbf{DALA NEWS}
\item \textbf{\underline{DALA NEWS}} is registered as a news agency. Dala News has a public social media reach with 12,000+ followers on its Instagram account. The newspaper publishes daily content covering domestic and international news. 
The article describes \mrls leadership of iKOMEK109 and its transformation. It highlights the key improvements made under \mrls direction. The article notes his master’s degree from UCL, funded by the Bolashak scholarship. Also written about his public presentations at major forums and his official recognition. It further mentions his earlier roles in innovation and strategy, his board service in state cybersecurity, and his registered software and peer-reviewed publications.

“From the Bolashaq scholarship to the smart city: Askar Taximov's leadership and IT transformation iKOMEK109” \emph{DALA NEWS}, 7 Oct 2025, Aqtoty Zhapatova. \\
URL: \url{https://dalanews.kz/kz/article/%
ot-stypendyy-bolashaq-do-umnogo-goroda-lyderstvo-askara-taksymova-y-it-transformasyya-ikomek109.html}.

% \textbf{ErtenMedia kz}
\item \textbf{\underline{ErtenMedia kz}} is a registered Kazakh language media portal. The outlet operates a multi-platform distribution model with significant reach. It has around 40,000 followers in Instagram, about 13,000 followers in Telegram, and approximately 90,000 followers in TikTok.
An interview outlines \mrl’s leadership of iKOMEK109 as a citywide digital response and analytics system. It reports about the significant improvements under \mrls leadership. It describes the 2022 transformation to a \emph{situational center} aligned with ITSM and Smart City practices. The article highlights \mrl’s research track (peer-reviewed publications) and ongoing AI tests for automatic classification/routing, along with continued infrastructure and service upgrades.
Together, these pieces are published material about \mrl, naming and quoting him and describing his work in IT project leadership. 

“iKOMEK109: 15 million+ requests — how the single contact center changes the capital’s life,” \emph{ErtenMedia.kz}, 26 May 2025. \\
URL: \url{https://ertenmedia.kz/ikomek109-15-million-requests}. 

\end{itemize}


The recognition of \mrl's work in these major media outlets highlights \mrl's 
extraordinary ability and significant role in advancing the field of \fie. 
These publications serve as objective evidence of the widespread impact of \mrl's 
work and its importance to the community.