% ==============================
% EB-1A — Criterion 7 (Comparable Evidence)
% ==============================

\subsection{Comparable evidence of public display of work (IT Project Management)}
\label{subsec:Display}

\subsubsection{Regulatory basis and why comparable evidence applies.}
Under 8~C.F.R.\ §\,204.5(h)(4), when a criterion in §\,204.5(h)(3) (such as “artistic exhibitions or showcases”) does not readily apply to the occupation, USCIS may consider \emph{comparable evidence}. \textbf{IT project management} work is not typically displayed in artistic exhibitions; instead, a person’s work product—project methods and roadmaps, architectures, implementation case studies, technical papers and measured results—is \emph{publicly shown} at professional and scholarly conferences and then \emph{archived in citable proceedings or repositories}. The materials below therefore constitute evidence of equivalent significance. For each item, the record confirms (i) the work is Mr.~Taximov’s own work product (title–author–date) and (ii) the venue is a public, curated forum with formal publication (program page and proceedings metadata).

\subsubsection{Documented public showings of Mr.\ Taximov’s work at scientific conferences}

\paragraph{(A) International conference \emph{“Digitalization and Technological Revolutions: Current Challenges and Opportunities”} (Omega Science) — 12~July~2025.}
\textbf{Person’s work product.} Paper: \emph{“How to Detect Multi-Level Cyber Threats in Real Time \textnormal{with} AI and Behavioral Pattern Analysis”} (author: A.~Taximov; date: 12~July~2025). \\
\textbf{Public showing \& archiving.} Official program lists Mr.~Taximov as author/speaker; proceedings volume bears bibliographic imprint (ISBN) confirming publication. \ExhibitRef{Conf1Program}\ExhibitRef{Conf1Proceedings} \\
\textbf{Participation \& recognition.} Participant Certificate and Diploma (First Degree). \ExhibitRef{Conf1Certificate}\ExhibitRef{Conf1Diploma} \\
\textbf{Technical summary (from the paper).} Addresses multi-stage APT chains and limitations of signature IDS/rule SIEM; proposes an AI tool that fuses multi-source telemetry, baselines behavior, combines supervised and unsupervised detection (e.g., autoencoders/Isolation Forest), correlates anomalies into attack chains, forecasts next stages and alerts in real time. Reported testbed results: detection \(\sim95\%\) vs \(\sim80\%\) traditional; false positives \(\sim3\%\) vs \(\sim8\%\); earlier alerts at mean stage \(\sim3.3\) vs \(\sim5.0\); throughput \(\sim5{,}000\) events/s with second-level latency. Implementation: Python (pandas, scikit-learn, TensorFlow), modular design; F1 \(\approx0.93\); includes an Isolation Forest code snippet. \\
\textbf{About the venue/publisher (credibility).} Organizer: International Centre for Innovative Research “Omega Science”; proceedings issued as citable book series and cataloged by university libraries. \\
\textbf{Comparable-evidence note.} Public, curated conference + citable proceedings = a professional showcase of Mr.~Taximov’s work.

\paragraph{(B) LXXXIII International Scientific–Practical Conference \emph{“World Science: Problems and Innovations”} — 30~May~2025 (Penza).}
\textbf{Person’s work product.} Paper: \emph{“Algorithm for Developing Post-Quantum Cryptography to Protect Critical Infrastructure \textnormal{Against} Quantum Attacks (LatticeCI)”} (author: A.~Taximov; date: 30~May~2025). \\
\textbf{Public showing \& archiving.} Proceedings identify series; paper appears with editor/publisher metadata (ISBN/series). \ExhibitRef{Conf2Proceedings}\ExhibitRef{Conf2Article} \\
\textbf{Participation \& recognition.} Certificate and Diploma. \ExhibitRef{Conf2Certificate}\ExhibitRef{Conf2Diploma} \\
\textbf{Technical summary (from the paper).} Surveys PQC families (e.g., CRYSTALS-Kyber/Dilithium, Classic McEliece, SPHINCS+); contribution is \emph{LatticeCI}, a lattice-based KEM over \(R=\mathbb{Z}_q[x]/(x^N-1)\) with small-coefficient secrets, encaps \(C=p\cdot r\*h+M \bmod q\), decaps via multiplication/reduction to recover \(M\); FO-style CCA hardening; SHA-2/SHA-3/HKDF (AES variant where HW AES exists). Reported figures: pk \(\sim384\)~B, ct \(\sim384\)~B; MCU exchange \(\sim10\text{–}15\)~ms (cf. Kyber-512 15–20~ms; RSA-2048 \(\sim50\text{–}100\)~ms); target security \(\gtrsim2^{128}\) classical at \(N\approx256,\, q\approx2^{11}\) with small noise. Deployment path includes hybrid channels and legacy gateways. \\
\textbf{About the venue/publisher (credibility).} Organizer: International Centre for Scientific Cooperation “Science and Education”; proceedings publicly released with bibliographic data. \\
\textbf{Comparable-evidence note.} Editorially compiled, publicly distributed proceedings demonstrate a curated public showing.

\paragraph{(C) International Scientific Conference \emph{“Modern Technologies. Technical and Natural Sciences”} — 5~June~2025.}
\textbf{Person’s work product.} Paper: \emph{“Optimization of Cloud-System Performance Using Adaptive Machine-Learning Algorithms”} (author: A.~Taximov; date: 5~June~2025). \\
\textbf{Public showing \& archiving.} Certificate confirms presentation and publication; proceedings list the paper. \ExhibitRef{Conf3Certificate}\ExhibitRef{Conf3Proceedings} \\
\textbf{Technical summary (from the paper).} Survey-style treatment of adaptive ML (neural networks/deep learning) to speed queries (learned indexing/plan selection, anticipatory caching), adapt execution to workload shifts, forecast DB load for proactive autoscaling and improve data quality via anomaly detection and clustering (autoencoders, GANs; t-SNE/UMAP). Notes containerized/cloud stacks (Docker/Kubernetes) and monitoring integration. \\
\textbf{Comparable-evidence note.} Public presentation + proceedings archiving = professional display of work.

\paragraph{(D) XLIII All-Russian Scientific–Practical Conference \emph{“Modern Methods and Innovations in Science”} — May~2025.}
\textbf{Person’s work product.} Paper: \emph{“Mechanism of Accelerated Technology Transfer from Scientific Laboratories to Industry of Kazakhstan (TTEP)”} (author: A.~Taximov; date: May~2025). \\
\textbf{Public showing \& curation.} Proceedings state materials are \emph{selected scientific works} recommended by the Editorial Publishing Council (protocol/date). \ExhibitRef{Conf4Proceedings}\ExhibitRef{Conf4Article} \\
\textbf{Participation documents.} Certificate and diploma. \ExhibitRef{Conf4Certificate}\ExhibitRef{Conf4Diploma} \\
\textbf{Technical summary (from the paper).} Proposes a \emph{Technology Transfer Ecosystem Platform (TTEP)}: components include a technology registry, marketplace, ML-based partner matching, IP/legal support, training/mentorship, funding access and analytics; envisages cloud/AI (and blockchain for transaction/IP security). Rollout: feasibility (3–6~mo) \(\rightarrow\) build (6–12~mo) \(\rightarrow\) 1–2 region pilot (6~mo) \(\rightarrow\) national launch (12~mo) \(\rightarrow\) continuous optimization; indicative budget USD~5–10M; roles for state, labs, industry, investors. Expected outcomes stated: \(+20\text{–}30\%\) commercialization growth within first 3~years, job creation, stronger partnerships, focus on green tech. \\
\textbf{Comparable-evidence note.} Editorial selection + publication provide a curated, public venue.

\paragraph{(E) LXXXV International Scientific–Practical Conference series \emph{“Scientific Forum: Innovative Science”} — Issue~6(85), 2025.}
\textbf{Person’s work product.} Paper: \emph{“Methodology of Data-Transfer Protocol Standardization for Cross-Platform Integration of IoT Devices”} (author: A.~Taximov; issue: 6(85), 2025). \\
\textbf{Public showing \& archiving.} Proceedings front matter identifies issue and lists the paper; electronic versions are placed in national repositories (e.g., eLIBRARY/RSCI). \ExhibitRef{Conf5Proceedings} \\
\textbf{Participation documents.} Certificate and diploma. \ExhibitRef{Conf5Certificate}\ExhibitRef{Conf5Diploma} \\
\textbf{Technical summary (from the paper).} Presents a multi-step methodology to solve IoT interoperability: (1) unified transport via IP gateways for non-IP links (BLE/Zigbee/LoRa/legacy buses); (2) single application protocol (recommends MQTT) with brokered hub-and-spoke; (3) unified data model via standard schemas (JSON/JSON-Schema or Protocol Buffers) managed in a “cloud data dictionary”; (4) adapters for legacy gear; (5) conformance certification; (6) versioning/governance. Reported benefits: interfaces drop from \(n(n-1)/2\) to \(n\); lower overhead replacing HTTP with MQTT; \(\sim\)one-third faster device onboarding; simpler, consistent security controls. Domains discussed include industrial automation, utilities/smart city and healthcare (HL7/FHIR). \\
\textbf{Comparable-evidence note.} Citable proceedings and repository placement evidence a public, durable showing.

\SubSubSubSection{Why this satisfies Criterion 7 (via comparable evidence)}
% Across these items, Mr.~Taximov’s \emph{own work product} (titles, authorship, dates shown) was \textbf{publicly presented} and \textbf{archived} in curated conference proceedings with bibliographic metadata. Because artistic exhibitions do not readily apply to STEM product/program leadership, these conferences are \emph{comparable in significance} under 8~C.F.R.\ §\,204.5(h)(4).
Across these items, Mr.~Taximov’s \emph{own work product} (titles, authorship, dates shown) was \textbf{publicly presented} and \textbf{archived} in curated conference proceedings with bibliographic metadata. Since artistic exhibitions do not readily apply to STEM product/program leadership, these conferences are \emph{comparable in significance} under 8~C.F.R.\ §,204.5(h)(4).

\ParagraphSmall{Translations.} Certified English translations are provided for all non-English documents cited in this section.

\ExhibitList{
  \ExhibitRef{Conf1Program}
  \ExhibitRef{Conf1Proceedings}
  \ExhibitRef{Conf1Certificate}
  \ExhibitRef{Conf1Diploma}
  \ExhibitRef{Conf2Proceedings}
  \ExhibitRef{Conf2Article}
  \ExhibitRef{Conf2Certificate}
  \ExhibitRef{Conf2Diploma}
  \ExhibitRef{Conf3Certificate}
  \ExhibitRef{Conf3Proceedings}
  \ExhibitRef{Conf4Proceedings}
  \ExhibitRef{Conf4Article}
  \ExhibitRef{Conf4Certificate}
  \ExhibitRef{Conf4Diploma}
  \ExhibitRef{Conf5Proceedings}
  \ExhibitRef{Conf5Certificate}
  \ExhibitRef{Conf5Diploma}
}

\pagebreak