\section{Summary of \mrls achievements and qualifications}


% \noindent This petition presents \mrl{} as an IT Project Manager. He works in IT product management, data platforms, and cybersecurity. His projects support government agencies and private businesses. We include his résumé \ExhibitRef{Resume} and diplomas \ExhibitRef{Diploma1}\ExhibitRef{Diploma2}. He built platforms for civic services and designed data pipelines for election registries. He created tools for national cyber operations and deployed computer vision systems in cities. He led digital programs for major corporations.
\noindent \mrl{} is an engineer specializing in project management, especially in IT project management, see his CV in [exhibit, page]. He graduated from Eurasian National University with honors and University College London (UCL). He has a Bachelor's degree (Civil Engineering) and Master's degree in Building and Urban Design in Development [exhibits UCL]. His Master's degree dissertation on affordable housing were focused on using IT method SDSS system.

\mrl{} is a Head, \textbf{IT project manager} at iKOMEK109 which is similar to the Office of Unified Communications 311 (non-emergency services) in the United States cities. \mrl{} joined iKOMEK109 in May 2022, after getting an experience and working in IT sector for more than 10 years and his career centers on \fie, \ins, \textbf{data platforms} and \textbf{cybersecurity} in government and enterprises. His résumé \ExhibitRef{Resume} and diplomas \ExhibitRef{Diploma1}\ExhibitRef{Diploma2} are included. Across roles, he has delivered (i) omnichannel civic-service platforms, (ii) election-grade address/registry data pipelines, (iii) national cyber-operations tooling, (iv) computer-vision deployments at city scale and (v) enterprise digitalization programs.





\medskip





\smallskip



\noindent\textbf{Criterion 1 — Awards (national/governmental and industry).}

The President awarded him a \emph{Letter of Appreciation} for the 2024 SCO summit 
He earned recognition for the 2022 extraordinary election 
Mayors commended his service Kaspersky honored his cybersecurity leadership 
These honors appear in the Awards Section.
He holds the national “Bolashak” Presidential Scholarship
This grant funded his graduate studies at UCL. The award aligns with his IT career.




\smallskip



\noindent\textbf{Criterion 2 — Association membership requiring outstanding achievements.}



By signed/ sealed Council decision, \mrl{} was admitted to the Kazakhstan Information Security Association (KISA), which applies achievement-based requirements and expert vetting \SectionRef{subsubsec:AssociationsKISA} (\SectionRef{subsec:Associations}).



\smallskip



\noindent\textbf{Criterion 3 — Published material about the person.}

Major media outlets featured his work on city digital platforms. We include translations and proof of credibility 


\smallskip



\noindent\textbf{Criterion 4 — Judge of the work of others.}
He serves as a permanent university reviewer (AIU; ENU) \SectionRef{subsubsec:JudgingAIU}\SectionRef{subsubsec:JudgingENU}, an expert/jury member for national programs (ITeachMe/OrleTECH) \SectionRef{subsubsec:JudgingITeachMeNew} and sits on expert commissions for Kaspersky, the city situation center, the national cyber operator STS and others, issuing written adopt/revise/reject conclusions (\SectionRef{subsubsec:JudgingKasperskyNew}\SectionRef{subsubsec:JudgingIKomek}\SectionRef{subsubsec:JudgingSTS}; see \SectionRef{subsec:Judging}).


\smallskip



\noindent\textbf{Criterion 5 — Original contributions of major significance.}

Independent officials and technical leaders document original platforms/architectures with measurable outcomes: \textit{omnichannel CRM/automation}; \textit{election registry pipelines} (accuracy improved to \(\,100\%\)); \textit{national cyber platforms} (\emph{Synaq}, \emph{ScanKZ}, a closed media-monitoring bot); \textit{600\(+\)}–camera computer vision; \textit{“Life Signal’’} emergency telematics; and \textit{wireless geophone arrays} (\SectionRef{subsec:Contributions}).


\smallskip



\noindent\textbf{Criterion 6 — Authorship of scholarly/professional articles.}

\mrl{} wrote \textbf{13} articles on smart-city analytics and municipal data engineering. He also examined open data, APIs, and civic IT products. Eight papers illustrate this work. They include full academic citations like UDC and DOI codes, and they appeared in VAK-listed journals. \SectionRef{subsec:Articles} presents the certificates and proceedings metadata.


\smallskip



\noindent\textbf{Criterion 7 — Comparable evidence (public display).}
Artistic exhibitions do not suit STEM product leadership, but the record offers \emph{comparable} evidence. It presents curated conference presentations of \mrls technical work. These talks happened publicly, and citable proceedings archive them.



\smallskip



\noindent\textbf{Criterion 8 — Leading or critical roles.}



Leading/critical roles are documented at distinguished organizations: modernization of the city situation center and election-registry accuracy (Governance/iKOMEK109) \SectionRef{subsubsec:LetterBaiken}\SectionRef{subsubsec:LetterBeisenbayev}; daily-used national cyber platforms and board-level governance at \textbf{JSC “State Technical Service’’} \SectionRef{subsubsec:LetterSTS}; cross-agency computer-vision operations \SectionRef{subsubsec:LetterPanchenko}; and enterprise digitalization at EQK 







\smallskip



\noindent\textbf{Criterion 9 — High salary.}



Signed records show his total 2024 pay was $\math{40{,}858{,}987.91}$~KZT. This amount combines income from the municipal enterprise and STS. It exceeds the 2024 average for Astana. HR~Praktika, HeadHunter, and RecCom confirm the difference. We used National Bank of Kazakhstan rates for conversion. High Salary section lists these figures.







\medskip



\emph{City platform, generation 1 — iKOMEK109.} This center handles monitoring and rapid response for the capital. It operates twenty-four hours a day. Residents contact the service through short code 109 or the app. The team uses CCTV feeds and incident analysis. They manage daily services and large events.



\emph{City platform, generation 2 — iKOMEK~2.0.} He led an update to automate the system. It now keeps accurate registries. The platform accepts data from many sources. He presented the work at industry meetings. His employment records confirm these results.



 







\bigskip 



The sections and exhibits prove that \mrl{} meets 9 criterions. He also satisfies Criterion 7 with comparable evidence. His career focus is consistent. He leads programs for civic platforms, protects election data, and builds tools for national cyber operations.