% ==============================
% EB-1A — Criterion 6 (Authorship of Scholarly Articles)
% ==============================

\subsection{Evidence of \mrls authorship of scholarly articles in the field, in professional or major trade publications or other major media}
\label{subsec:Authorship}

% \noindent\textbf{USCIS framework.} Under this criterion, USCIS first determines whether the person has authored \emph{scholarly} articles written for learned readers in the field (with recognizable scholarly apparatus such as abstracts, keywords, subject classifications like UDC/JEL codes, editorial processing, and references). Second, USCIS assesses whether those articles appeared in \emph{professional} or \emph{major trade/major media} venues, which is typically indicated by serial identifiers (ISSN), issue/volume numbering, editorial boards, indexing, and stated publication frequency.

\smallskip
\noindent\textbf{Summary.} Mr.~Taximov has authored \textbf{more than ten} scholarly and professional articles in smart-city analytics, municipal data engineering, open-data/APIs, and civic IT productization. The petition record includes six representative publications (annotated below) that demonstrate both (i) scholarly nature (structured abstracts, keyword sets, UDC/JEL classifications, references, and editorial history) and (ii) professional venues (journal ISSN, issue numbers, contents pages, and editorial boards).

% =========================================================
% Venues (objective indicators of scholarly/professional publication)
% =========================================================
\subsubsection{Representative venues and their scholarly/professional characteristics}

\paragraph{Components of Scientific and Technological Progress (Scientific and Practical Journal).}
The journal masthead explicitly states \emph{Scientific and Practical Journal} and displays \textbf{ISSN 1997-9347}, city and year of publication, and issue numbering (e.g., No.~4(94), 2024). The front matter lists editorial governance and serial metadata, evidencing a professional scientific periodical format appropriate for learned audiences. \ExhibitRef{Article_CSTP_2024_IKomek}\ExhibitRef{CSTP_Issue_Front}

\paragraph{Engineering Bulletin of the Don (Electronic Scientific Journal).}
The article is published in a numbered issue (No.~9, 2024) of a self-described \emph{electronic scientific journal}, confirming a professional, issue-based scientific venue with archival indexing and sectioned scientific content. \ExhibitRef{Article_EVD_2024_Geonomics}

\paragraph{Science and Business: Development Ways.}
This serial organizes content by scholarly sections (e.g., ``Mathematical Modeling and Numerical Methods'') with clear pagination and issue identification (Issue 1(151), 2024). The issue end-matter shows serial production metadata and print-run information, indicating a professional scientific publication aimed at learned readers. \ExhibitRef{Article_ScienceBusiness_2024_BigData}\ExhibitRef{ScienceBusiness_Issue_Pages}

\paragraph{Innovations \& Investments.}
The issue (No.~11, 2023) presents formal editorial apparatus (editorial council/board, issue numbering, contents) and uses economics field \emph{JEL} codes within articles, evidencing learned readership and scholarly framing common to professional economics/management venues. \ExhibitRef{Article_InnovationsInvestments_2023_OpenData}\ExhibitRef{InnovationsInvestments_Issue_Pages}

\paragraph{Vestnik of Technological University.}
The accepted article shows \textbf{UDC 004.65} on the first page and displays a \textbf{DOI} together with structured keywords and an English-language abstract, demonstrating standard scholarly apparatus and editorial processing typical for a professional technical journal. \ExhibitRef{Article_Vestnik_2025_Methodology}

\paragraph{Herald of Computer and Information Technologies (VKIT).}
The journal issue with Mr.~Taximov’s article presents standard scholarly apparatus: a visible \textbf{DOI} (\textbf{10.14489/vkit.2024.03.pp.052-062}), bilingual (EN/RU) title and abstract, a \emph{keywords} block, an \emph{About the Authors} section, and a \emph{References} list; the issue also offers a \emph{Purchase digital version} option. The article appears on pp.~52--62, evidencing formal pagination in a professional scholarly journal. \ExhibitRef{Article_VKIT_2024_AddressRegistry}


% =========================================================
% Annotated record (six exemplars)
% =========================================================
\subsubsection{Annotated record of six representative publications}

\paragraph{(1) ``Methodology for Creating an Effective IT Ecosystem under Resource Constraints'' (A.B.~Taximov; A.A.~Beisenbayev).}
\emph{Vestnik of Technological University}, 2025, Vol.~28, No.~4.  
\emph{Scholarly form:} first page shows \textbf{UDC 004.65}, a \textbf{DOI}, a structured \emph{keywords} block, and an English abstract.  
\emph{Contribution:} an original methodology for building a production IT platform and engineering team under budget limits, describing stack selection (TypeScript, React, Next.js), database-architecture optimization, CI/CD patterns, and staged deployment in operational settings.  
\ExhibitRef{Article_Vestnik_2025_Methodology}

\paragraph{(2) ``Information Technology Tools to Improve Urban Life: iKomek Experience'' (A.B.~Taximov; D.R.~Satvaldina).}
\emph{Components of Scientific and Technological Progress} (Scientific and Practical Journal), No.~4(94), 2024.  
\emph{Scholarly form:} page header identifies the scientific section; the article includes \textbf{UDC 004.65}, an English \emph{title}, \emph{abstract}, and \emph{keywords}, and lists institutional affiliation (City Center of Monitoring and Rapid Response, Astana).  
\emph{Contribution:} formalizes the iKomek operating concept as an algorithmic service-management architecture (omnichannel intake, staged triage, role-based workflows) and analyzes technology deployment that supports urban operations.  
\ExhibitRef{Article_CSTP_2024_IKomek}

\paragraph{(3) ``Geonomics: Address-Registry Maintenance and Population Heat-Map Analytics for Smart-City Operations'' (A.B.~Taximov; A.A.~Beisenbayev).}
\emph{Engineering Bulletin of the Don} (Electronic Scientific Journal), Issue No.~9, 2024.  
\emph{Scholarly form:} issue identification and scientific-journal styling; structured technical narrative with terms, definitions, and method steps; references to prior work.  
\emph{Contribution:} presents the ``Geonomics'' system that integrates municipal address registries with cartographic geometries and state databases to (i) keep resident records current in near-real-time, (ii) bind addresses to precincts for election-period accuracy, and (iii) generate population-density heat-maps used to site public services.  
\ExhibitRef{Article_EVD_2024_Geonomics}

\paragraph{(4) ``Possibilities of Using Open Data: the Concept of e-Democracy in Smart-City Management'' (A.B.~Taximov; A.A.~Beisenbayev).}
\emph{Innovations \& Investments}, No.~11, 2023.  
\emph{Scholarly form:} issue carries full editorial apparatus and contents; the article includes an extensive \emph{references} list to international sources and uses \emph{JEL} subject classifications standard in the economics/management literature.  
\emph{Contribution:} positions open data within smart-city governance and e-democracy practice, linking publication formats and API access to measurable transparency and service-improvement goals.  
\ExhibitRef{Article_InnovationsInvestments_2023_OpenData}

\paragraph{(5) ``Big Data as a Smart-City Management Tool'' (A.B.~Taximov; A.A.~Beisenbayev).}
\emph{Science and Business: Development Ways}, Issue 1(151), 2024 (Section: Mathematical Modeling and Numerical Methods).  
\emph{Scholarly form:} sectioned placement, serial pagination, and issue identification; the issue colophon shows serial production and print-run data.  
\emph{Contribution:} frames city-scale Big Data as a management instrument for operations and planning, aligning statistical/ML methods with urban KPI tracking and decision support.  
\ExhibitRef{Article_ScienceBusiness_2024_BigData}\ExhibitRef{ScienceBusiness_Issue_Pages}

\paragraph{(6) ``Information Technologies in Updating and Forming Address Information'' (A.B.~Taximov; A.A.~Beisenbayev).}
\emph{Herald of Computer and Information Technologies (VKIT)}, 2024, pp.~52--62; \textbf{DOI: 10.14489/vkit.2024.03.pp.052-062}. \\
\emph{Scholarly form:} the article is published with a visible DOI; it includes bilingual (EN/RU) title and abstract, \emph{keywords}, an \emph{About the Authors} section, and a \emph{References} list; the issue also provides a \emph{Purchase digital version} option—hallmarks of a professional scholarly journal. \\
\emph{Contribution:} the study documents the city’s data-engineering program for election-period registries and reports a measured lift of voter-list accuracy \textbf{from 84\% to 100\%}, achieved via modern information-technology methods for address-code verification, data updates, and precinct binding. The paper details methods, procedures, technical solutions, and supporting statistics, and concludes that the approach improves the accuracy and transparency of election processes and is scalable to other stakeholders. \\
\ExhibitRef{Article_VKIT_2024_AddressRegistry}

% =========================================================
% Why these works are "scholarly" and in professional venues
% =========================================================
\subsubsection{Why the record satisfies USCIS Criterion 6}

\paragraph{Scholarly nature.}
Across the exemplars, the record shows recognized scholarly apparatus: \textbf{UDC} classification (e.g., UDC~004.65), \textbf{DOI} identifiers on the article first page, structured \emph{abstracts} and \emph{keywords}, learned sectioning (e.g., ``Mathematical Modeling and Numerical Methods''), and substantive \emph{references} to international literature. Several items show \emph{editorial processing} markers (issue/volume, acceptance/issue pages), evidencing standard scholarly workflows. \ExhibitRef{Article_Vestnik_2025_Methodology}\ExhibitRef{Article_CSTP_2024_IKomek}\ExhibitRef{Article_InnovationsInvestments_2023_OpenData}

\paragraph{Professional/major trade or major media venues.}
The venues are serial scientific journals with professional indicia: \emph{Components of Scientific and Technological Progress} displays \textbf{ISSN 1997-9347}, location/year, and issue number on the front page, and labels itself a \emph{Scientific and Practical Journal}; \emph{Engineering Bulletin of the Don} identifies as an \emph{electronic scientific journal} with numbered issues; \emph{Science and Business: Development Ways} presents sectioned scholarly content with pagination and print-run/production metadata; and \emph{Innovations \& Investments} provides a full editorial council/board and issue-level contents. \ExhibitRef{CSTP_Issue_Front}\ExhibitRef{Article_EVD_2024_Geonomics}\ExhibitRef{ScienceBusiness_Issue_Pages}\ExhibitRef{InnovationsInvestments_Issue_Pages}

% =========================================================
% Anticipating typical RFE prompts (completeness, scholarly nature, venue)
% =========================================================
\subsubsection{Addressing common RFE points}

\begin{itemize}
  \item \textbf{Completeness of record.} The petition documents \textbf{more than ten} authored works; six representative items are provided with venue/issue proof that shows author name, article title, and the publication. Additional titles can be listed in the publications appendix as needed. \ExhibitRef{Article_List_Master}
  \item \textbf{Scholarly nature.} The attached articles exhibit standard scholarly markers: UDC/DOI on first pages, abstracts and keywords, learned sectioning, and references—demonstrating that the works are written for learned readers in public-sector IT, urban informatics, and applied analytics. \ExhibitRef{Article_Vestnik_2025_Methodology}\ExhibitRef{Article_CSTP_2024_IKomek}
  \item \textbf{Professional/major publication venues.} The journals identify as scientific periodicals, display ISSN and issue numbering, provide contents and editorial governance, and (where shown) present production metadata or indexation notes—factors USCIS considers when determining professional status. \ExhibitRef{CSTP_Issue_Front}\ExhibitRef{InnovationsInvestments_Issue_Pages}
\end{itemize}

\subsubsection{Conclusion under Criterion 6}
The documentary record demonstrates that Mr.~Taximov is the author of \textbf{more than ten} scholarly and professional publications in his field. The six detailed exemplars show recognizable scholarly apparatus and placement in professional scientific journals with serial identifiers and editorial governance. This satisfies both prongs of USCIS Criterion~6.

% =========================================================
% Exhibits referenced in this section (placeholders to map in your index)
% =========================================================
\ExhibitList{
  \ExhibitRef{Article_Vestnik_2025_Methodology} % Vestnik of Technological University article (UDC + DOI + abstract/keywords)
  \ExhibitRef{Article_CSTP_2024_IKomek}         % Components of Scientific and Technological Progress article (UDC + English abstract)
  \ExhibitRef{CSTP_Issue_Front}                 % Issue front matter showing ISSN 1997-9347, location, numbering
  \ExhibitRef{Article_EVD_2024_Geonomics}       % Engineering Bulletin of the Don article (Issue 9, electronic scientific journal)
  \ExhibitRef{Article_ScienceBusiness_2024_BigData} % Science and Business: Development Ways article (Issue 1(151), sectioned scholarly content)
  \ExhibitRef{ScienceBusiness_Issue_Pages}      % Issue pages/colophon with print-run/production metadata
  \ExhibitRef{Article_InnovationsInvestments_2023_OpenData} % Innovations & Investments article (issue pages, references, JEL usage)
  \ExhibitRef{InnovationsInvestments_Issue_Pages} % Editorial council/board and contents for No. 11 (2023)
  \ExhibitRef{Article_AddressRegistry_Workflow} % Manuscript on address register / residents’ registry workflow
  \ExhibitRef{Article_List_Master}              % Master list summary showing >10 authored works (appendix)
}

==============================
EB-1A — Criterion 6 (Authorship of Scholarly Articles)
==============================

% \subsection{Evidence of \mrls authorship of scholarly articles in the field, in professional or major trade publications or other major media}
% \label{subsec:Authorship}

% \subsubsection{\mrl has authored more than ten scholarly and professional articles in smart-city IT and public-sector analytics}
% As evidenced in the petition record and the attached journal issues, Mr.~Taximov has authored \textbf{more than ten} scholarly and professional publications. Six representative articles (attached) span municipal analytics, smart-city data engineering, open data/APIs, and operational IT productization:
% \begin{enumerate}
%   \item \emph{Methodology for Creating an Effective IT Ecosystem under Resource Constraints} (with A.A.~Beisenbayev), \textit{Vestnik of Technological University}, 2025, Vol.~28, No.~4 — first page shows UDC 004.65 and a DOI; structured abstract and keywords. \ExhibitRef{Article_Vestnik_2025_Methodology}
%   \item \emph{Information Technology Tools to Improve Urban Life: iKomek Experience} (with D.R.~Satvaldina), \textit{Components of Scientific and Technological Progress}, No.~4(94), 2024 — scientific/practical journal; English abstract and keywords; UDC on article header. \ExhibitRef{Article_CSTP_2024_IKomek}
%   \item \emph{Geonomics: Address-Registry Maintenance and Population Heat-Map Analytics} (with A.A.~Beisenbayev), \textit{Engineering Bulletin of the Don} (Electronic Scientific Journal), Issue 9, 2024 — issue-numbered scientific journal. \ExhibitRef{Article_EVD_2024_Geonomics}
%   \item \emph{Possibilities of Using Open Data: the Concept of e-Democracy in Smart-City Management} (with A.A.~Beisenbayev), \textit{Innovations \& Investments}, No.~11, 2023 — references section with international sources; JEL subject codes. \ExhibitRef{Article_InnovationsInvestments_2023_OpenData}
%   \item \emph{Big Data as a Smart-City Management Tool} (with A.A.~Beisenbayev), \textit{Science and Business: Development Ways}, Issue 1(151), 2024, section “Mathematical Modeling and Numerical Methods.” \ExhibitRef{Article_ScienceBusiness_2024_BigData}
%   \item \emph{Information Technologies in Updating and Forming Address Information} (with A.A.~Beisenbayev), \textit{Herald of Computer and Information Technologies (VKIT)}, 2024, pp.~52–62; \textbf{DOI: 10.14489/vkit.2024.03.pp.052-062}. \ExhibitRef{Article_VKIT_2024_AddressRegistry}
% \end{enumerate}
% These attached items document the authorship, titles, and publication venues and are representative of Mr.~Taximov’s broader publication record (the remaining items are listed in the publications appendix). \ExhibitRef{Article_List_Master}

% \subsubsection{Mr.~Taximov’s publications have appeared in professional scientific journals and major trade venues in the field}
% The attached venues show the attributes USCIS associates with professional publication (ISSN, editorial boards, peer-review statements, serial numbering, and indexing), as well as formal pagination and production metadata:
% \begin{itemize}
%   \item \textbf{Components of Scientific and Technological Progress} (Scientific and Practical Journal). The masthead identifies a scientific/practical journal with \textbf{ISSN 1997-9347}, place/year and issue numbering (e.g., No.~4(94), 2024), and editorial governance; issue front matter includes production data (print approval, print run) and international contacts. \ExhibitRef{CSTP_Issue_Front}\ExhibitRef{Article_CSTP_2024_IKomek}
%   \item \textbf{Engineering Bulletin of the Don} (Electronic Scientific Journal). The article appears in a numbered issue (Issue 9, 2024) of a scientific e-journal with archived issues and article pages. \ExhibitRef{Article_EVD_2024_Geonomics}
%   \item \textbf{Science and Business: Development Ways}. The serial organizes learned sections (e.g., “Mathematical Modeling and Numerical Methods”), shows issue identification and pagination, and prints a colophon with serial production metadata (including print run). \ExhibitRef{ScienceBusiness_Issue_Pages}\ExhibitRef{Article_ScienceBusiness_2024_BigData}
%   \item \textbf{Innovations \& Investments}. Issue No.~11 (2023) presents full editorial apparatus (editorial council/board, issue numbering, contents), and articles use economics \textbf{JEL} classifications, reflecting a professional, learned audience. \ExhibitRef{InnovationsInvestments_Issue_Pages}\ExhibitRef{Article_InnovationsInvestments_2023_OpenData}
%   \item \textbf{Vestnik of Technological University}. The accepted article page shows \textbf{UDC 004.65} and a \textbf{DOI}, with structured keywords and abstract, evidencing technical journal processing. \ExhibitRef{Article_Vestnik_2025_Methodology}
%   \item \textbf{Herald of Computer and Information Technologies (VKIT)}. The published item shows a visible \textbf{DOI} (\textbf{10.14489/vkit.2024.03.pp.052-062}), bilingual title/abstract, keywords, \emph{About the Authors}, \emph{References}, and a “Purchase digital version” option—hallmarks of a professional scholarly journal with formal article workflows. \ExhibitRef{Article_VKIT_2024_AddressRegistry}
% \end{itemize}
% For each venue, the record also includes—or will include—\emph{official website screenshots with visible URL} (About/Editorial Policy/Peer-review pages, circulation notes) to corroborate status as professional journals or major media. \ExhibitRef{CSTP_Web_Screenshot}\ExhibitRef{EVD_Web_Screenshot}\ExhibitRef{ScienceBusiness_Web_Screenshot}\ExhibitRef{InnovationsInvestments_Web_Screenshot}\ExhibitRef{Vestnik_Web_Screenshot}\ExhibitRef{VKIT_Web_Screenshot}

% \subsubsection{Scholarly nature: learned audience, peer review, and formal scholarly apparatus}
% Because Razvan’s template emphasizes impact or peer review in lieu of citation statistics when appropriate, we document the following scholarly features across the attached articles and issues:
% \begin{itemize}
%   \item \textbf{Peer-review statements and inclusion in lists of leading peer-reviewed journals.} Issues describe internal/external review procedures or inclusion in formal peer-reviewed lists, and present editorial boards/advisory councils. \ExhibitRef{InnovationsInvestments_Issue_Pages}\ExhibitRef{CSTP_Issue_Front}
%   \item \textbf{Standard scholarly apparatus.} First pages or headers show \textbf{DOI} and/or \textbf{UDC} codes; articles include \emph{abstracts}, \emph{keywords}, \emph{About the Authors}, and \emph{References}. \ExhibitRef{Article_Vestnik_2025_Methodology}\ExhibitRef{Article_VKIT_2024_AddressRegistry}\ExhibitRef{Article_CSTP_2024_IKomek}
%   \item \textbf{Learned sectioning and pagination.} Journals use technical sections (e.g., “Mathematical Modeling and Numerical Methods”), issue/volume numbering, and formal pagination (e.g., VKIT pp.~52–62). \ExhibitRef{Article_ScienceBusiness_2024_BigData}\ExhibitRef{Article_VKIT_2024_AddressRegistry}
%   \item \textbf{Circulation and geography.} Issue colophons provide print-run data and distribution indicators (e.g., print run and international production contacts), supporting professional standing as serial publications. \ExhibitRef{ScienceBusiness_Issue_Pages}\ExhibitRef{CSTP_Issue_Front}
% \end{itemize}

% \subsubsection{Conclusion under Criterion 6}
% The documentary record shows that Mr.~Taximov has authored \textbf{more than ten} scholarly and professional publications, with six representative articles attached. The venues are professional scientific journals with peer-review processes, serial identifiers (ISSN/issue numbering), editorial governance, and formal scholarly apparatus (UDC/DOI, abstracts, keywords, references). This mirrors USCIS’s two-step inquiry (scholarly authorship + professional/major venue) and satisfies Criterion~6.

% % Exhibits referenced in this section (placeholder keys to map to your index)
% \ExhibitList{
%   \ExhibitRef{Article_Vestnik_2025_Methodology}
%   \ExhibitRef{Article_CSTP_2024_IKomek}
%   \ExhibitRef{CSTP_Issue_Front}
%   \ExhibitRef{Article_EVD_2024_Geonomics}
%   \ExhibitRef{Article_ScienceBusiness_2024_BigData}
%   \ExhibitRef{ScienceBusiness_Issue_Pages}
%   \ExhibitRef{Article_InnovationsInvestments_2023_OpenData}
%   \ExhibitRef{InnovationsInvestments_Issue_Pages}
%   \ExhibitRef{Article_VKIT_2024_AddressRegistry}
%   \ExhibitRef{CSTP_Web_Screenshot}
%   \ExhibitRef{EVD_Web_Screenshot}
%   \ExhibitRef{ScienceBusiness_Web_Screenshot}
%   \ExhibitRef{InnovationsInvestments_Web_Screenshot}
%   \ExhibitRef{Vestnik_Web_Screenshot}
%   \ExhibitRef{VKIT_Web_Screenshot}
%   \ExhibitRef{Article_List_Master}
% }
