\subsubsection{Joint-Stock Company “Astana Innovations” (Smart City Operator)}
\label{subsubsec:RoleAIN}

\SubSubSubSection{Context and distinguished reputation}

\textbf{Astana Innovations} (AIN) is the city-owned Smart City operator, responsible for digital platforms that power municipal analytics, open data/APIs and telecom-duct infrastructure. Its public website sets out this mandate and governance structure; the official Instagram account reflects sustained public activity and outreach. \ExhibitRef{AINSiteShot}\ExhibitRef{AINInstagramShot}  
Given its control of Big Data, APIs and telecom ducts used by municipal agencies, AIN acts as the \textbf{platform backbone} for multiple public services in Astana.

\SubSubSubSection{Appointment and mandate}

AIN appointed Mr.\ Taximov to lead cross-functional IT programs spanning \textbf{(i) Big Data \& analytics}, \textbf{(ii) Open Data $\rightarrow$ Open APIs transition}, \textbf{(iii) telecom-duct operations} and \textbf{(iv) data-driven policy projects} (transport planning, social compliance). The official role letter documents the scope and results below. \ExhibitRef{AINRoleLetter}

\SubSubSubSection{Evidence of a leading and critical role (with quantified results)}

\paragraph{1) City Big Data operator and transport planning impact.}
\ParagraphQuoteByExhibit{“As operator of the Big Data platform, Mr.\ Taximov supervised around \textbf{76} municipal databases. Under his leadership, \textbf{12} analytical models were developed, including a new text/geo visualization block. Updates to the transport model enabled planning by passenger flows and improved efficiency by \textbf{17\%}.”}{AIN Role Letter}{AINRoleLetter}  
This is a \textbf{leading} role in platform and model governance with \textbf{critical} impact on a major city function (public transport).

\paragraph{2) Social policy analytics and cross-agency compliance.}
\ParagraphQuoteByExhibit{“He directed analytics that identified \textbf{32{,}000} illegally registered residents (‘rubber apartments’) and profiled \textbf{14{,}601} large families with \textbf{92{,}957} children to target social support.”}{AIN Role Letter}{AINRoleLetter}  
Delivering law-enforcement and social-policy datasets is \textbf{central to AIN’s public value} and shows significant cross-agency coordination.

\paragraph{3) Open Data $\rightarrow$ Open APIs modernization.}
\ParagraphQuoteByExhibit{“He moved the Open Data portal to interactive APIs (xls, csv, json), enabling automated and secure integrations across education, healthcare, transport and utilities.”}{AIN Role Letter}{AINRoleLetter}  
This is \textbf{core platform modernization}. Converting static publication into programmatic APIs is a textbook product leadership milestone.

\paragraph{4) Telecom-duct turnaround with commercial results.}
\ParagraphQuoteByExhibit{“As manager of the telecom ducts, he automated processes, reduced permit timelines from \textbf{30} to \textbf{14} days, increased contracts from \textbf{20} to \textbf{73} and grew revenue from \textbf{KZT 38 million} to \textbf{KZT 152 million}.”}{AIN Role Letter}{AINRoleLetter}  
Process + revenue + partner growth = \textbf{critical business impact} driven by IT.

\paragraph{5) Elections automation and data integrity.}
\ParagraphQuoteByExhibit{“He automated election procedures, achieving accuracy lifts from \textbf{84.4\%} to \textbf{100\%} of voter lists, produced \textbf{248} precinct passports and launched an online voter-check service.”}{AIN Role Letter}{AINRoleLetter}  
High-stakes civic data quality and service rollout reflect \textbf{hands-on leadership} with citywide consequences.

\SubSubSubSection{Why this meets USCIS Criterion 8}

AIN’s status as the Smart City platform operator and its persistent public footprint establish a \textbf{distinguished reputation}. The AIN letter provides \textbf{quantified outcomes} attributable to Mr.\ Taximov (transport efficiency, revenue growth, compliance analytics, election integrity), satisfying the \textbf{leading/critical} performance prong.

\ExhibitList{
  \ExhibitRef{AINRoleLetter}
  \ExhibitRef{AINSiteShot}
  \ExhibitRef{AINInstagramShot}
}
